---
title: "Model yearly flux"
author: "Kriddie"
date: "2023-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(dplyr)
library(here)
library(lme4)
library(lmerTest)
library(jtools)
library(reshape2)
library(ggplot2)
```

## modeling CO2 and CH4 flux

In this iteration of this R markdown, I am simplifying my analysis. For now this makes sense to do because I need to make a poster very soon and so I need to cut some loses. As of now, I'm not sure whether what I am doing can be fully supported and whether I should add the other analysis in for the paper.

1. Drop analysis with no Wetland 12. I looked into dropping wetland 12 because it is different from the other wetlands (lots of veg, uneven border 0and also I didn't measure depth so we don't have depth to surface area ratio. BUT not that i've done analysis, the predictors for co2 and ch4 do not include depth to surface area ratio, so I think, for now, we will leave in wetland 12

2. Model with modeled k instead of mean... cause i don't think it matters much? or should I use mean --- ahhhh
Ok I'm going to just use mean


Also added in this version is conversion of k from co2 to ch4, as found here: Raymond et al. 2012
https://aslopubs.onlinelibrary.wiley.com/doi/full/10.1215/21573689-1597669

k(gas1)/k(gas2) = (sc(gas1)/sc(gas2))^-n
because we are doing ponds, n = 2/3
Sc: Schmidt number temperature dependencies -- using Wanninkhof(1992) as reported in linked citation above
    CO2: 1911 + -118.11* T + 3.453 * T^2 + -0.0413 * T^3
    CH4: 1898 + -114.28* T + 3.29* T^2 + -.0391 * T^3
    
  T is in degree celcius
```{r read in data}

df <- read.csv(here::here("Wetlands/Wetland_df_MERGE_2023-11-10.csv"))
df$Date <- as.Date(df$Date)

#calculate k for ch4
#k(gas1)/k(gas2) = (sc(gas1)/sc(gas2))^-n
df$Sc_co2 <- 1911 - 118.11*df$Watertemp_c + 3.453*(df$Watertemp_c)^2 - 0.0413*(df$Watertemp_c)^3
df$Sc_ch4 <- 1898 + -114.28*df$Watertemp_c + 3.29*(df$Watertemp_c)^2 + -.0391*(df$Watertemp_c)^3

df$k_ch4 <- (df$Sc_ch4/df$Sc_co2)^2/3 * df$k_m.d

WL_df <- read.csv(here::here("Wetlands/WaterLevel_FINAL/WL_Wetland_all_FINAL.csv"))
WL_df <- WL_df[c("DateTime","Station","Baro_kpa","BaroTemp_c","WLTemp_c","depth_ave_m","surface_area_m2","Volumn_m3","SA_to_Vol_ratio")]
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
WL_df$Wetland <- gsub(".*_","",WL_df$Station)
WL_df$Station <- NULL
WL_df$Date <- as.Date(WL_df$DateTime)
WL_df$WaterTemp_c <- WL_df$WLTemp_c
WL_df$WLTemp_c <- NULL

WL_df_saved <- WL_df


#add henry's constant co2
kH_STP_mol.L.atm = .035
D_K = 2400 
T_STP_K = 298.15

#calculate henry's law constant using 
WL_df$KH_CO2_mol.L.atm <- kH_STP_mol.L.atm * exp(D_K*(1/(WL_df$WaterTemp_c+273.15) - 1/T_STP_K))


#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
WL_df$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(WL_df$WaterTemp_c+273.15)-1/T_STP_K))

#co2 in the air
#concentration of air
#from www.esrl.noaa.gov
#average of July and August
#410.86 ppm
CO2_air_ppm <- 410*10^-6
R=0.08205736608096
gCO2asC <- 12

WL_df$air_pressure_atm <- WL_df$Baro_kpa * 0.00986923 #convert kpa to atm
WL_df$VaporPressure_atm <- 10^(5.40221-(1838.675/((WL_df$BaroTemp_c + 273.15)-31.737)))
WL_df$TotalAir_atm <- WL_df$air_pressure_atm - WL_df$VaporPressure_atm
WL_df$Total_air_MolperL <- WL_df$TotalAir_atm/(R*(WL_df$BaroTemp_c + 273.15)) 
WL_df$CO2_air_umol.L <- WL_df$Total_air_MolperL * CO2_air_ppm *1000

#Ambient CH4 concentration ppm	1.912388333	
#average 2021 from Moaa

CH4_air_ppm <- 1.912388333	*10^-6

WL_df$CH4_air_umol.L <- WL_df$Total_air_MolperL * CH4_air_ppm *1000
```

#Buid time series data frame

```{r build dataframe}
#here are the factors that are important for CO2 FLUX
#BaroTemp_c_yearly
#waterTemp_c_yearly
#Water_minus_air_Temp
#waterTemp_c_day
#precip_mm_ave2
#solarrad_Wm2

#add in yearly, elevation, watershed
#AirTemp yearly aka BaroTemp_c_yearly
    #see Merge_wetlandDATA.R for more details
WL_df_new <- left_join(WL_df,df[c("Wetland","BaroTemp_c_yearly","waterTemp_c_yearly","Elevation_m",
                                  "Watershed_m2")],by="Wetland")
BaroStation <- 4158.6912
slope_temp <- -6.5/1000
WL_df_new$Baro_Water_minus_air_Temp <- WL_df_new$BaroTemp_c - WL_df_new$WaterTemp_c

WL_df_new$SA_log <- log(WL_df_new$surface_area_m2)
WL_df_new$SA_log  <- replace(WL_df_new$SA_log , is.infinite(WL_df_new$SA_log ), 
NA)

WL_df_new <- unique(WL_df_new)
```

```{r  add enviro factor, echo=FALSE}

WL_summary_day <- WL_df %>%
  group_by(Wetland,Date)%>%
  summarise(waterTemp_c_day = mean(WaterTemp_c, na.rm = TRUE))

WL_df_new <- left_join(WL_df_new,WL_summary_day,by=c("Date","Wetland"))

Solar_df <- read.csv(here::here("Wetlands/WeatherStation_LaVirgen/M5025_Radiacion_Solar_Dato_validado.csv"))
colnames(Solar_df) <- c("DateTime","solarrad_W_m2","Solarrad_max","solarrad_min")
Solar_df$DateTime <- as.POSIXct(Solar_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
Solar_df$DateTime <- round_date(Solar_df$DateTime,unit = "15 minutes")
Solar_df$Date <- as.Date(Solar_df$DateTime)
Solar_df <- na.omit(Solar_df)

#want solar at the instant
Solar_df_DateTime <- Solar_df%>%group_by(DateTime)%>% 
  summarise(
    solarrad_Wm2 = mean(solarrad_W_m2, na.rm = TRUE))
#I also want solar ave day
Solar_df <- Solar_df%>%group_by(Date)%>% 
  summarise(
    solarrad_Wm2_daymean = mean(solarrad_W_m2, na.rm = TRUE),
#    solarrad_min = min(solarrad_min, na.rm = TRUE) # don't include min because it will always be 0 (night)
  )

WL_df_new <- left_join(WL_df_new,Solar_df_DateTime,by=c("DateTime"))
WL_df_new <- left_join(WL_df_new,Solar_df,by=c("Date"))

#need precip at time interval and also ave of two days precipt 

precip_df <- read.csv(here::here("Wetlands/WeatherStation_LaVirgen/M5025_Precipitacion_Dato_validado.csv"))
colnames(precip_df) <- c("DateTime","precipt_mm")
precip_df$DateTime <- as.POSIXct(precip_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
precip_df$Date <- as.Date(precip_df$DateTime,format="%Y-%m-%d")
precip_summary <- precip_df%>%group_by(Date)%>%summarise(PrecipAccuDay_mm = sum(precipt_mm))
#now add previous amount of precipitation from day previous
precip_summary$Date_used <- precip_summary$Date
precip_summary$Date <- precip_summary$Date - 1
precip_summar_previous <- precip_summary[,c("Date","PrecipAccuDay_mm")]
colnames(precip_summar_previous) <- c("Date","PrecipAccuPreviousDay_mm")
precip_summary <- precip_summary[,c("Date_used","PrecipAccuDay_mm")]
colnames(precip_summary) <- c("Date","PrecipAccuDay_mm")

precip_df_2 <- full_join(precip_summary,precip_summar_previous, by="Date")

#add average precip of day and previous
precip_df_2$precip_mm_ave2 <- (precip_df_2$PrecipAccuDay_mm + precip_df_2$PrecipAccuPreviousDay_mm)/2

WL_df_new <- left_join(WL_df_new,precip_df[c("DateTime","precipt_mm")],by=c("DateTime"))
WL_df_new <- left_join(WL_df_new,precip_df_2,by=c("Date"))

rm(Solar_df,Solar_df_DateTime, precip_df,precip_df_2,precip_summary,precip_summar_previous)


WL_df_extrapolate <- WL_df_new
```

## Write flux models AIc and BIC, with and without wetland 12
#in nower version of this script, we only do BIC
#time to extrapolate
1. calculate flux for each time segment


#notes
  Air minus water temperature is significant in both flux and k. However we don't have that data throughout the year. we do have Baro_air_minus_water_temp, but that is not a significant predictor in either case
  When we replace Air minus water temperature with Baro_air_minus_water_temp, instead solar rad becomes more imporatant as an explainer
  could it be that the way that I collected air temperature (bringing a water level sensor that is fully exposed to the air) somehow captures variability in solar radiation in a way that is not captured when correcting temperature collected in the barmetric temp
  
  for now we will model early trends without air-water temp. however, we should look into this further 

```{r plot what you've done, echo=FALSE}


#checked
  #surface_area_m2
  #SA_to_Vol_ratio
  #WaterTemp_c
  #KH_CO2_mol.L.atm
  #KH_CH4_mol.L.atm
  #SA_log
  #waterTemp_c_day
  #solarrad_Wm2
  #solarrad_Wm2_daymean
  #precipt_mm
  #PrecipAccuDay_mm
  #PrecipAccuPreviousDay_mm

WL_df_extrapolate$FLUX_noW12_umol_15min
WL_df_extrapolate$FLUX_W12

#ggplot(WL_df_extrapolate%>%filter(Wetland=="Wetland11"),aes(x=DateTime, y=FLUX_W12)) + geom_point(size=2, shape=23)


```



```{r flux models, echo=FALSE}

#BIC: 	
#(Intercept), scale(BaroTemp_c_yearly), scale(waterTemp_c_day), scale(log(surface_area_m2)), scale(solarrad_Wm2_daymean)

df_1 <- df#%>%filter(Wetland!="Wetland12")

M_FLUX_scratch <- lmer(log(Flux_umol_m2_s) ~ 
                  log(CO2_umol.L)+
                  (1 |Wetland), data =df_1,REML = FALSE)

M_FLUX_W12 <- lmer(log(Flux_umol_m2_s) ~ 
                  BaroTemp_c_yearly+ 
                  waterTemp_c_day +
                  log(surface_area_m2) +
                    solarrad_Wm2_daymean +
                  (1 |Wetland), data =df_1,REML = FALSE)

sum_df <- summary(M_FLUX_W12)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_FLUX_W12)$Wetland[1]
intercept_df$Wetland <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Wetland")
WL_df_extrapolate <- left_join(WL_df_extrapolate,intercept_df,by="Wetland")

WL_df_extrapolate$FLUX_W12 <- exp(WL_df_extrapolate$intercept #+ 
#   WL_df_extrapolate$BaroTemp_c_yearly * coeff_df[2,"Estimate"] +
#  WL_df_extrapolate$waterTemp_c_day * coeff_df[3,"Estimate"] +
#  WL_df_extrapolate$SA_log * coeff_df[4,"Estimate"] +
#  WL_df_extrapolate$solarrad_Wm2_daymean * coeff_df[5,"Estimate"]
)

WL_df_extrapolate$intercept <- NULL

```

#co2 models

```{r co2 models, echo=FALSE}

##
#co2 WITH wetland 12

df_1 <- df#%>%filter(Wetland!="Wetland12")

##
#BIC: (Intercept), scale(BaroTemp_c_yearly), scale(waterTemp_c_yearly)


M_CO2_W12 <- lmer(log(CO2_umol.L) ~ 
                  BaroTemp_c_yearly+ 
                  waterTemp_c_yearly +
                  (1 |Wetland), data =df_1,REML = FALSE)
sum_df <- summary(M_CO2_W12)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_CO2_W12)$Wetland[1]
intercept_df$Wetland <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Wetland")
WL_df_extrapolate <- left_join(WL_df_extrapolate,intercept_df,by="Wetland")

WL_df_extrapolate$CO2_W12 <- exp(
  WL_df_extrapolate$intercept +
   WL_df_extrapolate$BaroTemp_c_yearly * coeff_df[2,"Estimate"] +
  WL_df_extrapolate$waterTemp_c_yearly * coeff_df[3,"Estimate"]
  )


WL_df_extrapolate$intercept <- NULL

```

#model k

for all k models, solar radiation is the most important predictor. 

```{r k models, echo=FALSE}

#k WITH Wetland 12
df_1 <- df#%>%filter(Wetland!="Wetland12")

#AIC k: (Intercept), scale(solarrad_W_m2)
M_k_W12 <- lmer(k_m.d ~ 
                  solarrad_Wm2_daymean+ 
                  (1 |Wetland), data =df_1,REML = FALSE)
sum_df <- summary(M_k_W12)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_k_W12)$Wetland[1]
intercept_df$Wetland <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Wetland")
WL_df_extrapolate <- left_join(WL_df_extrapolate,intercept_df,by="Wetland")

WL_df_extrapolate$k_W12 <- WL_df_extrapolate$intercept +
   WL_df_extrapolate$solarrad_Wm2_daymean * coeff_df[2,"Estimate"] 

WL_df_extrapolate$intercept <- NULL

#averages

WL_df_extrapolate$K_m.d_mean <- mean(df$k_m.d)
WL_df_extrapolate$K600_mean <- mean(df$K600)

WL_df_extrapolate$K_ch4_mean <- mean(df$k_ch4)

```


#model CH4

```{r  CH4 models, echo=FALSE}

#CH4 WITH Wetland 12
df_1 <- df#%>%filter(Wetland!="Wetland12")

#BIC
#	(Intercept), (Intercept), scale(BaroTemp_c_yearly), scale(Baro_Water_minus_air_Temp), scale(waterTemp_c_day)


M_CH4_W12 <- lmer(log(CH4_umol.L) ~ 
                          BaroTemp_c_yearly+
                  (1 |Wetland), data =df_1,REML = FALSE)
sum_df <- summary(M_CH4_W12)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_CH4_W12)$Wetland[1]
intercept_df$Wetland <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Wetland")
WL_df_extrapolate <- left_join(WL_df_extrapolate,intercept_df,by="Wetland")

WL_df_extrapolate$CH4_W12 <- exp(
  WL_df_extrapolate$intercept +
   WL_df_extrapolate$BaroTemp_c_yearly * coeff_df[2,"Estimate"]
)

WL_df_extrapolate$intercept <- NULL

```

```{r  calc flux, echo=TRUE}
#calculate total flux

WL_df_extrapolate$FLUX_W12_umol_15min <- WL_df_extrapolate$FLUX_W12 * WL_df_extrapolate$surface_area_m2 * 60 *15 

#use CO2 and k models to calc flux

WL_df_extrapolate$FLUX_W12_CALC_umol_s <- WL_df_extrapolate$K_m.d_mean * (WL_df_extrapolate$CO2_W12 - WL_df_extrapolate$CO2_air_umol.L) 

WL_df_extrapolate$FLUX_W12_CALC_umol_15min <- WL_df_extrapolate$FLUX_W12_CALC_umol_s * WL_df_extrapolate$surface_area_m2 * 60 *15

#####
#CH4#
#####
WL_df_extrapolate$FLUXch4_noW12_CALC_umol_s <- WL_df_extrapolate$K_ch4_mean * (WL_df_extrapolate$K_ch4_mean - WL_df_extrapolate$CH4_air_umol.L) 

WL_df_extrapolate$FLUXch4_noW12_CALC_umol_15min <- WL_df_extrapolate$FLUXch4_noW12_CALC_umol_s * WL_df_extrapolate$surface_area_m2 * 60 *15 


WL_df_extrapolate$FLUXch4_W12_CALC_umol_s <- WL_df_extrapolate$K_ch4_mean * (WL_df_extrapolate$CH4_W12 - WL_df_extrapolate$CH4_air_umol.L) 

WL_df_extrapolate$FLUXch4_W12_CALC_umol_15min <- WL_df_extrapolate$FLUXch4_W12_CALC_umol_s * WL_df_extrapolate$surface_area_m2 * 60 *15 

```

2. sum per month or week?
3. sum per year
4. compare for all models

```{r   summary tables, echo=FALSE}

WL_df_extrapolate$month <- format(as.Date(WL_df_extrapolate$Date), "%Y-%m")

WL_df_extrapolate_daySUMMARY <- WL_df_extrapolate%>%
  group_by(Date,Wetland)%>% 
  summarise(
    FLUX_W12_umol15min_dayAve = mean(FLUX_W12_umol_15min, na.rm = TRUE),
    FLUX_W12_CALC_umol15min_dayAve = mean(FLUX_W12_CALC_umol_15min, na.rm = TRUE)
  )

WL_df_extrapolate_yearSUMMARY <- WL_df_extrapolate_daySUMMARY%>%
  group_by(Wetland)%>% 
  summarise(
    FLUX_W12_umol_yearMEAN = mean(FLUX_W12_umol15min_dayAve, na.rm = TRUE),
    FLUX_W12_CALC_umol_yearMEAN = mean(FLUX_W12_CALC_umol15min_dayAve, na.rm = TRUE)
  )


WL_df_extrapolate_yearSUMMARY$FLUX_W12_umol_year <- WL_df_extrapolate_yearSUMMARY$FLUX_W12_umol_yearMEAN *365

WL_df_extrapolate_yearSUMMARY$FLUX_W12_CALC_umol_year <- WL_df_extrapolate_yearSUMMARY$FLUX_W12_CALC_umol_yearMEAN *365

WL_df_extrapolate_yearSUMMARY <- WL_df_extrapolate_yearSUMMARY[c("Wetland","FLUX_W12_umol_year","FLUX_W12_CALC_umol_year")]

#melt data
melt.WL_df_extrapolate_yearSUMMARY<-melt(WL_df_extrapolate_yearSUMMARY, id=c("Wetland"))
```

#same thing for ch4
```{r   summary tables ch4, echo=FALSE}

WL_df_extrapolate_daySUMMARYch4 <- WL_df_extrapolate%>%
  group_by(Date,Wetland)%>% 
  summarise(
    FLUXch4_W12_CALC_umol15min_dayAve = mean(FLUXch4_W12_CALC_umol_15min, na.rm = TRUE),
  )

WL_df_extrapolate_yearSUMMARY <- WL_df_extrapolate_daySUMMARYch4%>%
  group_by(Wetland)%>% 
  summarise(
    FLUXch4_W12_CALC_umol_yearMEAN = mean(FLUXch4_W12_CALC_umol15min_dayAve, na.rm = TRUE)
  )


WL_df_extrapolate_yearSUMMARY$FLUXch4_W12_CALC_umol_year <- WL_df_extrapolate_yearSUMMARY$FLUXch4_W12_CALC_umol_yearMEAN *365


WL_df_extrapolate_yearSUMMARYch4 <- WL_df_extrapolate_yearSUMMARY[c("Wetland","FLUXch4_W12_CALC_umol_year")]


melt.WL_df_extrapolate_yearSUMMARYch4<-melt(WL_df_extrapolate_yearSUMMARYch4, id=c("Wetland"))


```
```{r   play with units, echo=FALSE}
melt_all <- rbind(melt.WL_df_extrapolate_yearSUMMARYch4,melt.WL_df_extrapolate_yearSUMMARY)

melt_all$value_gC <- melt_all$value * 10^-6 * 12

```



#plot
```{r   plot data, echo=FALSE}
p1 <- ggplot(data = WL_df_extrapolate, aes(x = DateTime, y = CH4_BIC_W12_log)) + 
  geom_point() 
p1+facet_wrap(~Wetland)
library(plotly)
plot_ly(data=WL_df_extrapolate%>%filter(Wetland=="Wetland02"), x = ~DateTime, y = ~CH4_BIC_W12)#%>%add_markers(size=1)

p1<-ggplot(data=WL_df_extrapolate_yearSUMMARY, aes(x=Wetland, y=log(FLUX_AIC_noW12_umol_year))) +
  geom_bar(stat="identity")

p2<-ggplot(data=melt.WL_df_extrapolate_yearSUMMARY%>%filter(variable!="FLUX_W12_umol_year")
           , aes(x=Wetland, y =value,fill=variable)) +
  geom_bar(stat="identity", position=position_dodge())

p3<-ggplot(data=melt.WL_df_extrapolate_yearSUMMARYch4, aes(x=Wetland, y=value,fill=variable)) +
  geom_bar(stat="identity", position=position_dodge())



p4<-ggplot(data=melt_all%>%filter(variable!="FLUX_W12_umol_year"), aes(x=Wetland, y=log(value),fill=variable)) +
  geom_bar(stat="identity", position=position_dodge())


```


```{r final bar plot, echo=FALSE}
library(MASS) # to access Animals data sets
library(scales) # to access break formatting functions
p4<-ggplot(data=melt_all%>%filter(variable!="FLUX_W12_umol_year"), aes(x=Wetland, y=log(value),fill=variable)) +
  geom_bar(stat="identity", position=position_dodge())

#sort by mean surface area
size_sum <- WL_df_extrapolate %>%
  group_by(Wetland)%>% 
  summarise(
    SA_mean = mean(surface_area_m2, na.rm = TRUE))
#join to melt data
melt_all <- full_join(melt_all,size_sum,by="Wetland")

melt_all$name.code <- paste("W",as.numeric(gsub("\\D", "", melt_all$Wetland)))
library(stringr)
melt_all$name.code <- str_replace_all(melt_all$name.code, " ", "")

#
p4<-ggplot(data=melt_all %>%filter(variable!="FLUX_W12_umol_year"), aes(x=factor(name.code, level=c('W9', 'W11', 'W10', 'W8','W6','W4','W7','W5','W3','W2','W12','W1')), y=value_gC,fill=variable)) +
  geom_bar(stat="identity", colour="black"
           , position=position_dodge()
           )+
    scale_fill_discrete(name = "", labels = c(expression('gC as CH'[4]), expression('gC as CO'[2]))) +
  xlab('Wetland') + ylab('Yearly Emissions') +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  theme_bw() +
  theme(text=element_text(size=18)) +
  theme(
    axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black")
  )+
  theme(text=element_text(size=25))

p4 + annotation_logticks() 

```

```{r visualize, echo=FALSE}

M_k_W12 <- lmer(k_m.d ~ 
                  Water_minus_air_Temp+ 
                  (1 |Wetland), data =df_1,REML = FALSE)

sjPlot::tab_model(M_k_W12, 
                  show.re.var= TRUE, 
                 # pred.labels =c("(Intercept)", "Water/Air temperature difference (c)"),
                  dv.labels= "k (m d^-1)")

sjPlot::tab_model(M_FLUX_W12, 
                  show.re.var= TRUE, 
                #  pred.labels =c("(Intercept)", "Water/Air temperature difference (c)"),
                  dv.labels= "CO2 Flux")
sjPlot::tab_model(M_CO2_W12, 
                  show.re.var= TRUE, 
                 # pred.labels =c("(Intercept)", "Water/Air temperature difference (c)"),
                  dv.labels= "CO2")
sjPlot::tab_model(M_CH4_W12, 
                  show.re.var= TRUE#, 
                 # pred.labels =c("(Intercept)", "Water/Air temperature difference (c)"),
                 # dv.labels= (CH[4]~mu*"mol (m d^-1)")
                 )




WL_df_extrapolate$FLUX_W12_CALC_umol_s

ggplot(WL_df_extrapolate%>%filter(Wetland=="Wetland10"),
       aes(x=DateTime, y=FLUX_W12_CALC_umol_s)) +
  geom_point(size=2, shape=23)


```

