---
title: "Model yearly flux"
author: "Kriddie"
date: "2024-05-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(dplyr)
library(here)
library(lme4)
library(lmerTest)
library(jtools)
library(reshape2)
library(ggplot2)
library(tidyr)
```

## modeling CO2 and CH4 flux

In this markdown I model CO2 and CH4 concentrations using models selected by AICc and BIC methods.
> I am only predicting concentration because I feel like flux is has more uncertainty then concentration, and that way I can model ch4 too.
> I dropped Wetland 12 because it is different from the other sites (lots of veg, uneven border) and also I didn't measure depth so we don't have depth to surface area ratio. It is unfortunate that surface area is strongly collrelated with elevation when I exclude wetland 12
> I dropped surface area as a predictor because it correlates strongly with elevation :(
> I dropped catchement because it simplifies analysis in a data poor data set, and DTW is expected to be a stronger predictor

2. big question is if I should take a mean of k or model k. I'm feeling more and more strongly that I should use mean k because...
> k does not predict concentration
> k is not predicted by and variable (i think? maybe I need to do that again)

2. Model with modeled k instead of mean... cause i don't think it matters much? or should I use mean --- ahhhh
Ok I'm going to just use mean


Also added in this version is conversion of k from co2 to ch4, as found here: Raymond et al. 2012
https://aslopubs.onlinelibrary.wiley.com/doi/full/10.1215/21573689-1597669

k(gas1)/k(gas2) = (sc(gas1)/sc(gas2))^-n
because we are doing ponds, n = 2/3
Sc: Schmidt number temperature dependencies -- using Wanninkhof(1992) as reported in linked citation above
*Update*
We are now using numbers reported in Wanninkhof (2014)
    
  T is in degree celcius




#Buid time series data frame

```{r build dataframe}
#here are the factors that were selected as predictors of CO2 and CH4
#1. Watertemp_c 
#2. waterTemp_c_yearly
#3. log(WS_area_minus_pond)
#4. percent_DTW
#5. Elevation_m



WL_df <- read.csv(here::here("Wetlands/WaterLevel_FINAL/WL_Wetland_all_FINAL.csv"))%>%select(DateTime,Station,Baro_kpa,BaroTemp_c,WLTemp_c,depth_ave_m,surface_area_m2,Volumn_m3,SA_to_Vol_ratio)%>%rename(Site=Station)%>%rename(WaterTemp_c=WLTemp_c)
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
WL_df$Site <- gsub(".*_","",WL_df$Site)
WL_df$Date <- as.Date(WL_df$DateTime)

df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))

#Read in data that is consistant per site
df_1 <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))%>%select(Site,waterTemp_c_yearly,WS_area_minus_pond,Elevation_m,percent_DTW)
df_1 <- unique(df_1)

df_2 <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))%>%select(Site,CO2_umol.L,CH4_umol.L,K600)

df_3 <- df_2%>%group_by(Site)%>%summarise(
  CO2_umol.L_mean = mean(CO2_umol.L,na.rm=TRUE),
  CH4_umol.L_mean = mean(CH4_umol.L,na.rm=TRUE),
)

K600_m.day.median = median(df$K600,na.rm=TRUE)

#bind data 
df_full <- full_join(WL_df,df_1,by="Site")
df_full <- full_join(df_full,df_3,by="Site")
##add gas transfer velocity
df_full$K600_m.day.median <- K600_m.day.median
df_full$K600_m.sec <- df_full$K600_m.day.median / (60*60*24)

#calculate schmidts number based on temperature Wanninkhof 2014
df_full$Sc_ch4 <- 1909.4 + -120.78*df_full$WaterTemp_c - .0805681*(df_full$WaterTemp_c)^2 + .00065777*(df_full$WaterTemp_c)^3

df_full$Sc_co2 <- 1923.6 - 125.06*df_full$WaterTemp_c + 4.3773*(df_full$WaterTemp_c)^2 - 0.085681*(df_full$WaterTemp_c)^3 + 0.00070284 * (df_full$WaterTemp_c)^4



## convert to k for co2 and k for ch4
df_full$k_co2_m.sec <-  df_full$K600_m.sec / ((600/df_full$Sc_co2)^(-.57))
df_full$k_ch4_m.sec <-  df_full$K600_m.sec / ((600/df_full$Sc_ch4)^(-.57))

```

#henry's constant


```{r henry's constant}

df_full$air_pressure_atm <- df_full$Baro_kpa / 101.3 #convert kpa to atm
df_full$water_pressure_atm <- df_full$Baro_kpa / 101.3 + 0.000967841

#######
##CO2##
#######

df_full$pCO2_air_ppm <- 418.53 # 2022 average manoa
#adjust henry to temp: KH = KH(STP) x exp(D(1/T-1/T(STP)))
#use constants in  	Burkholder et al. (2019) and convert to desired units
#  k°H (mol/(kg*bar) = mol/l/atm
#d(ln(kH))/d(1/T) (K)
kH_STP_mol.l.atm = .035*1/0.986923
D_K = 2400 
T_STP_K = 298.15

df_full$KH_mol.l.atm_CO2 <- kH_STP_mol.l.atm * exp(D_K*(1/(df_full$WaterTemp_c+273.15) - 1/T_STP_K))

df_full$KH_mol.m3.atm_CO2 <- df_full$KH_mol.l.atm_CO2 * 1000

df_full$CO2_air_atm <- df_full$air_pressure_atm * df_full$pCO2_air_ppm *10^-6
df_full$CO2_sat_mol.m3 <- df_full$CO2_air_atm*df_full$KH_mol.m3.atm_CO2 
#######
##CH4##
######

df_full$CH4_air_ppb <- 1910.97 #Ambient CH4 concentration ppb	1910.97 from Manoa

#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
df_full$KH_mol.L.atm_CH4 <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(df_full$WaterTemp_c+273.15)-1/T_STP_K))

df_full$KH_mol.m3.atm_CH4 <- df_full$KH_mol.L.atm_CH4 * 1000


df_full$CH4_air_atm <- df_full$air_pressure_atm * df_full$CH4_air_ppb * 10^-9
df_full$CH4_sat_mol.m3 <- df_full$CH4_air_atm*df_full$KH_mol.m3.atm_CH4

```

## Write flux models AIc and BIC,  without wetland 12
#time to extrapolate
#model results
df_1 <- df%>%filter(Site!="Wetland12")

#(Intercept), scale(waterTemp_c_yearly), scale(percent_DTW), scale(Elevation_m)


M_AICc_CH4 <- lmer(log(CH4_umol.L) ~ 
                  scale(waterTemp_c_yearly)+
                scale(percent_DTW) +
                scale(Elevation_m) +
                  (1 |Site), data =df_1,REML = FALSE)
sum_AICc_CH4 <- summary(M_AICc_CH4)
sum_AICc_CH4_coefficients <- sum_AICc_CH4$coefficients
modelPerformance(M_AICc_CH4)

#without wetland 12
#(Intercept), scale(waterTemp_c_yearly), scale(percent_DTW), scale(Elevation_m)

M_BIC_CH4 <- lmer(log(CH4_umol.L) ~ 
                 scale(waterTemp_c_yearly)+
                scale(percent_DTW) +
                scale(Elevation_m) +
                  (1 |Site), data =df_1,REML = FALSE)
sum_BIC_CH4 <- summary(M_BIC_CH4)
sum_BIC_CH4_coefficients <- sum_BIC_CH4$coefficients
modelPerformance(M_BIC_CH4)

#CO2 AICc 
#AICc: (Intercept), scale(Watertemp_c), scale(waterTemp_c_yearly), scale(log(WS_area_minus_pond)), scale(percent_DTW), scale(Elevation_m)

M_AICc_CO2 <- lmer(log(CO2_umol.L) ~ 
                  scale(Watertemp_c)+ 
                  scale(waterTemp_c_yearly) +
                 scale(log(WS_area_minus_pond)) +
                    scale(percent_DTW) +
                  scale(Elevation_m) +
                  (1 |Site), data =df_1,REML = FALSE)
sum_AICc_CO2 <- summary(M_AICc_CO2)
sum_AICc_CO2_coefficients <- sum_AICc_CO2$coefficients
modelPerformance(M_AICc_CO2)

#CO2 BIC
#(Intercept), scale(waterTemp_c_yearly), scale(log(WS_area_minus_pond)), scale(percent_DTW), scale(Elevation_m)


M_BIC_CO2 <- lmer(log(CO2_umol.L) ~ 
                scale(waterTemp_c_yearly) +
                scale(log(WS_area_minus_pond)) +
                scale(percent_DTW) +
                scale(Elevation_m) +
                  (1 |Site), data =df_1,REML = FALSE)
sum_BIC_CO2 <- summary(M_BIC_CO2)
sum_BIC_CO2_coefficients <- sum_BIC_CO2$coefficients
modelPerformance(M_BIC_CO2)



```{r models, echo=FALSE}

##
#cH4 WITHOUT wetland 12
df_model <- df%>%filter(Site!="Wetland12")

#(Intercept),   scale(waterTemp_c_yearly)+ scale(percent_DTW) + scale(Elevation_m) +

M_AICc_CH4 <- lmer(log(CH4_umol.L) ~ 
                   waterTemp_c_yearly+
                percent_DTW +
                Elevation_m +
                  (1 |Site), data =df_model,REML = FALSE)
sum_df <- summary(M_AICc_CH4)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_AICc_CH4)$Site[1]
intercept_df$Site <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Site")
df_full <- left_join(df_full,intercept_df,by="Site")

df_full$M_AICc_CH4 <- exp(
  df_full$intercept +
   df_full$waterTemp_c_yearly * coeff_df[2,"Estimate"] +
    df_full$percent_DTW * coeff_df[3,"Estimate"] +
    df_full$Elevation_m * coeff_df[4,"Estimate"] 
  )

df_full$intercept <- NULL


#without wetland 12
#(same as CH4 AICc)
#(Intercept),   scale(waterTemp_c_yearly)+ scale(percent_DTW) + scale(Elevation_m) +
M_BIC_CH4 <- lmer(log(CH4_umol.L) ~ 
                 waterTemp_c_yearly+
                percent_DTW +
                Elevation_m +
                  (1 |Site), data =df_model,REML = FALSE)

sum_df <- summary(M_BIC_CH4)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_BIC_CH4)$Site[1]
intercept_df$Site <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Site")
df_full <- left_join(df_full,intercept_df,by="Site")

df_full$M_BIC_CH4 <- exp(
  df_full$intercept +
  df_full$waterTemp_c_yearly * coeff_df[2,"Estimate"] +
    df_full$percent_DTW * coeff_df[3,"Estimate"] +
    df_full$Elevation_m * coeff_df[4,"Estimate"]
  )

df_full$intercept <- NULL

#CO2 AICc 
#AICc: (Intercept),  scale(Watertemp_c)+ scale(waterTemp_c_yearly) +scale(log(WS_area_minus_pond)) +scale(percent_DTW) + scale(Elevation_m) 

M_AICc_CO2 <- lmer(log(CO2_umol.L) ~ 
                  Watertemp_c + 
                  waterTemp_c_yearly +
                 log(WS_area_minus_pond) +
                    percent_DTW +
                  Elevation_m +
                  (1 |Site), data =df_model,REML = FALSE)

sum_df <- summary(M_AICc_CO2)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_AICc_CO2)$Site[1]
intercept_df$Site <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Site")
df_full <- left_join(df_full,intercept_df,by="Site")

df_full$M_AICc_CO2 <- exp(
  df_full$intercept +
   df_full$WaterTemp_c * coeff_df[2,"Estimate"] +
    df_full$waterTemp_c_yearly * coeff_df[3,"Estimate"] +
    log(df_full$WS_area_minus_pond) * coeff_df[4,"Estimate"] +
        df_full$percent_DTW * coeff_df[5,"Estimate"] +
    df_full$Elevation_m * coeff_df[6,"Estimate"]
  )

df_full$intercept <- NULL

#BIC, without elevation: (Intercept),  waterTemp_c_yearly + log(WS_area_minus_pond) + percent_DTW + Elevation_m

M_BIC_CO2 <-lmer(log(CO2_umol.L) ~ 
                waterTemp_c_yearly +
                log(WS_area_minus_pond) +
                percent_DTW +
                Elevation_m +
                  (1 |Site), data =df_model,REML = FALSE)

sum_df <- summary(M_BIC_CO2)
coeff_df <- as.data.frame(sum_df$coefficients)
coeff_df$effects <- rownames(coeff_df)

intercept_df <- coef(M_BIC_CO2)$Site[1]
intercept_df$Site <- rownames(intercept_df)
colnames(intercept_df) <- c("intercept","Site")
df_full <- left_join(df_full,intercept_df,by="Site")

df_full$M_BIC_CO2 <- exp(
  df_full$intercept +
    df_full$waterTemp_c_yearly * coeff_df[2,"Estimate"] +
    log(df_full$WS_area_minus_pond) * coeff_df[3,"Estimate"] +
      df_full$percent_DTW * coeff_df[4,"Estimate"] +
    df_full$Elevation_m * coeff_df[5,"Estimate"]
  )

df_full$intercept <- NULL


```

#calc flux (umol/(m2*sec))

```{r flux (umol/(m2*sec)), echo=FALSE}
#multiply by 1000 to convert 1/L to 1/m3
#multiply by 10^6 to convert mol to umol

df_full$F_umol.m2.s_AICc_CO2 <- df_full$k_co2_m.sec * (df_full$M_AICc_CO2*1000 - df_full$CO2_sat_mol.m3*10^6)
df_full$F_umol.m2.s_BIC_CO2 <- df_full$k_co2_m.sec * (df_full$M_BIC_CO2*1000 - df_full$CO2_sat_mol.m3*10^6)
df_full$F_umol.m2.s_mean_CO2 <- df_full$k_co2_m.sec * (df_full$CO2_umol.L_mean*1000 - df_full$CO2_sat_mol.m3*10^6)

df_full$F_umol.m2.s_AICc_CH4 <- df_full$k_ch4_m.sec * (df_full$M_AICc_CH4*1000 - df_full$CH4_sat_mol.m3*10^6)
df_full$F_umol.m2.s_BIC_CH4 <- df_full$k_ch4_m.sec * (df_full$M_BIC_CH4*1000 - df_full$CH4_sat_mol.m3*10^6)
df_full$F_umol.m2.s_mean_CH4 <- df_full$k_ch4_m.sec * (df_full$CH4_umol.L_mean*1000 - df_full$CH4_sat_mol.m3*10^6)


```

#calc flux (umole/sec)
```{r flux (umol/(sec)), echo=FALSE}
df_full$F_umol.s_AICc_CO2 <-  df_full$F_umol.m2.s_AICc_CO2 * df_full$surface_area_m2
df_full$F_umol.s_BIC_CO2 <-  df_full$F_umol.m2.s_BIC_CO2 * df_full$surface_area_m2
df_full$F_umol.s_mean_CO2 <-  df_full$F_umol.m2.s_mean_CO2 * df_full$surface_area_m2

df_full$F_umol.s_AICc_CH4 <-  df_full$F_umol.m2.s_AICc_CH4 * df_full$surface_area_m2
df_full$F_umol.s_BIC_CH4 <-  df_full$F_umol.m2.s_BIC_CH4 * df_full$surface_area_m2
df_full$F_umol.s_mean_CH4 <-  df_full$F_umol.m2.s_mean_CH4 * df_full$surface_area_m2

```

#write out dataframe (this is going to be really big)
```{r write out, echo=FALSE}

write.csv(df_full,here::here("ProcessedData/modeled_GHG_df.csv"))

```




