---

title: "CO2_EC"
author: "Kayla Emerson"
date: "6/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About
<<<<<<< HEAD
In this file I clean and collect CO2 data collected at Cayambe Coca, EC on June 6, 2022

### We start by reading in an then cleaning data, file 

```{r cars}
## I'm not sure that we need this code chunk
#setwd(here::here("Injections/2022-06-06/CO2"))
## Read files into R

#File_name <- "Inj_CO2_xn10m_2022-06-06.csv"

#CO2Data <- read.csv(File_name, skip=6, header = TRUE)
#CO2Data=CO2Data[,1:3]
#colnames(CO2Data) <- c("Date","Time","ppm")

#DOWNLOAD DATA using UNC computer
#CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")

#DOWNLOAD DATA using USFQ computer
#CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%y %H:%M:%S", tz = "UTC")


#Clean data
#CO2Data <- CO2Data %>% filter(DateTime < as.POSIXct("2021-10-02 21:45:00", tz = "UTC") | DateTime > as.POSIXct("2021-10-20 13:15:00", tz = "UTC"))


#plot pressure
#plot_ly(CO2_02%>% filter(ppm <  5000), x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'lines+markers')
#plot_ly(CO2_03, x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'lines+markers')
#plot_ly(CO2Data, x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'lines+markers')

```



## Do loop to read in csv files and compile them together

=======

In this file I clean and collect CO2 data collected at Cayambe Coca, EC salt injection from June 6, 2022

### We start by reading in an then cleaning data, file 

>>>>>>> f2bd05646d9a1cd712745f9286e135e85a07adaa
```{r pressure, echo=FALSE}
setwd(here::here("Injections/2022-06-06/CO2"))

all_files=list.files(pattern=".csv")        #pulls out the csv files from WL folder in HOBOware folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)


#shorten site name by removing underscores
sites_rp = sapply(strsplit(all_files, "_"), function(x) x[3])

site_names=unique(sites_rp) #creates list of site names for following loop



#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=7, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=7, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}
```

## Clean up CO2 data- remove everything after 16:00 on 2022-06-06
<<<<<<< HEAD
We flipped station 10m and 50m because they were most likely mixed up when downloading data. We are also not analyzing the viasala data from 100m because it the CO2 slug did not make it through. But, the data is here if we want to use it at some point. 

```{r pressure, echo=FALSE}
# 
=======
This is when we stopped collecting data

```{r pressure, echo=FALSE}
>>>>>>> f2bd05646d9a1cd712745f9286e135e85a07adaa
xn10m = filter(xn10m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

x10m = filter(x10m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

x50m = filter(x50m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

#x100m = filter(x100m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

# Notes from the notebook to decipher which viasala box was at each station

# x50m is an old Viasala labeled box 1 
# x10m is an old viasala labeled box 6
# xn10m is a new viasala labeled box 1

```

## Correct viasalas temperature and pressure with HOBO data for the time period we collected data
```{r check CO2 data plot, echo=FALSE}

setwd(here::here("Injections/2022-06-06"))

# first, read in WL hobo at -10m 
waterlevel_n10 <- read_csv("TEMP_xn10m_2022-06-06")

# format DateTime in WL 


# correct kpa to hpa 


#full_join to join co2 data to wl by datetime

# Old Vaisala adjust for tempo and pressure
#df_old$adjusted_ppm <- df_old$ppm * (1 + (1013 - df_old$Total_hPa) * 0.0015) * (1 - (25 - df_old$WLTemp_c) * 0.003)

#new vaisala adjust for peressure ONLY

#df_new$adjusted_ppm <- (df_new$ppm)* (1 + (1013 - df_new$Total_hPa) * 0.0015) 
```
## Plot CO2 for Viasala @ -10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(xn10m,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Viasala @ 10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(x10m,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```




## Plot CO2 for 50m Viasala
```{r check CO2 data plot, echo=FALSE}
##check data
plot_ly(x50m,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 
```


<<<<<<< HEAD
## Plot CO2 for Viasala @50m
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(x50m,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Viasala @ 100m
This is optional- we aren't analyzing this data for this injection bc it never reached 100m
=======
## Plot CO2 for 100m Viasala
>>>>>>> f2bd05646d9a1cd712745f9286e135e85a07adaa
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(x100m,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}

# join data frames to make plotting easier

df_new <- rbind(xn10m, x10m, x50m)

# use facet wrap to plot multiple stations

together_plot <- ggplot(df_new, aes(DateTime, ppm, color = Station)) +
  geom_point(size = 2) +
  xlab(NULL) +
  ylab(NULL)

together_plot + facet_wrap(~Station, ncol= 3, scales = "free")

together_plot

```



## Data Cleaning -- need to work on this section and correct for pressure and temp
Use the data from vaisala correction 

```{r plot, echo=FALSE}

```


## Finding the mean for before, during, and after the plateau
NEED to fix this section
FIND mean before plateau, during the plateau, and after the plateau
EXPORT to excel somehow to make a nice table or something 

```{r plot, echo=FALSE}

# find average for each station before plateau

preplat_n10 <- filter(xn10m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:15:00", tz = "UTC"))
preplat_10 <- filter(x10m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:15:00", tz = "UTC"))
preplat_50 <- filter(x50m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:15:00", tz = "UTC"))

#calculate mean
preplatmeann10m = mean(preplat_n10$ppm)
preplatmean10m = mean(preplat_10$ppm)
preplatmean50m = mean(preplat_50$ppm)

# find average of plateaus for each station
<<<<<<< HEAD
=======

>>>>>>> f2bd05646d9a1cd712745f9286e135e85a07adaa
### Change data frame, date and wanted time frame as needed 
plat_n10 <- filter(xn10m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))
plat_10 <- filter(x10m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))
plat_50 <- filter(x50m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))

#now find the mean of this filtered subset
platmeann10m = mean(plat_n10$ppm)
platmean10m = mean(plat_10$ppm)
platmean50m = mean(plat_50$ppm)

# find average at each station after the slug

#first, clean up data by focusing on wanted time
postplat_n10 <- filter(xn10m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))
postplat_10 <- filter(x10m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))
postplat_50 <- filter(x50m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))

#find mean of post plateau
postplatmeann10m = mean(postplat_n10$ppm)
postplatmean10m = mean(postplat_10$ppm)
postplatmean50m = mean(postplat_50$ppm)

```



