---
---
title: "CO2_EC"
author: "Kayla Emerson"
date: "6/21/2022"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About
In this file I clean and collect CO2 data collected at Cayambe Coca, EC on June 20, 2022

### We start by reading in an then cleaning data, file 



## Do loop
pulls out CO2 files from injection and merges them together; also corrects time and date 

```{r pressure, echo=FALSE}

setwd(here::here("Injections/2022-06-20/CO2"))

all_files=list.files(pattern=".csv")        #pulls out the csv files from WL folder in HOBOware folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)


#shorten site name by removing underscores
sites_rp = sapply(strsplit(all_files, "_"), function(x) x[3])

site_names=unique(sites_rp) #creates list of site names for following loop




#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}


```


## Clean up CO2 data- if necessary but for this injection we downloaded vaisalas right away
```{r pressure, echo=FALSE}
#xn10m = filter(xn10m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

#x10m = filter(x10m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

#x50m = filter(x50m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

#x100m = filter(x100m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

# Now join all sites into a singular data frame so it is easier to analyze 
df_new <- rbind(xn10m, x0m, x15m, x30m)
```


## Notes from the notebook to decipher which viasala box was at each station
 
-10m was R37297 K600 Old
0m was Box 1 New
** had some issues because CO2 was so high
15m was Box 3 New
30m was R37301 Station 3 old 

## Correct viasalas temperature and pressure with HOBO data for the time period we collected data
```{r check CO2 data plot, echo=FALSE}

setwd(here::here("Injections/2022-06-20"))


# first, read in WL hobo at -10m 
waterlevel_n10 <- read.csv("Injection_Temp_xn10_2022-06-20.csv", skip = 1)
waterlevel_n10 <- waterlevel_n10[,c(2:4)]
colnames(waterlevel_n10) <- c("DateTime", "WL_Pressure", "Temp")

# format DateTime in WL 
waterlevel_n10$DateTime <- as.POSIXct(paste(waterlevel_n10$Date, waterlevel_n10$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")

# correct kpa to hpa 
##1 kPa = 10 hPa
##1 kPa = 0.101972 m
waterlevel_n10$WL_Pressure <- waterlevel_n10$WL_Pressure * 10

#full_join to join CO2 data to WL by datetime
#df_corr <- full_join(df_new, waterlevel_n10, by = "DateTime" )
df_corr <- right_join(df_new, waterlevel_n10, by = "DateTime" )

# clean data <- remove NA values bc vaisala reads every 1s and WL reads ever 10s
df_corr <- na.omit(df_corr) 

# create a new column for adjusted ppm
df_corr$adjusted_ppm <- 0
df_corr$adjusted_ppm <- as.numeric(df_corr$adjusted_ppm)
df_corr$ppm <- as.numeric(df_corr$ppm)

```

## Correct old Vaisalas 
Old vaisalas need to be corrected for temperature and pressure 
Also need to be corrected for individual calibration -- calibration equations are from vaisalacalibration csv
-10m  and 30m were old

```{r check CO2 data plot, echo=FALSE}

# Make a new data frame from df_corr but just with old vaisalas

df_oldv <- df_corr %>% 
      filter(Station =='xn10m' | Station == 'x30m')

# Now correct the adjusted ppm 
df_oldv$adjusted_ppm <- df_oldv$ppm * (1 + (1013 - df_oldv$WL_Pressure) * 0.0015) * (1 - (25 - df_oldv$Temp) * 0.003)

# Now correct for individual vaisala calibration 

# x30m was an old viasala labeled R37301 Station 3

df_x30m <- df_oldv %>% 
      filter(Station =='x30m')

df_x30m$adjusted_ppm <-  (df_x30m$adjusted_ppm * 1.08208) - 231.66433

# xn10m was an old Viasala labeled R37297 K600

df_xn10m <- df_oldv %>% 
      filter(Station =='xn10m')

df_xn10m$adjusted_ppm <- (df_xn10m$adjusted_ppm * 1.06933) - 105.52898

```

## Correct new Vaisalas
New vaisalas need to be corrected for just pressure 
Also need to be corrected for individual calibaration
0m and 15m were new 
```{r check CO2 data plot, echo=FALSE}
# Make a new data frame from df_corr but just with new vaisalas
df_newv <- df_corr %>% 
      filter(Station =='x0m'| Station == 'x15m')

# Now correct the adjusted ppm 
df_newv$adjusted_ppm <- (df_newv$ppm * 2 )* (1 + (700 - df_newv$WL_Pressure) * 0.0015)

# Now correct for individual vaisala calibration

# x0m a new viasala labeled box 1
df_x0m <- df_newv %>% 
      filter(Station =='x0m')

df_x0m$adjusted_ppm <- (df_x0m$adjusted_ppm * 1.00054) - 65.15813

# x15m was labeled Box 3 New
df_x15m <- df_newv %>% 
      filter(Station =='x15m')

df_x15m$adjusted_ppm <- (df_x15m$adjusted_ppm * 1.05036) - 6.27667

```


## Plot CO2 for Viasala @ -10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_xn10m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```


## Plot CO2 for Viasala @ 0m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x0m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```


## Plot CO2 for Viasala @ 15m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x15m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```


## Plot CO2 for Viasala @30m
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x30m,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```



## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}
# join data frames to make plotting easier

df_plot <- rbind(df_xn10m, df_x0m, df_x15m, df_x30m)

# use facet wrap to plot multiple stations

together_plot <- ggplot(df_plot, aes(DateTime, adjusted_ppm, color = Station)) +
  geom_point(size = 2) +
  xlab(NULL) +
  ylab(NULL)

together_plot + facet_wrap(~Station, ncol= 3, scales = "free")

together_plot

```



## Data Cleaning -- need to work on this section and correct for pressure and temp
CORRECT FOR PRESSURE AND TEMPERATURE - HAVE NOT DONE THIS YET AS OF 2022-06-21

more notes for this specific injection 
 
vaisala @ -10 m 
R37297 K600 old 

vaisala @ 0 m
Box 1 New

vaisala @ 15m 
Box 3 new

vaisala @ 30m 
R37391 Station 3

```{r plot, echo=FALSE}

# find average of plateaus for each station

# testing to see if mean function works 
mean_test <- mean(df_new$ppm)

#focus on just one station; -10m
mean_two <- mean(xn10m$ppm)

#now figure out how to only focus on data after 11:30
### Change data frame, date and wanted time frame as needed 
cleaned_n10 <- filter(xn10m, DateTime >= as.POSIXct("2022-05-26 11:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-05-26 11:40:00", tz = "UTC"))

#now clean up all of the stations
cleaned_0 <- filter(x0m, DateTime >= as.POSIXct("2022-05-26 11:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-05-26 11:40:00", tz = "UTC"))
cleaned_50 <- filter(x50m, DateTime >= as.POSIXct("2022-05-26 11:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-05-26 11:40:00", tz = "UTC"))

#now find the mean of this filtered subset
meann10m = mean(cleaned_n10$ppm)
mean0m = mean(cleaned_0$ppm)
mean50m = mean(cleaned_50$ppm)


```


