---
title: "Figures Rmarkdown"
author: "K. M. Whitmore"
date: "2025-02-11"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

#load library

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(lubridate)
library(dplyr)
library(ggplot2)
library(reshape2)
library("ggpubr")
library(rstatix)
library(devtools)
library(PMCMRplus)
library(lme4)
library(lmerTest)
library(jtools)
library(extraoperators)
library(JWileymisc)
library(multilevelTools)
library(broom)
library(tidyr)
library(stringr)
library(scales)
library(ggbreak)
library(viridis)
library(cowplot)
library(zoo)
```

#About
This Rmarkdown file contains all code needed to produce figures in the publication:
"Water Temperature and Catchment Characteristics Drive Variance in Greenhouse Gas Emissions from Small Ponds in a Peatland-Rich, High-Altitude Tropical Ecosystem"

*note*
The here package sets your working directory to the folder that contains your r project
https://here.r-lib.org/allows

#Figure 2

```{r figure 2,echo=FALSE}


WL_df <- read.csv(here::here("PondPaper_Repository/continuous_data.csv"))
#we don't have depth for wetland, we will use water level to plot
WL_df[WL_df$Site_ID=="Wetland",]$depth_ave_m <- WL_df[WL_df$Site_ID=="Wetland",]$WaterLevel_m
WL_df <- WL_df%>%select(DateTime,Site_ID,surface_area_m2,depth_ave_m)
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

#read in elevation data to merge with WL
df <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))%>%select(Site_ID,Elevation_m)
df <- unique(df)

Summary_df <- WL_df%>%
 group_by(Site_ID)%>%
  summarise(
    SA_max = max(surface_area_m2, na.rm = TRUE),
    SA_min = min(surface_area_m2, na.rm = TRUE),
    SA_mean = mean(surface_area_m2, na.rm = TRUE),
    depth_max = max(depth_ave_m, na.rm = TRUE),
    depth_min = min(depth_ave_m, na.rm = TRUE),
    depth_mean = mean(depth_ave_m, na.rm = TRUE)
  )

Summary_df <- full_join(Summary_df,df,by="Site_ID")

p2 <- ggplot(data=Summary_df,aes(x=SA_mean,y=depth_mean, fill=Elevation_m)) +
  geom_point(shape=22,size=5) +
  geom_segment(aes(x = SA_min, y = depth_mean, xend = SA_max, yend = depth_mean), color="grey25",linewidth=.5) +
  geom_segment(aes(x = SA_mean, y = depth_min, xend = SA_mean, yend = depth_max), color="grey25",linewidth=.5) +
  scale_y_log10() + scale_x_log10() +
  theme_classic() +
  theme(text=element_text(size=20)) + guides(fill=guide_legend(title="Elevation (m)")) +
  theme(
    axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black")) +
  xlab(expression('Surface Area ('~m^2~')')) + ylab("Depth (m)") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))
)

p3 <- p2 + annotation_logticks(
  base = 10,
  sides = "bl",
  outside = TRUE,
  scaled = TRUE,
  short = unit(0.1, "cm"),
  mid = unit(0.2, "cm"),
  long = unit(0.3, "cm"),
  colour = "black",
  linewidth = 0.5,
  linetype = 1,
  alpha = 1,
  color = "grey40"
) + coord_cartesian(clip = "off")

```

# Figure 3

```{r Figure 3, echo=FALSE}
 
df <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))

p.ch4 <- ggplot(df,aes(x=reorder(Site_ID,Elevation_m,median,decreasing = TRUE),y=pCH4_ppm)) +
   geom_point(size=2) +
  stat_summary(geom = "point", fun = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  scale_y_log10() +
   ylab(expression(italic(p)~CH[4] ~'(ppm)')) + xlab("") +
  theme_classic2(base_size = 18) +
  theme(axis.text.x=element_blank()) +
  annotate("text", x = "S1", y = 15000, label = "A") +
  annotate("text", x = "S2", y = 15000, label = "A") +
  annotate("text", x = "S3", y = 15000, label = "AB") +
  annotate("text", x = "S4", y = 15000, label = "CD") +
  annotate("text", x = "S5", y = 15000, label = "BC") +
  annotate("text", x = "S6", y = 15000, label = "BC") +
  annotate("text", x = "S7", y = 15000, label = "B") +
  annotate("text", x = "S8", y = 15000, label = "CD") +
  annotate("text", x = "Wetland", y = 15000, label = "ABC") +
  annotate("text", x = "S10", y = 15000, label = "D") +
  annotate("text", x = "S11", y = 15000, label = "D") +
  annotate("text", x = "S12", y = 15000, label = "CD")



p.co2 <- ggplot(df,aes(x=reorder(Site_ID,Elevation_m,median,decreasing = TRUE),y=pCO2_ppm)) +
   geom_point(size=2) +
  stat_summary(geom = "point", fun = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  scale_y_log10() +
  ylab(expression(italic(p)~CO[2] ~'(ppm)')) + xlab("Site") +
theme_classic2(base_size = 18) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  annotate("text", x = "S1", y = 15000, label = "AB") + 
  annotate("text", x = "S2", y = 15000, label = "A") +
  annotate("text", x = "S3", y = 15000, label = "ABC") +
  annotate("text", x = "S4", y = 15000, label = "C") +
  annotate("text", x = "S5", y = 15000, label = "ABC") +
  annotate("text", x = "S6", y = 15000, label = "ABC") +
  annotate("text", x = "S7", y = 15000, label = "ABC") +
  annotate("text", x = "S8", y = 15000, label = "BCD") +
  annotate("text", x = "Wetland", y = 15000, label = "DE") +
  annotate("text", x = "S10", y = 15000, label = "E") +
  annotate("text", x = "S11", y = 15000, label = "ED") +
  annotate("text", x = "S12", y = 15000, label = "E")



fig3 <- ggarrange(p.ch4, p.co2, labels = c("A", "B"),ncol = 1, nrow = 2)

```


# Figure 4

```{r figure 4, echo=FALSE}

gavi_df <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))%>%filter(Site_ID=="Wetland")%>%select(Site_ID, Date,AirPressure_kPa,WaterTemp_c,pCO2_ppm, pCH4_ppm,CH4_umol.L, CO2_umol.L)%>%rename(Site=Site_ID)
gavi_df$Date <- as.Date(gavi_df$Date,format = "%Y-%m-%d")
gavi_df$Location <- "center"
gavi_df$Site2 <- NA
gavi_df$Lat <- -0.328064
gavi_df$Lon <- -78.200203
 
drone_GHG <- read.csv(here::here("PondPaper_Repository/wetland_GHG_data.csv"))
###

df <- rbind(gavi_df,drone_GHG)
#summerize
df_summ <- df%>%group_by(Site)%>%drop_na(pCH4_ppm)%>%summarise(
  pCH4_ave = mean(pCH4_ppm,rm.na=TRUE),
  pCO2_ave = mean(pCO2_ppm,rm.na=TRUE))

df_melt <- df %>%select(Location,Date,Site2,pCH4_ppm,pCO2_ppm)%>%
    pivot_longer(
      cols = -c(Location,Date,Site2),  # Columns to be melted
      names_to = "gas",      # Name of the new key column
      values_to = "ppm"         # Name of the new value column
    )
 

fig4 <- ggplot(df_melt,aes(x=gas, y=ppm,fill=Location)) +
  geom_boxplot() +
  geom_point(shape=21,color="black",position = position_jitterdodge(jitter.width = .25, jitter.height = 0, dodge.width = 0.75)) + ylab("") + xlab("") +
  scale_fill_discrete(labels=c("open-water \ntransect","wetland \nmargins")) + 
    scale_x_discrete(labels=c("pCH4_ppm" = expression(paste("CH"[4]~"(ppm)" )), "pCO2_ppm" = expression(paste("CO"[2]~"(ppm)" )))) +
  scale_y_continuous(transform = "log1p",breaks=c(1,10,100,1000,10000)) + theme_bw(base_size = 24) + theme(legend.position="top")

```



# Figure 5

```{r Figure 5, echo=FALSE}

df <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))
df$DateTime <- as.POSIXct(df$DateTime)
df$pCO2_air_uatm <- df$pCO2_air_atm*10^6

CO2_air_max <- max(df$pCO2_air_uatm,na.rm = TRUE)
CO2_air_min <- min(df$pCO2_air_uatm,na.rm = TRUE)
CO2_air_ave <- mean(df$pCO2_air_uatm,na.rm = TRUE)

fig5 <- ggplot(df ,aes(x=pCO2_ppm,y=Flux_CO2_umol.m2.s*10^-6*60*60*24)) + geom_point(aes(fill=Site_ID),shape=21,size=3) +  
   geom_smooth(method='lm', color='black') + guides(fill=guide_legend(title="Site name"))+
  annotate("text",x=8000, y=.001, label=expression(paste(r^2 ," = .77")),size=5) +
  geom_rect(aes(xmin=CO2_air_min, xmax=CO2_air_max, ymin=0, ymax=Inf),fill="red",alpha=.5) +
      ylab(expression(paste("CO"[2] ,"  Evasion (mol ", m^-2," ", d^-1,")"))) +
  xlab(substitute(paste(italic('p'),CO[2], " (ppm)"))) +
  scale_x_continuous(transform = "log10") + scale_y_continuous(transform = "log10") +
  theme_bw(base_size = 18) 


```

# Figure 6

```{r figure 6, echo=FALSE}

df <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))

#mean center variables
gmc <- df %>%
  group_by(Site_ID,Elevation_m,percent_DTW,
           WS_area_minus_pond) %>%
  mutate(gpm_Watertemp_c = mean(WaterTemp_c),
         mean_pCO2_ppm = mean(pCO2_ppm),
         mean_pCH4_ppm = mean(pCH4_ppm),
         WaterTemp_c = WaterTemp_c - gpm_Watertemp_c) %>% 
  ungroup()


xlab <- "Water temperature (°C)"
p.co2 <- ggplot(df,aes(x=WaterTemp_c,y=pCO2_ppm,color = reorder(Site_ID,Elevation_m,median,decreasing = TRUE))) +
  geom_point(size=2)+
  geom_point(data=df,aes(x=WaterTemp_c,y=pCO2_ppm,),shape=1,size=2,color="black")+
  geom_smooth(method='lm',formula = "y ~ x",se=FALSE) +
  geom_point(data=gmc,aes(x=gpm_Watertemp_c,y=mean_pCO2_ppm,fill=Elevation_m),color="black",shape=23,size=4)+
    geom_point(data=gmc,aes(x=gpm_Watertemp_c,mean_pCO2_ppm),shape=3,size=1,color="black") +
    ylab(expression(italic(p)~CO[2] ~'(ppm)')) + xlab(xlab) +
  scale_color_viridis(name="Site",discrete = TRUE) +
  scale_y_continuous(transform="log",breaks=c(300,1000,3000,10000)) +
    theme_bw(base_size = 24) 

p.co2.ele <- ggplot() +
    geom_smooth(data=df,aes(x=Elevation_m,y=pCO2_ppm), method='lm',formula = "y ~ x",se=FALSE,color="black") +
  geom_point(data=df,aes(x=Elevation_m,y=pCO2_ppm,color=reorder(Site_ID,Elevation_m,median,decreasing = TRUE)),size=2) +
  geom_point(data=df,aes(x=Elevation_m,y=pCO2_ppm),shape=1,size=2) +
    ylab(expression(italic(p)~CO[2] ~'(ppm)')) + xlab('Elevation (m)') +
  scale_color_viridis(name="Site",discrete = TRUE) +
  scale_y_continuous(transform="log",breaks=c(300,1000,3000,10000)) +
  theme_bw(base_size = 24)


p.ch4 <- ggplot() + 
  geom_smooth(data=gmc,aes(x=gpm_Watertemp_c,y=mean_pCH4_ppm),method='lm',formula = "y ~ x",se=FALSE,color="black") +
  geom_point(data=df,aes(x=WaterTemp_c,y=pCH4_ppm,color=reorder(Site_ID,Elevation_m,median,decreasing = TRUE)),size=2) +
  geom_point(data=df,aes(x=WaterTemp_c,y=pCH4_ppm),color="black",shape=1, size=2) +
  geom_point(data=gmc,aes(x=gpm_Watertemp_c,y=mean_pCH4_ppm,fill=Elevation_m),shape=23,size=4)+
  geom_point(data=gmc,aes(x=gpm_Watertemp_c,y=mean_pCH4_ppm),color="black",shape=3,size=1)+
  ylab(expression(italic(p)~CH[4] ~'(ppm)')) +
  xlab(xlab) +
  scale_color_viridis(name="Site",discrete = TRUE) +
  scale_y_continuous(transform="log10",breaks = c(1,3,10,30,100,300,1000,3000)) + 
  theme_bw(base_size = 24) +
  theme(legend.box = "horizontal") +
  scale_fill_continuous(name = "Elevation (m)") 

p.ch4.ele <- ggplot() +
    geom_smooth(data=df,aes(x=Elevation_m,y=pCH4_ppm), method='lm',formula = "y ~ x",se=FALSE,color="black") +
  geom_point(data=df,aes(x=Elevation_m,y=pCH4_ppm,color=reorder(Site_ID,Elevation_m,median,decreasing = TRUE)),size=2) +
  geom_point(data=df,aes(x=Elevation_m,y=pCH4_ppm),shape=1,size=2) +
    ylab(expression(italic(p)~CH[4] ~'(ppm)')) + xlab('Elevation (m)') +
  scale_color_viridis(name="Site",discrete = TRUE) +
  scale_y_continuous(transform="log",breaks=c(3,10,30,100,300,1000,3000,10000)) +
  theme_bw(base_size = 24)


leg <- ggpubr::get_legend(p.ch4)

full_1 <- plot_grid(p.ch4 + rremove("x.title") + rremove("legend") , p.co2+ rremove("legend"), ncol = 1, align = "v")


full_2 <- plot_grid(p.ch4.ele + rremove("x.title") + rremove("y.title") + rremove("legend") ,p.co2.ele+ rremove("y.title") + rremove("legend"),nrow=2)

fig6 <- plot_grid(full_1,full_2,nrow=1)
  

fig6_legend <- ggarrange(leg,nrow=1)




```


# Figure 7

```{r Figure 7, echo=FALSE}
df <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))
df$DateTime <- as.POSIXct(df$DateTime, format = "%Y-%m-%d %H:%M:%S")
##add elevation levels
df$Watertemp_c_saved <- df$WaterTemp_c
df$log_SA <- log(df$surface_area_m2)
df$log_WS <- log(df$WS_area_minus_pond)
df_1 <- df%>%filter(Site_ID !="Wetland")

# get list of residuals
model <- lm(log(df$pCO2_ppm)~df$Elevation_m)
df$res <- resid(model) 


gmc_co2 <- df %>%
  select(res,pCH4_ppm,pCO2_ppm,Site_ID,Elevation_m,percent_DTW,WS_area_minus_pond,Watertemp_c_saved,WaterTemp_c,Volumn_m3,surface_area_m2,SA_to_Vol_ratio,depth_ave_m,log_SA,log_WS)%>%
  group_by(Site_ID,Elevation_m,percent_DTW,
           WS_area_minus_pond,log_WS) %>%
  mutate(mean_res = mean(res),
         median_res = median(res)) %>%
  mutate( gpm_SA = mean(surface_area_m2),
          surface_area_m2 = surface_area_m2 - gpm_SA) %>%
  mutate( gpm_depth = mean(depth_ave_m),
          depth_ave_m = depth_ave_m - gpm_depth) %>% 
  mutate( gpm_log_SA = mean(log_SA),
          log_SA = log_SA - gpm_log_SA) %>% 
  ungroup()

gmc_ch4 <- df%>%filter(pCH4_ppm > 4)%>%
  select(res,pCH4_ppm,pCO2_ppm,Site_ID,Elevation_m,percent_DTW,WS_area_minus_pond,Watertemp_c_saved,WaterTemp_c,Volumn_m3,surface_area_m2,SA_to_Vol_ratio,depth_ave_m,log_SA,log_WS)%>%
  group_by(Site_ID,Elevation_m,percent_DTW,
           WS_area_minus_pond,log_WS) %>%
  mutate(mean_res = mean(res),
         median_res = median(res)) %>%
  mutate( gpm_SA = mean(surface_area_m2),
          surface_area_m2 = surface_area_m2 - gpm_SA) %>%
  mutate( gpm_depth = mean(depth_ave_m),
          depth_ave_m = depth_ave_m - gpm_depth) %>% 
  mutate( gpm_log_SA = mean(log_SA),
          log_SA = log_SA - gpm_log_SA) %>% 
  ungroup()

#plot

p.dtw.co2 <-  ggplot() + 
  geom_smooth(data=df,aes(x=percent_DTW,y=res),method='lm',formula = "y ~ x",se=FALSE,color="black") +
  geom_point(data=df,aes(x=percent_DTW,y=res,color=reorder(Site_ID,Elevation_m,median,decreasing = TRUE)),size=2) +
  geom_point(data=df,aes(x=percent_DTW,y=res),color="black",shape=1, size=2) +
  ylab('residuals') + xlab('% DTW < 1-m') +
  scale_x_continuous(transform="log",breaks=c(1,3,10,30,100)) +
  scale_color_viridis(name="Site",discrete = TRUE) +
  theme_bw(base_size = 24)+ 
guides(color = guide_legend(ncol = 2))

#surface area v 

p.sa.co2 <- ggplot(gmc_co2%>%filter(Site_ID!="Wetland"),aes(x=surface_area_m2,y=pCO2_ppm,color = reorder(Site_ID, Elevation_m, median, decreasing = TRUE))) + 
    geom_vline(xintercept = 0,linetype="dashed") +
  geom_point(size=2) +
  geom_smooth(method='lm',formula = "y ~ x",se=FALSE) +
    geom_point(data=gmc_co2%>%filter(Site_ID!="S1")%>%filter(Site_ID!="S3")%>%filter(Site_ID!="Wetland"),aes(x=surface_area_m2,y=pCO2_ppm),color="black",shape=1, size=2) +
    ylab(expression(italic(p)~CO[2] ~'(ppm)')) + xlab(expression(atop('surface area'~ (m^2),'centered on group mean'))) +
  scale_color_viridis(name="Site",discrete = TRUE) +
  scale_y_continuous(transform="log",breaks=c(300,1000,3000,10000)) +
  theme_bw(base_size = 24)

p.depth.ch4 <- ggplot(gmc_ch4%>%filter(pCH4_ppm > 4)%>%filter(Site_ID!="Wetland"),aes(x=depth_ave_m,y=pCO2_ppm,color = reorder(Site_ID,Elevation_m,median,decreasing = TRUE))) + 
      geom_vline(xintercept = 0,linetype="dashed") +
  geom_point(size=2)+
  geom_smooth(method='lm',formula = "y ~ x",se=FALSE) +
    geom_point(data=gmc_ch4%>%filter(pCH4_ppm > 4)%>%filter(Site_ID!="Wetland"),aes(x=depth_ave_m,y=pCO2_ppm),color="black",shape=1, size=2) +
    ylab(expression(italic(p)~CH[4] ~'(ppm)')) + xlab("average depth (m)\ncentered on group mean") +
  scale_color_viridis(name="Site",discrete = TRUE) +
  scale_y_continuous(transform="log",breaks=c(300,1000,3000,10000)) +
  theme_bw(base_size = 24)


leg <- ggpubr::get_legend(p.sa.co2)

p <- plot_grid(p.depth.ch4+rremove("legend"),p.sa.co2+rremove("legend"))
p2 <-ggarrange(NULL,p.dtw.co2+rremove("legend"),NULL,nrow=1,widths = c(1,2, 1))
fig7 <-ggarrange(p,p2,nrow=2)



```



#Figure 8

```{r Figure 8}

WL_df <- read.csv(here::here("PondPaper_Repository/continuous_data.csv"))%>%select(DateTime,Site_ID,WaterTemp_c,AirTemp_c)
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

df1 <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))
df <- df1%>%select(Site_ID,Elevation_m)
df <- unique(df)

WL_df <- left_join(WL_df,df,by="Site_ID")

start_time <- as.POSIXct("2022-06-16 11:00:00",tz="UTC")
end_time <- as.POSIXct("2023-08-24 13:15:00",tz="UTC")
timestamp_sequence <- seq.POSIXt(start_time, end_time, by = "hour")

new_df <- as.data.frame(timestamp_sequence)
new_df <- new_df%>%rename(DateTime=timestamp_sequence)

new_df$slope <- NA
new_df$adjR <- NA
new_df$n <- NA
new_df$AirTemp_c <- NA
new_df$RMSE <- NA
new_df$pvalue <- NA
new_df$slope <- NA
i <-2
for (i in 1:nrow(new_df)) {
  select_timestamp <- new_df[i,]$DateTime
  #filter 
  filter_df <-  WL_df%>%filter(DateTime==select_timestamp)
  new_df[i,]$AirTemp_c <- mean(filter_df$AirTemp)
  if(nrow(filter_df) > 5){
    model <- lm(WaterTemp_c ~ Elevation_m, data = filter_df)
    new_df[i,]$slope <- summary(model)$coefficients[2,1]
    new_df[i,]$adjR <- summary(model)$adj.r.squared
    new_df[i,]$RMSE <- sqrt(mean(model$residuals^2))
    new_df[i,]$pvalue <- summary(model)$coefficients[2,4]
    new_df[i,]$n <- nrow(filter_df)
    new_df[i,]$slope <- as.numeric(model$coefficients[2])
    
  }else{
    new_df[i,]$adjR <- NA
  }
    
} 


p1 <- ggplot() + geom_point(data=df1,aes(x=Elevation_m,y=Watertemp_c,fill = reorder(New.Name,Elevation_m,median,decreasing = TRUE)),shape=21,size=3)+
  geom_point(data=gmc,aes(x=Elevation_m,y=gpm_Watertemp_c),fill="black",shape=23,size=4)+
  guides(fill=guide_legend(title="Site name"))+ 
  xlab("Elevation (m)") + ylab("Water temperature (c)") +
  geom_smooth(data=gmc,aes(x=Elevation_m,y=gpm_Watertemp_c),method='lm',formula = "y ~ x",se=TRUE,color="black") +
  theme_bw(base_size = 18)


Fig8.B <- ggplot()+ geom_line(data=new_df,aes(x=DateTime,y=adjR),color="salmon") +
  ylab(expression(paste("Adj. r squared"))) +
   theme_classic(base_size = 18)+
  xlim(as.POSIXct("2022-07-01 12:00:00"),as.POSIXct("2023-07-01 00:00:00"))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) 

fig8.c <- ggplot()+ 
  geom_point(data=new_df%>%filter(slope<0),aes(x=DateTime,y=slope),color="black",shape=1)  +
  geom_point(data=new_df%>%filter(slope>0),aes(x=DateTime,y=slope),color="grey",shape=1) + ylab("slope of\n linear regression") +
   theme_classic(base_size = 18)+
  xlim(as.POSIXct("2022-07-01 12:00:00"),as.POSIXct("2023-07-01 00:00:00"))


#fig 8 E
d = data.frame(x = seq(from = as.POSIXct("2022-07-01 12:00:00"), to=as.POSIXct("2022-08-01 00:00:00"), by = "1 hour"), y = 1)
d$hour = as.numeric(format(d$x, "%H"))
d$hour_shade =ifelse(d$hour >= 18 | d$hour <= 6, "gray80", "gray95")


fig8.E <- ggplot(d, aes(x, y)) + 
  geom_rect(aes(xmin = x, xmax = lead(x), ymin = -Inf, ymax = Inf,
                fill = hour_shade)) +
  scale_fill_identity() +
  geom_line(data=new_df,aes(x=DateTime,y=adjR),color="salmon",linewidth=1) +
  ylab(expression(paste("Adj. r squared"))) + xlab("")  +
   theme_classic(base_size = 18)+
  xlim(as.POSIXct("2022-07-01 12:00:00"),as.POSIXct("2022-08-01 00:00:00"))



```

#barplot Figure 9 

```{r Figure 9, echo=FALSE}

modeled_GHG_df <- read.csv(here::here("PondPaper_Repository/modeled_GHG_data.csv"))
modeled_GHG_df$DateTime <- as.POSIXct(modeled_GHG_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

modeled_GHG_df$month <- month(modeled_GHG_df$DateTime)

modeled_GHG_sum_df <- modeled_GHG_df %>%
  select(Site_ID,DateTime,
         F_mol.s_CH4,F_mol.s_CH4_fixedTemp,F_mol.s_CH4_fixedSA,F_mol.s_CH4_fixedTempfixedSA,
         F_mol.s_CO2,F_mol.s_CO2_fixedTemp,F_mol.s_CO2_fixedSA,F_mol.s_CO2_fixedTempfixedSA)
modeled_GHG_sum_df$month_Day <-  format(as.Date(modeled_GHG_sum_df$DateTime,format="%Y-%m-%d"), format = "%m-%d")
modeled_GHG_sum_df_2 <- modeled_GHG_sum_df%>%group_by(Site_ID,month_Day)%>%
  summarise(
    F_CH4_mol.day = mean(F_mol.s_CH4,na.rm=TRUE),
    F_CH4_fixedTemp_mol.day = mean(F_mol.s_CH4_fixedTemp,na.rm=TRUE),
    F_CH4_fixedSA_mol.day = mean(F_mol.s_CH4_fixedSA,na.rm=TRUE),
    F_CH4_fixedTempfixedSA_mol.day = mean(F_mol.s_CH4_fixedTempfixedSA,na.rm=TRUE),
    F_CO2_mol.day = mean(F_mol.s_CO2,na.rm=TRUE),
    F_CO2_fixedTemp_mol.day = mean(F_mol.s_CO2_fixedTemp,na.rm=TRUE),
    F_CO2_fixedSA_mol.day = mean(F_mol.s_CO2_fixedSA,na.rm=TRUE),
    F_CO2_fixedTempfixedSA_mol.day = mean(F_mol.s_CO2_fixedTempfixedSA,na.rm=TRUE)
  )
modeled_GHG_sum_df_2$F_CH4_mol.day <- modeled_GHG_sum_df_2$F_CH4_mol.day*60*60*24
modeled_GHG_sum_df_2$F_CH4_fixedTemp_mol.day <- modeled_GHG_sum_df_2$F_CH4_fixedTemp_mol.day*60*60*24
modeled_GHG_sum_df_2$F_CH4_fixedSA_mol.day <- modeled_GHG_sum_df_2$F_CH4_fixedSA_mol.day*60*60*24
modeled_GHG_sum_df_2$F_CH4_fixedTempfixedSA_mol.day <- modeled_GHG_sum_df_2$F_CH4_fixedTempfixedSA_mol.day*60*60*24
modeled_GHG_sum_df_2$F_CO2_mol.day <- modeled_GHG_sum_df_2$F_CO2_mol.day*60*60*24
modeled_GHG_sum_df_2$F_CO2_fixedTemp_mol.day <- modeled_GHG_sum_df_2$F_CO2_fixedTemp_mol.day*60*60*24
modeled_GHG_sum_df_2$F_CO2_fixedSA_mol.day <- modeled_GHG_sum_df_2$F_CO2_fixedSA_mol.day*60*60*24
modeled_GHG_sum_df_2$F_CO2_fixedTempfixedSA_mol.day <- modeled_GHG_sum_df_2$F_CO2_fixedTempfixedSA_mol.day*60*60*24

modeled_GHG_sum_df_3 <- modeled_GHG_sum_df_2%>%group_by(Site_ID)%>%
  summarise(
    F_CH4_mol.year = mean(F_CH4_mol.day,na.rm=TRUE),
    F_CH4_fixedTemp_mol.year = mean(F_CH4_fixedTemp_mol.day,na.rm=TRUE),
    F_CH4_fixedSA_mol.year = mean(F_CH4_fixedSA_mol.day,na.rm=TRUE),
    F_CH4_fixedTempfixedSA_mol.year = mean(F_CH4_fixedTempfixedSA_mol.day,na.rm=TRUE),
    F_CO2_mol.year = mean(F_CO2_mol.day,na.rm=TRUE),
    F_CO2_fixedTemp_mol.year = mean(F_CO2_fixedTemp_mol.day,na.rm=TRUE),
    F_CO2_fixedSA_mol.year = mean(F_CO2_fixedSA_mol.day,na.rm=TRUE),
    F_CO2_fixedTempfixedSA_mol.year = mean(F_CO2_fixedTempfixedSA_mol.day,na.rm=TRUE)
  )

modeled_GHG_sum_df_3$F_CH4_mol.year <- modeled_GHG_sum_df_3$F_CH4_mol.year * 365 
modeled_GHG_sum_df_3$F_CH4_fixedTemp_mol.year <- modeled_GHG_sum_df_3$F_CH4_fixedTemp_mol.year * 365
modeled_GHG_sum_df_3$F_CH4_fixedSA_mol.year <- modeled_GHG_sum_df_3$F_CH4_fixedSA_mol.year * 365
modeled_GHG_sum_df_3$F_CH4_fixedTempfixedSA_mol.year <- modeled_GHG_sum_df_3$F_CH4_fixedTempfixedSA_mol.year * 365
modeled_GHG_sum_df_3$F_CO2_mol.year <- modeled_GHG_sum_df_3$F_CO2_mol.year * 365
modeled_GHG_sum_df_3$F_CO2_fixedTemp_mol.year <- modeled_GHG_sum_df_3$F_CO2_fixedTemp_mol.year * 365
modeled_GHG_sum_df_3$F_CO2_fixedSA_mol.year <- modeled_GHG_sum_df_3$F_CO2_fixedSA_mol.year * 365
modeled_GHG_sum_df_3$F_CO2_fixedTempfixedSA_mol.year <- modeled_GHG_sum_df_3$F_CO2_fixedTempfixedSA_mol.year * 365

#convert to mol and then to gC-CO2
 melted_data_2 <- modeled_GHG_sum_df_3 %>%
    pivot_longer(
      cols = -c(Site_ID),  # Columns to be melted
      names_to = "Model",      # Name of the new key column
      values_to = "mol.year"         # Name of the new value column
    )
 

melted_data_2$Site_ID <- factor(melted_data_2$Site_ID, levels = c("S10","S6","S11","S12","S5","S4","S7","S8","S3","S2","Wetland","S1"))

 
melted_data_2$Variable <- melted_data_2$Model

melted_data_3 <- melted_data_2%>%filter(Site_ID!="Wetland")
melted_data_2_sub <- melted_data_2%>%filter(Site_ID=="Wetland")%>%filter( Model=="F_CH4_fixedSA_mol.year"|Model=="F_CH4_fixedTempfixedSA_mol.year"|Model=="F_CO2_fixedSA_mol.year"|Model=="F_CO2_fixedTempfixedSA_mol.year")
melted_data_2_sub2 <- melted_data_2%>%filter(Site_ID=="Wetland")%>%filter( Model=="F_CO2_mol.year"|Model=="F_CO2_fixedTemp_mol.year"|Model=="F_CH4_mol.year"|Model=="F_CH4_fixedTemp_mol.year")
melted_data_2_sub2$mol.year <- 0

melted_data_3 <- rbind(melted_data_3,melted_data_2_sub,melted_data_2_sub2)


melted_data_co2 <- melted_data_3%>%filter(Variable=="F_CO2_mol.year"|Variable=="F_CO2_fixedTemp_mol.year"|Variable=="F_CO2_fixedSA_mol.year"|Variable=="F_CO2_fixedTempfixedSA_mol.year")
melted_data_ch4 <- melted_data_3%>%filter(Variable=="F_CH4_mol.year"|Variable=="F_CH4_fixedTemp_mol.year"|Variable=="F_CH4_fixedSA_mol.year"|Variable=="F_CH4_fixedTempfixedSA_mol.year")

melted_data_co2$gCasCO2.year <- melted_data_co2$mol.year*12
  
melted_data_ch4$gCasCH4.year <- melted_data_ch4$mol.year*12

#rearrang variable
melted_data_co2$Model <- factor(melted_data_co2$Model, levels = c("F_CO2_fixedTempfixedSA_mol.year","F_CO2_fixedSA_mol.year","F_CO2_fixedTemp_mol.year","F_CO2_mol.year"))

melted_data_ch4$Model <- factor(melted_data_ch4$Model, levels = c("F_CH4_fixedTempfixedSA_mol.year","F_CH4_fixedSA_mol.year","F_CH4_fixedTemp_mol.year","F_CH4_mol.year"))
#plot



wetland_df_ch4 <- melted_data_ch4%>%filter(Site_ID=="Wetland")
wetland_df_ch4$Model <- ifelse(wetland_df_ch4$Model=="F_CH4_fixedSA_mol.year","F_CH4_mol.year", wetland_df_ch4$Model)
wetland_df_ch4 <- wetland_df_ch4%>%
  mutate(Site_ID = case_match(Site_ID, 
                      'Wetland' ~ 'W'))
melted_data_ch4 <- melted_data_ch4%>%filter(Site_ID!="Wetland")
melted_data_ch4 <- rbind(melted_data_ch4,wetland_df_ch4)

melted_data_ch4$Site_ID <- factor(melted_data_ch4$Site_ID, levels = c("S10","S6","S11","S12","S5","S4","S7","S8","S3","S2","W","S1"))


wetland_df_co2 <- melted_data_co2%>%filter(Site_ID=="Wetland")
wetland_df_co2$Model <- ifelse(wetland_df_co2$Model=="F_CO2_fixedSA_mol.year","F_CO2_mol.year", wetland_df_co2$Model)
wetland_df_co2 <- wetland_df_co2%>%  mutate(Site_ID = case_match(Site_ID,   'Wetland' ~ 'W'))
melted_data_co2 <- melted_data_co2%>%filter(Site_ID!="Wetland")
melted_data_co2 <- rbind(melted_data_co2,wetland_df_co2)

melted_data_co2$Site_ID <- factor(melted_data_co2$Site_ID, levels = c("S10","S6","S11","S12","S5","S4","S7","S8","S3","S2","W","S1"))

p.ch4 <- ggplot(data=melted_data_ch4%>%filter(Model=="F_CH4_mol.year"), aes(x=Site_ID, y=gCasCH4.year)) +
geom_bar(stat="identity", color="black",fill="#225ea8", position=position_dodge()) +
    theme_bw(base_size = 22) +
  xlab("Site (ordered by increasing surface area)") +
    ylab(expression("grams of"~CH[4]~"as C"~~year^-1)) 

  
p.co2 <- ggplot(melted_data_co2%>%filter(Model=="F_CO2_mol.year")) + aes(x = Site_ID, y = gCasCO2.year) +
  geom_bar(stat="identity", color="black",fill= "#225ea8", position=position_dodge())+
  ylab(expression("grams of"~CO[2]~"as C"~~year^-1)) + 
xlab("") +
  scale_y_cut(breaks=c(1.25*10^5), which=c(1, 2), scales=c(0.5, 3.1)) + theme_bw(base_size = 22) 
 

library(cowplot)


full_2 <- ggarrange(p.ch4,p.co2, ncol = 1, nrow = 2)

```
#supp fig 1
```{r Supp Fig 1, echo=FALSE}

k_df <- read.csv(here::here("PondPaper_Repository/GHGsampling_discrete_data.csv"))

k_df$BelowSat <- NA
k_df$BelowSat <- ifelse(k_df$CH4_sat_precent < 100, "*", NA)

p2 <- ggplot(k_df) + geom_point(
  aes(x=surface_area_m2,y=K600),fill="#31a354",
  shape=21,size=3)  + 
  geom_hline(aes(yintercept = median(k_df$K600,na.rm = TRUE)), color="blue", linetype="dashed") +
  theme_bw(base_size = 18) +
  scale_x_log10() +
  xlab(expression(paste("Surface Area (",m^2, ")"))) +
    ylab(expression(paste(italic('k')[600]," (m ", d^-1,")"))) 

```
# supp Figs 2, 3, 4, and 5 


```{r Supp Fig 2,3,4 & 5, echo=FALSE}

modeled_GHG_df <- read.csv(here::here("PondPaper_Repository/modeled_GHG_data.csv"))
modeled_GHG_df$DateTime <- as.POSIXct(modeled_GHG_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

modeled_GHG_df$month <- month(modeled_GHG_df$DateTime)
####
# Supplementary Figure 2 amd 3

p.F.co2 <- ggplot(modeled_GHG_df) + 
  geom_line(aes(x=DateTime,y=flux_mol.sec.m2_co2_fluctuate*60*60*24),linetype="solid",color="#d95f02") + 
    geom_line(aes(x=DateTime,y=flux_mol.sec.m2_co2_fixed*60*60*24),linetype = "dashed", color="#1b9e77",linewidth=1) +
    facet_wrap(~Site_ID, scales = "free") +
    ylab(CO[2]~evasion~(mol~m^-2~day^-1)) +
    scale_x_datetime(date_breaks = '4 month', date_labels=c('%b')) +
  scale_y_continuous(labels = scientific) +
  theme_bw(base_size = 14) 


#filter out extremes in S2 and S3
modeled_GHG_df_2 <- modeled_GHG_df%>%filter(Site_ID!="S2")%>%filter(Site_ID!="S3")

sub <-  modeled_GHG_df %>%filter(Site_ID=="S2"|Site_ID=="S3")%>%filter(flux_mol.sec.m2_ch4_fluctuate<0.0003/60/60/24)

sub_test <-  modeled_GHG_df%>%filter(Site_ID=="S2"|Site_ID=="S3")%>%filter(flux_mol.sec.m2_ch4_fluctuate>0.0003/60/60/24)

modeled_GHG_df_3<-rbind(modeled_GHG_df_2,sub)

p.F.ch4 <- ggplot(modeled_GHG_df_3) + 
    geom_line(aes(x=DateTime,y=flux_mol.sec.m2_ch4_fluctuate*60*60*24),linetype="solid",color="#d95f02") + 
  geom_line(aes(x=DateTime,y=flux_mol.sec.m2_ch4_fixed*60*60*24),linetype = "dashed",color="#1b9e77",linewidth=1) +
  facet_wrap(~Site_ID, scales = "free") +
  ylab(expression(CH[4]~evasion~(mol~m^-2~day^-1))) +
  scale_x_datetime(
    date_breaks = '4 month',
    date_labels=c('%b')) +
  scale_y_continuous(labels = scientific) +
  theme_bw(base_size = 14) 


# Supplementary Figure 4 amd 5

p.F.co2 <- ggplot(modeled_GHG_df) + 
   geom_line(aes(x=DateTime,y=F_mol.s_CO2*60*60*24), color="black",linewidth=1) +
  geom_line(aes(x=DateTime,y=F_mol.s_CO2_fixedTemp*60*60*24),linetype="solid",color="#d95f02") + 
     geom_line(aes(x=DateTime,y=F_mol.s_CO2_fixedSA*60*60*24), color="blue",linewidth=1) +
    geom_line(aes(x=DateTime,y=F_mol.s_CO2_fixedTempfixedSA*60*60*24),linetype = "dashed", color="#1b9e77",linewidth=1) +
    facet_wrap(~Site_ID, scales = "free") +
    ylab(CO[2]~evasion~(mol~day^-1)) +
    scale_x_datetime(
    date_breaks = '4 month',
    date_labels=c('%b')
    ) +
  theme_bw(base_size = 14) 


p.F.ch4 <- ggplot(modeled_GHG_df_3) + 
    geom_line(aes(x=DateTime,y=F_mol.s_CH4*60*60*24), color="black",linewidth=1) +
    geom_line(aes(x=DateTime,y=F_mol.s_CH4_fixedTemp*60*60*24),linetype="solid",color="#d95f02") + 
       geom_line(aes(x=DateTime,y=F_mol.s_CH4_fixedSA*60*60*24), color="blue",linewidth=1) +
  geom_line(aes(x=DateTime,y=F_mol.s_CH4_fixedTempfixedSA*60*60*24),linetype = "dashed",color="#1b9e77",linewidth=1) +
  facet_wrap(~Site_ID, scales = "free") +
  ylab(expression(CH[4]~evasion~(mol~day^-1))) +
  scale_x_datetime(
    date_breaks = '4 month',
    date_labels=c('%b')) +
  theme_bw(base_size = 14) 
```


#supp fig 6
relationship between pressure and gas saturation

```{r supp fig 6, echo=FALSE}
df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))

p.A <- ggplot(df ,aes(x=Elevation_m,y=CO2_sat_precent)) + geom_point() +
  xlab("Elevation (m)") + 
      ylab(expression(paste("% saturation CO"[2] ,))) +
  scale_y_continuous(transform="log",breaks=c(300,1000,3000,10000)) +
  theme_bw(base_size = 18) 

p.B <- ggplot(df ,aes(x=Elevation_m,y=pCO2_ppm)) + geom_point() +
  ylab(substitute(paste(italic('p'),CO[2], " (ppm)"))) +
  xlab(expression("Elevation (m)")) +
  scale_y_continuous(transform="log",breaks=c(300,1000,3000,10000)) +
  theme_bw(base_size = 18)


p.C <- ggplot(df ,aes(x=Elevation_m,y=CH4_pSat)) + geom_point() +
  xlab(expression("Elevation (m)")) +
        ylab(expression(paste("% saturation CH"[4] ,))) +
  scale_y_continuous(transform="log",breaks=c(1000,10000,100000,1000000,10000000)) +
    theme_bw(base_size = 18)

p.D <- ggplot(df ,aes(x=Elevation_m,y=pCH4_ppm)) + geom_point() + 
    xlab(expression("Elevation (m)")) +
  ylab(substitute(paste(italic('p'),CH[4], " (ppm)"))) +
    scale_y_continuous(transform="log",breaks=c(1,10,100,1000,10000)) +
    theme_bw(base_size = 18)


full_plot <-plot_grid(p.A + theme(axis.title.x=element_blank()),
                      p.B + theme(axis.title.x=element_blank()),
                      p.C, 
                      p.D ,
                      ncol = 2, nrow = 2, align = "v")


#% sat v concntration
p.E <- ggplot(df ,aes(x=pCH4_ppm,y=CH4_pSat)) + geom_point() +
    xlab(substitute(paste(italic('p'),CH[4], " (ppm)"))) +
          ylab(expression(paste("% saturation CH"[4] ,))) +
      theme_bw(base_size = 18)


p.F <- ggplot(df ,aes(x=pCO2_ppm,y=CO2_sat_precent)) + geom_point() +
#  geom_abline(intercept = 0, slope = 1, color="red") +
    xlab(substitute(paste(italic('p'),CO[2], " (ppm)"))) +
        ylab(expression(paste("% saturation CO"[2] ,))) +
      theme_bw(base_size = 18)

full_plot <-plot_grid(p.F ,
                      p.E,
                      ncol = 2)


```


```{r Supp Fig 2,3,4 & 5, echo=FALSE}
#surface area


library(stringr)
library(grid)

df <- read.csv(here::here("Wetlands/Wetland_df_MERGE_2023-11-10.csv"))
df$Date <- as.Date(df$Date)

df$New.Name <- df$Wetland
df <- df%>%
  mutate(New.Name = case_match(New.Name, 
                      'Wetland01' ~ 'S1', 
                      'Wetland02' ~ 'S2',
                      'Wetland03' ~ 'S3',
                      'Wetland04' ~ 'S4',
                      'Wetland05' ~ 'S8',
                      'Wetland06' ~ 'S5',
                      'Wetland07' ~ 'S7',
                      'Wetland08' ~ 'S12',
                      'Wetland09' ~ 'S10',
                      'Wetland10' ~ 'S11',
                      'Wetland11' ~ 'S6',
                      'Wetland12' ~ 'Wetland'
                ))

#I want to make a 12 panel figure with 2 axis depth and surface area

WL_df <- read.csv(here::here("Wetlands/WaterLevel_FINAL/WL_Wetland_all_FINAL.csv"))
#we don't have depth for wetland 12 but we can use water level to plot
WL_df[WL_df$Station=="WL_Wetland12",]$depth_ave_m <- WL_df[WL_df$Station=="WL_Wetland12",]$WaterLevel_m
WL_df <- WL_df[c("DateTime","Station","Baro_kpa","BaroTemp_c","WLTemp_c","depth_ave_m","surface_area_m2","Volumn_m3","SA_to_Vol_ratio")]
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

WL_df$New.Name <- WL_df$Station
WL_df <- WL_df%>%
  mutate(New.Name = case_match(New.Name, 
                      'WL_Wetland01' ~ 'S1', 
                      'WL_Wetland02' ~ 'S2',
                      'WL_Wetland03' ~ 'S3',
                      'WL_Wetland04' ~ 'S4',
                      'WL_Wetland05' ~ 'S8',
                      'WL_Wetland06' ~ 'S5',
                      'WL_Wetland07' ~ 'S7',
                      'WL_Wetland08' ~ 'S12',
                      'WL_Wetland09' ~ 'S10',
                      'WL_Wetland10' ~ 'S11',
                      'WL_Wetland11' ~ 'S6',
                      'WL_Wetland12' ~ 'Wetland'
                ))



p1 <- ggplot(data = WL_df%>%filter(Station=="WL_Wetland01")) + 
  geom_point(aes(x = DateTime, y = depth_ave_m),size=1)
p1
p1 + facet_wrap(~Station)+theme(text=element_text(size=21))


p1 <- ggplot(WL_df%>%filter(DateTime<as.POSIXct("2023-06-07 00:00:00")), aes(x=DateTime)) +
  geom_line( aes(y=surface_area_m2),color="brown") + 
   theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
 # scale_y_continuous(breaks = c(0,)) +
  theme(text=element_text(size=18))

p2 <- p1 + facet_wrap(~New.Name, scales = "free_y")

```

##surface area over time 
```{r SA, echo=FALSE}
#Figs
#2022-11-28
#this script is to make time series to use for AGU poster and wetland paper 
library(stringr)
library(grid)

df <- read.csv(here::here("Wetlands/Wetland_df_MERGE_2023-11-10.csv"))
df$Date <- as.Date(df$Date)

df$name.code <- paste("W",as.numeric(gsub("\\D", "", df$Wetland)))
df$name.code <- str_replace_all(df$name.code, " ", "")
df$name.code <- factor(df$name.code, levels = c("W1","W2","W3","W4","W5","W6","W7","W8","W9","W10","W11","W12"))

#I want to make a 12 panel figure with 2 axis depth and surface area

WL_df <- read.csv(here::here("Wetlands/WaterLevel_FINAL/WL_Wetland_all_FINAL.csv"))
#we don't have depth for wetland 12 but we can use water level to plot
WL_df[WL_df$Station=="WL_Wetland12",]$depth_ave_m <- WL_df[WL_df$Station=="WL_Wetland12",]$WaterLevel_m
WL_df <- WL_df[c("DateTime","Station","Baro_kpa","BaroTemp_c","WLTemp_c","depth_ave_m","surface_area_m2","Volumn_m3","SA_to_Vol_ratio")]
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")

WL_df$New.Name <- WL_df$Station
#make column with new name to reflect elevation. S stands for "site"
WL_df <- WL_df%>%mutate(New.Name = case_match(New.Name, 'WL_Wetland01' ~ 'S1', 'WL_Wetland02' ~ 'S2','WL_Wetland03' ~ 'S3','WL_Wetland04' ~ 'S4','WL_Wetland05' ~ 'S8','WL_Wetland06' ~ 'S5','WL_Wetland07' ~ 'S7','WL_Wetland08' ~ 'S12','WL_Wetland09' ~ 'S10','WL_Wetland10' ~ 'S11','WL_Wetland11' ~ 'S6','WL_Wetland12' ~ 'W'))

WL_df$New.Name <- factor(WL_df$New.Name, levels = c("S1","S2","S3","S4","S5","S6","S7","S8","W","S10","S11","S12"))


p1 <- ggplot(WL_df%>%filter(DateTime<as.POSIXct("2023-06-06 00:00:00")), aes(x=DateTime,y=surface_area_m2)) +
  geom_line(color="blue") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
  ylab("Surface area")

p1 + facet_wrap(~New.Name, scales = "free_y")

```
