---
title: "FindWaterlevelData_2022-08-19"
author: "Kriddie"
date: "2022-08-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate) #package for our date parsing
library(here)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(purrr)
library(sjmisc)
library(plotly)
#theme_set(theme_bw())
```

## Description

The purpose of this script is to identify the Waterlevel and water temp, at the time of sampling each wetland 

After reading in the data, we will plot it to see if the Waterlevel and water temp is within a range that "makes sense" for the environment that we are measuring.

For each wetland sampled we will take an average of the Waterlevel and water temp collected during the sample period

For example: if samples were sampled wetland 1 on 7/14/2022 between 10am and 11am, we need an average of Waterlevel and water temp from that time period

#Read in Data
We will run a loop so that all water level is merged by site

```{r Hobo WL}
#First the Hobos

setwd(here::here("Wetlands/Files_Renamed/WaterLevelDATA"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop


#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      WLData <- read.csv(file, skip=11, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(WLData[1,3],"Abs Pres, psi")){
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*6.89476
        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000
        
      } else { 
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
      }
      WLData$DateTime <- as.POSIXct(WLData$DateTime, tz="UTC",
                                    tryFormats = c("%m/%d/%y %I:%M:%S %p",
                                                   "%m/%d/%Y %H:%M"))
    }
    if (exists("WLData")){
      Temp_WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      #      
      
      if(str_contains(Temp_WLData[1,3],"Abs Pres, psi")){
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*6.89476
        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        
        
      } else { 
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
      }
      
      Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, tz="UTC",
                                         tryFormats = c("%m/%d/%y %I:%M:%S %p",
                                                        "%m/%d/%Y %H:%M"))
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData$DateTime <- round_date(WLData$DateTime, "15 mins")
  WLData$Station <- site
  WLData=unique(WLData)
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}

```

### Now read in solinst

#Clean Data

```{r clean data and plot, echo=FALSE}


ggplot(data = WL_Wetland01, aes(x = DateTime, y = WLPres_kpa)) + geom_point()
plot_ly(data = WL_Wetland01, x = ~DateTime, y = ~WLPres_kpa)

#wetland01
WL_Wetland01 <- WL_Wetland01%>%filter(DateTime >= as.POSIXct("2022-06-17 11:00:00",tz = "UTC"))
WL_Wetland01 <- WL_Wetland01%>%filter(DateTime < as.POSIXct("2022-07-14 10:00:00",tz="UTC")|
                                        DateTime > as.POSIXct("2022-07-14 11:00:00",tz = "UTC"))

plot_ly(data = WL_Wetland01, x = ~DateTime, y = ~WLPres_kpa)

#wetland02
WL_Wetland02 <- WL_Wetland02%>%filter(DateTime != as.POSIXct("2022-06-16 11:30:00",tz = "UTC"))
WL_Wetland02 <- WL_Wetland02%>%filter(DateTime != as.POSIXct("2022-07-07 13:45:00",tz = "UTC"))

#wetland03
WL_Wetland03 <- WL_Wetland03%>%filter(DateTime != as.POSIXct("2022-07-14 12:30:00",tz = "UTC"))


#wetland04
WL_Wetland04 <- WL_Wetland04%>%filter(DateTime < as.POSIXct("2022-07-15 13:00:00",tz="UTC")|
                                        DateTime > as.POSIXct("2022-07-15 13:30:00",tz = "UTC"))
#logger shifted 6/29/2022 10:00
#there are no notes in the notebook, but I believe the logger was switched for ? reason

WL_Wetland04_1 <- WL_Wetland04%>%filter(DateTime < as.POSIXct("2022-06-29 10:00:00",tz="UTC"))
WL_Wetland04_1$WLPres_kpa <- WL_Wetland04_1$WLPres_kpa + (66.926-64.264)
WL_Wetland04_2 <- WL_Wetland04%>%filter(DateTime > as.POSIXct("2022-06-29 12:00:00",tz="UTC"))
WL_Wetland04 <- rbind(WL_Wetland04_1,WL_Wetland04_2)
rm(WL_Wetland04_1,WL_Wetland04_2)

#wetland05
WL_Wetland05 <- WL_Wetland05%>%filter(DateTime != as.POSIXct("2022-07-27 11:15:00",tz = "UTC"))

#wetland06
WL_Wetland06 <- WL_Wetland06%>%filter(DateTime != as.POSIXct("2022-06-16 14:15:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-19 13:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-19 13:15:00",tz = "UTC"))

#wetland07
WL_Wetland07 <- WL_Wetland07%>%filter(DateTime != as.POSIXct("2022-07-11 12:45:00",tz = "UTC"))

#wetland08
WL_Wetland08 <- WL_Wetland08%>%filter(DateTime > as.POSIXct("2022-07-05 10:00:00",tz="UTC"))%>%
  filter(DateTime < as.POSIXct("2022-07-08 10:00:00",tz="UTC")|
                                        DateTime > as.POSIXct("2022-07-08 12:30:00",tz = "UTC"))

#wetland09
WL_Wetland09 <- WL_Wetland09%>%filter(DateTime > as.POSIXct("2022-07-05 11:30:00",tz="UTC"))%>%
  filter(DateTime < as.POSIXct("2022-07-08 10:00:00",tz="UTC")|
                                        DateTime > as.POSIXct("2022-07-08 12:30:00",tz = "UTC"))

#wetland10
WL_Wetland10 <- WL_Wetland10%>%filter(DateTime != as.POSIXct("2022-07-12 11:15:00",tz="UTC"))

#logger shifted July 12
WL_Wetland10_1 <- WL_Wetland10%>%filter(DateTime <= as.POSIXct("2022-07-12 10:00:00",tz="UTC"))
WL_Wetland10_1$WLPres_kpa <- WL_Wetland10_1$WLPres_kpa + (68.838-68.04)
WL_Wetland10_2 <- WL_Wetland10%>%filter(DateTime > as.POSIXct("2022-07-12 11:30:00",tz="UTC"))
WL_Wetland10 <- rbind(WL_Wetland10_1,WL_Wetland10_2)
rm(WL_Wetland10_1,WL_Wetland10_2)

#wetland11
WL_Wetland11 <- WL_Wetland11%>%filter(DateTime > as.POSIXct("2022-07-11 12:30:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-28 12:15:00",tz="UTC"))

#wetland12
WL_Wetland12 <- WL_Wetland12%>%filter(DateTime > as.POSIXct("2022-06-07 14:15:00",tz="UTC"))

plot_ly(data = WL_Wetland09, x = ~DateTime, y = ~WLPres_kpa)
```
##  Plot
plot all water level data

```{r merge and plot, echo=FALSE}
WL_Wetland <- rbind(WL_Wetland01,WL_Wetland02,WL_Wetland03,WL_Wetland04,WL_Wetland05,WL_Wetland06,WL_Wetland07,WL_Wetland08,WL_Wetland09,WL_Wetland10,WL_Wetland11,WL_Wetland12)

p1 <- ggplot(data = WL_Wetland, aes(x = DateTime, y = WLPres_kpa)) + geom_point()
p1 + facet_wrap(~Station)

p2 <- ggplot(data = WL_Wetland, aes(x = DateTime, y = WLTemp_c)) + geom_point()
p2 + facet_wrap(~Station)

```

```{r baro, echo=FALSE}

###merge data with baro data###
setwd(here::here("Water_Level/BaroPress"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
site_names="Baro" #creates list of site names for following loop

#rm old files, if they exsist
rm(BaroData)
rm(Temp_BaroData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("BaroData")){
      BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
    }
    if (exists("BaroData")){
      Temp_BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      BaroData <- rbind(BaroData, Temp_BaroData)
      rm(Temp_BaroData)
    }
    
  }
  colnames(BaroData)=c("Date","Time","ms","Baro_kpa","BaroTemp_c")
  BaroData=unique(BaroData)
  BaroData$DateTime <- paste(BaroData$Date, BaroData$Time)
  BaroData$DateTime <- as.POSIXct(BaroData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  BaroData$DateTime <- round_date(BaroData$DateTime, "15 mins")
  BaroData$ms <- NULL
  BaroData$Date <- NULL
  BaroData$Time <- NULL
  BaroData <- BaroData[,c(3,1,2)]
  BaroData=unique(BaroData)
  assign((paste(site,sep="_")),BaroData) #creates object with new appended data
  rm(BaroData) #removes WLdata so that multiple sites aren't appended together
}

BaroSTATION <- Baro 

```

#correct for baro press
```{r subtract baro, echo=FALSE}

WL_Wetland <- left_join(WL_Wetland,BaroSTATION,by="DateTime")

WL_Wetland$WaterLevel_m <- (WL_Wetland$WLPres_kpa - WL_Wetland$Baro_kpa) * 0.10197442889221


p1 <- ggplot(data = WL_Wetland, aes(x = DateTime, y = WaterLevel_m)) + geom_point()
p1 + facet_wrap(~Station)

```

##select data
select the wetland you want to find water level and water temp from and the date and time

plot the water level and water temp for the entire day

#start here amy!!

```{r select time, echo=FALSE}
#enter wetland dataframe
wetland <- "WL_Wetland04" #WL_Wetland01, WL_Wetland02
#enter date of collection
date <- "2022-06-16"

#code below extract desired wetland, do not change
wetland_data <- WL_Wetland%>%filter(Station==wetland)

#this is where you run it line by line

#Water Level

plot_ly(data=wetland_data %>%
  filter(DateTime > as.POSIXct(paste(date,"00:00:01"), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date,"23:59:59"), format="%Y-%m-%d %H:%M:%S", tz = "UTC")),
  x=~DateTime,y=~WaterLevel_m)

#Water Temp

plot_ly(data=wetland_data %>%
  filter(DateTime > as.POSIXct(paste(date,"00:00:01"), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date,"23:59:59"), format="%Y-%m-%d %H:%M:%S", tz = "UTC")),
  x=~DateTime,y=~WLTemp_c)

#Most likely during the sample period there is data missing or the numbers look very different from before and after sampling. This is because we pulled up and downloaded the logger during the same time - changing both the pressure and temperature

#select an hour time period just before logger was downloaded. 

DateTime_BEFORE <- "2022-07-14 08:00:00"
DateTime_AFTER <- "2022-07-14 09:00:00"

#calculate average


ave <- wetland_data %>%
  filter(DateTime >= as.POSIXct(DateTime_BEFORE, format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime <= as.POSIXct(DateTime_AFTER, format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  summarize(WaterlLevel_mean = mean(WaterLevel_m),
            WaterTemp_mean = mean(WLTemp_c))

print(ave)


```