---
title: "FindFluxData_2022-09-17"
author: "Kriddie"
date: "2022-09-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate) #package for our date parsing
library(here)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(purrr)
library(sjmisc)
library(plotly)
library(lubridate)
```

## Description

The purpose of this script is to find flux data, at the time of sampling each wetland 

After reading in the data, we will plot it to see if the flux is within a range that "makes sense" for the environment that we are measuring.


#Read in Data


```{r read in data}
FluxData <- read.csv(here::here("Wetlands/Wetland_Flux.csv"), skip=0, header = TRUE)
FluxData$X <- NULL
FluxData$DateTime <- as.POSIXct(FluxData$DateTime, format="%Y-%m-%d %H:%M:%S", tz = "UTC")
#FluxData$DateTime_adjusted <- FluxData$DateTime - hours(1)
```

## Quickly plot to check Data


```{r Check Data, echo=FALSE}
ggplot(FluxData, aes(x=DateTime, y=Flux)) +
    geom_point(size=2, shape=23)

```

#select day of sample
```{r Check sample day, echo=FALSE}
#enter date of collection
date <- "2022-07-27"
test <- FluxData%>%filter(Date==date)
ggplot(FluxData%>%filter(Date==date),
       aes(x=DateTime, y=Flux)) +
  geom_point(size=2, shape=23)

```

```{r select time, echo=FALSE}
#enter date of collection
date <- "2022-07-27"
#enter start and end time that wetland was sampled
time_START <- "08:00:00"
time_END <- "15:00:00"


plot_ly(data=FluxData%>%filter(Date==date)%>%
  filter(DateTime > as.POSIXct(paste(date, time_START), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date, time_END), format="%Y-%m-%d %H:%M:%S", tz = "UTC")),
  x=~DateTime,y=~Flux)

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
