---
title: "FindBaroData"
author: "Kriddie"
date: "2022-08-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## Description

The purpose of this script is to identify the airpresser, air temp, at the time of sampling each wetland 

After reading in the data, we will plot it to see if the air temperature and air pressure is within a range that "makes sense" for the environment that we are measuring.

For each wetland sampled we will take an average of the Airpressure and airtemperature collected during the sample period

For example: if samples were sampled wetland 1 on 7/14/2022 between 10am and 11am, we need an average of air temperature and air pressure from that time period

#read in data for Baro

```{r Read in Data}
BaroData <- read.csv(here::here("Wetlands/Wetland_Baro.csv"), skip=0, header = TRUE)
BaroData <- BaroData[,2:4]

BaroData$DateTime <- as.POSIXct(BaroData$DateTime, format="%Y-%m-%d %H:%M:%S", tz = "UTC")
```

## Check Data

#Plot all data


```{r Check Data, echo=FALSE}
ggplot(BaroData, aes(x=DateTime, y=AirPres_kpa)) +
    geom_point(size=2, shape=23)
ggplot(BaroData, aes(x=DateTime, y=AirTemp_c)) +
    geom_point(size=2, shape=23,color="blue")

```
## Check Data

#Plot 1 day

Now we zoom into the day that we sampled data
does the data "make sense"?


```{r Check sample day, echo=FALSE}
#enter date of collection
date <- "2022-06-28"


ggplot(BaroData %>%
  filter(DateTime > as.POSIXct(paste(date,"00:00:01"), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date,"23:59:59"), format="%Y-%m-%d %H:%M:%S", tz = "UTC")),
       aes(x=DateTime, y=AirPres_kpa)) +
  geom_point(size=2, shape=23)


ggplot(BaroData %>%
  filter(DateTime > as.POSIXct(paste(date,"00:00:01"), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date,"23:59:59"), format="%Y-%m-%d %H:%M:%S", tz = "UTC")),
       aes(x=DateTime, y=AirTemp_c)) +
  geom_point(size=2, shape=23, color="blue")

```
#plot Time sampled for single wetland

now select the time period a single wetland was sampled

make sure there are no dramatice change in air temperature or air pressure during this time period

If there is, we may need to exclude some data within the sample period

If not, then we can use the average calculated at the end of the chunk

```{r Check sample day, echo=FALSE}
#enter date of collection
date <- "2022-07-14"
#enter start and end time that wetland was sampled
time_START <- "10:16:00"
time_END <- "10:48:00"


ggplot(BaroData %>%
  filter(DateTime > as.POSIXct(paste(date,time_START), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date,time_END), format="%Y-%m-%d %H:%M:%S", tz = "UTC")),
       aes(x=DateTime, y=AirPres_kpa)) +
  geom_point(size=2, shape=23)


ggplot(BaroData %>%
  filter(DateTime > as.POSIXct(paste(date,time_START), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date,time_END), format="%Y-%m-%d %H:%M:%S", tz = "UTC")),
       aes(x=DateTime, y=AirTemp_c)) +
  geom_point(size=2, shape=23, color="blue")

```

```{r SUMMARIZE, echo=FALSE}

#SUMMARIZE 


ave <- BaroData%>%
  filter(DateTime > as.POSIXct(paste(date, time_START), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct(paste(date, time_END), format="%Y-%m-%d %H:%M:%S", tz = "UTC"))%>%
  summarize(AirPres_mean = mean(AirPres_kpa),
            AirTemp_mean = mean(AirTemp_c))

print(ave)

```
