---

title: "CO2_EC"
author: "Kayla Emerson"
date: "6/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About

In this file I clean and collect CO2 data collected at Cayambe Coca, EC salt injection from June 6, 2022

### We start by reading in an then cleaning data, file 

```{r pressure, echo=FALSE}
setwd(here::here("Injections/2022-06-06/CO2"))

all_files=list.files(pattern=".csv")        #pulls out the csv files from WL folder in HOBOware folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)


#shorten site name by removing underscores
sites_rp = sapply(strsplit(all_files, "_"), function(x) x[3])

site_names=unique(sites_rp) #creates list of site names for following loop



#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=7, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=7, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}
```

## Clean up CO2 data- remove everything after 16:00 on 2022-06-06
This is when we stopped collecting data

```{r pressure, echo=FALSE}
xn10m = filter(xn10m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

x10m = filter(x10m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

x50m = filter(x50m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

x100m = filter(x100m, DateTime <= as.POSIXct("2022-06-06 16:00:00", tz = "UTC"))

```

## Plot CO2 for Viasala @ -10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(xn10m,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Viasala @ 10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(x10m,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```




## Plot CO2 for 50m Viasala
```{r check CO2 data plot, echo=FALSE}
##check data
plot_ly(x50m,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 
```


## Plot CO2 for 100m Viasala
this data may be irrelevant because we don't think the CO2 made it to 100m
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(x100m,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}

# join data frames to make plotting easier

df_new <- rbind(xn10m, x10m, x50m)

# use facet wrap to plot multiple stations

together_plot <- ggplot(df_new, aes(DateTime, ppm, color = Station)) +
  geom_point(size = 1) +
  xlab("time") +
  ylab("ppm")

together_plot + facet_wrap(~Station, ncol= 3, scales = "fixed")

together_plot

```



## Data Cleaning -- need to work on this section and correct for pressure and temp
Use the data from vaisala correction 

```{r plot, echo=FALSE}

```


## Finding the mean for before, during, and after the plateau
NEED to fix this section
FIND mean before plateau, during the plateau, and after the plateau
EXPORT to excel somehow to make a nice table or something 

```{r plot, echo=FALSE}

# find average of plateaus for each station

### Change data frame, date and wanted time frame as needed 
cleaned_n10 <- filter(xn10m, DateTime >= as.POSIXct("2022-05-26 11:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-05-26 11:40:00", tz = "UTC"))

#now clean up all of the stations
cleaned_0 <- filter(x0m, DateTime >= as.POSIXct("2022-05-26 11:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-05-26 11:40:00", tz = "UTC"))
cleaned_50 <- filter(x50m, DateTime >= as.POSIXct("2022-05-26 11:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-05-26 11:40:00", tz = "UTC"))

#now find the mean of this filtered subset
meann10m = mean(cleaned_n10$ppm)
mean0m = mean(cleaned_0$ppm)
mean50m = mean(cleaned_50$ppm)


```



