---

title: "CO2_EC"
author: "Kayla Emerson"
date: "6/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About

In this file I clean and collect CO2 data collected at Cayambe Coca, EC salt injection from June 6, 2022

### We start by reading in an then cleaning data, file 

```{r pressure, echo=FALSE}
setwd(here::here("Injections/2022-06-06/CO2"))

all_files=list.files(pattern=".csv")        #pulls out the csv files from WL folder in HOBOware folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)


#shorten site name by removing underscores
sites_rp = sapply(strsplit(all_files, "_"), function(x) x[3])

site_names=unique(sites_rp) #creates list of site names for following loop



#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=7, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=7, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}
```

## Clean up CO2 data- remove everything after 16:30 on 2022-06-06
This is when we stopped collecting data
We flipped station 10m and 50m because they were most likely mixed up when downloading data. We are also not analyzing the viasala data from 100m because it the CO2 slug did not make it through. But, the data is here if we want to use it at some point. 

```{r pressure, echo=FALSE}
xn10m = filter(xn10m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

x10m = filter(x10m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

x50m = filter(x50m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

x100m = filter(x100m, DateTime <= as.POSIXct("2022-06-06 16:30:00", tz = "UTC"))

# Now join all sites into a singular data frame so it is easier to analyze 
df_new <- rbind(xn10m, x10m, x50m)

```

## Notes from the notebook to decipher which viasala box was at each station

x50m is an old Viasala labeled box 1 
x10m is an old viasala labeled box 6
xn10m is a new viasala labeled box 1



## Correct viasalas temperature and pressure with HOBO data for the time period we collected data
```{r check CO2 data plot, echo=FALSE}

setwd(here::here("Injections/2022-06-06"))


# first, read in WL hobo at -10m 
waterlevel_n10 <- read.csv("Inj_TEMP_-10m_2022-06-06.csv", skip = 1)
waterlevel_n10 <- waterlevel_n10[,c(2:4)]
colnames(waterlevel_n10) <- c("DateTime", "WL_Pressure", "Temp")

# format DateTime in WL 
waterlevel_n10$DateTime <- as.POSIXct(paste(waterlevel_n10$Date, waterlevel_n10$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")

# correct kpa to hpa 
##1 kPa = 10 hPa
##1 kPa = 0.101972 m
waterlevel_n10$WL_Pressure <- waterlevel_n10$WL_Pressure * 10

#full_join to join CO2 data to WL by datetime
df_corr <- full_join(df_new, waterlevel_n10, by = "DateTime" )

# clean data <- remove NA values bc vaisala reads every 1s and WL reads ever 10s
df_corr <- na.omit(df_corr) 

# create a new column for adjusted ppm
df_corr$adjusted_ppm <- 0
df_corr$adjusted_ppm <- as.numeric(df_corr$adjusted_ppm)
df_corr$ppm <- as.numeric(df_corr$ppm)


```
## Correct old Vaisalas 
Old vaisalas need to be corrected for temperature and pressure 
Also need to be corrected for individual calibration -- calibration equations are from vaisalacalibration csv
x10m and x50m are old 

```{r check CO2 data plot, echo=FALSE}

# Make a new data frame from df_corr but just with old vaisalas

df_oldv <- df_corr %>% 
      filter(Station =='x10m' | Station == 'x50m')

# Now correct the adjusted ppm 
df_oldv$adjusted_ppm <- df_oldv$ppm * (1 + (1013 - df_oldv$WL_Pressure) * 0.0015) * (1 - (25 - df_oldv$Temp) * 0.003)

# Now correct for individual vaisala calibration 

# x50m was an old viasala labeled box 6

df_x50m <- df_oldv %>% 
      filter(Station =='x50m')

df_x50m$adjusted_ppm <-  (df_x50m$adjusted_ppm * 0.99484) - 252.9031

# x10m was an old Viasala labeled K600

df_x10m <- df_oldv %>% 
      filter(Station =='x10m')

df_x10m$adjusted_ppm <- (df_x10m$adjusted_ppm * 1.06933) - 105.52898

```

## Correct new Vaisalas
New vaisalas need to be corrected for just pressure 
Also need to be corrected for individual calibaration
xn10m is new, ignore x100m

```{r check CO2 data plot, echo=FALSE}
# Make a new data frame from df_corr but just with new vaisalas
df_newv <- df_corr %>% 
      filter(Station =='xn10m')

# Now correct the adjusted ppm 
df_newv$adjusted_ppm <- (df_newv$ppm * 2 )* (1 + (700 - df_newv$WL_Pressure) * 0.0015)

# Now correct for individual vaisala calibration

# xn10m a new viasala labeled box 1
df_xn10m <- df_newv %>% 
      filter(Station =='xn10m')

df_xn10m$adjusted_ppm <- (df_xn10m$adjusted_ppm * 1.00054) - 65.15813

```

## Plot CO2 for Viasala @ -10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_xn10m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Viasala @ 10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x10m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```




## Plot CO2 for 50m Viasala
```{r check CO2 data plot, echo=FALSE}
##check data
plot_ly(df_x50m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```






## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}
# join data frames to make plotting easier

df_plot <- rbind(df_xn10m, df_x10m, df_x50m)

# use facet wrap to plot multiple stations

together_plot <- ggplot(df_plot, aes(DateTime, adjusted_ppm, color = Station)) +
  geom_point(size = 2) +
  xlab(NULL) +
  ylab(NULL)

together_plot + facet_wrap(~Station, ncol= 3, scales = "free")

together_plot

```



## Finding the mean for before, during, and after the plateau

EXPORT to excel somehow to make a nice table or something 

```{r plot, echo=FALSE}

# find average for each station before plateau

preplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:15:00", tz = "UTC"))
preplat_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:15:00", tz = "UTC"))
preplat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:15:00", tz = "UTC"))

#calculate mean
preplatmeann10m = mean(preplat_n10$adjusted_ppm)
preplatmean10m = mean(preplat_10$adjusted_ppm)
preplatmean50m = mean(preplat_50$adjusted_ppm)

### Change data frame, date and wanted time frame as needed 
plat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))
plat_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))
plat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))

#now find the mean of this filtered subset
platmeann10m = mean(plat_n10$adjusted_ppm)
platmean10m = mean(plat_10$adjusted_ppm)
platmean50m = mean(plat_50$adjusted_ppm)

# find average at each station after the slug

#first, clean up data by focusing on wanted time
postplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))
postplat_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))
postplat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))

#find mean of post plateau
postplatmeann10m = mean(postplat_n10$adjusted_ppm)
postplatmean10m = mean(postplat_10$adjusted_ppm)
postplatmean50m = mean(postplat_50$adjusted_ppm)

```


## Calculating CO2 in the air (look at data before or after vaisalas went into the water)
```{r plot, echo=FALSE}
# Create new data frames for time when vaisalas are out of water
air_n10 <-filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 15:26:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:27:00", tz = "UTC"))
air_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 12:36:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 12:38:00", tz = "UTC"))
air_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 15:25:30", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:26:00", tz = "UTC"))

# Now find mean for this time frame 
airmean_n10m = mean(air_n10$adjusted_ppm)
airmean_10m = mean(air_10$adjusted_ppm)
airmean_50m = mean(air_50$adjusted_ppm)

```

## Create data table with important objects and export to excel 
focus on calculated vars: pre plateau, plateau, post plateau, and air 
```{r plot, echo=FALSE}
# Create a data frame 
vaisala <- c('xn10m', 'x10m', 'x50m')
air_co2_ppm <- c(airmean_n10m, airmean_10m, airmean_50m)
pre_plateau_co2_ppm <- c(preplatmeann10m, preplatmean10m, preplatmean50m) 
plateau_co2_ppm <- c(platmeann10m, platmean10m, platmean50m)
post_plateau_co2_ppm <- c(postplatmeann10m, postplatmean10m, postplatmean50m)

co2_table <- data.frame(vaisala, air_co2_ppm, pre_plateau_co2_ppm, plateau_co2_ppm, post_plateau_co2_ppm)

co2_table

# Export table to excel- you can stop here if you don't want to do CO2 conversions 
#write.csv(co2_table,here::here("Injections/2022-06-06/injection_co2_result.csv"))

#melt data so it is easier to manipulate for CO2 conversions
library(reshape)
co2_table_melt <- melt(co2_table, id=c("vaisala"))


```

## CO2 conversions (concentration to load)
```{r plot, echo=FALSE}

### Calculate concentration (gCO2-C per Liter) in air using ###

#concentration of air
#from www.esrl.noaa.gov
#average of July and August
#410.86 ppm
CO2_air_ppm <- 410*10^-6
R=0.08205736608096
gCO2asC <- 12

#convert hpa to atm; 1hPa = 0.0009869233 atm
co2_table$air_pressure_atm <- synoptic.df$Total_hPa * 0.0009869233

synoptic.df$VaporPressure_atm <- 10^(5.40221-(1838.675/((synoptic.df$AirTemp_c + 273.15)-31.737)))

synoptic.df$TotalAir_atm <- synoptic.df$air_pressure_atm - synoptic.df$VaporPressure_atm
synoptic.df$Total_air_MolperL <- synoptic.df$TotalAir_atm/(R*(synoptic.df$AirTemp_c + 273.15)) 
synoptic.df$CO2_air_MolesPerLiter <- synoptic.df$Total_air_MolperL * CO2_air_ppm
# 12 grams of C in 1 mole of CO2
synoptic.df$CO2_air_gCO2asCPerLiter <- synoptic.df$CO2_air_MolesPerLiter * gCO2asC


### Calculate concentration CO2 in water (gCO2-C per Liter) using Henry's law ###
#Equation below can be used to adjust Henry's constant to the temperature of the environment
# *NOTE: we may need to do an additional calculation to adjust for low pressure in our environment?*
#**KH = KH(STP) x exp(D(1/T-1/T(STP)))**
#* KH(STP) = Henry's law constant at STP (0.035 mol/L)
#*NOTE: the cited literature say that this in mol/(kg x bar)*
#  * D = Temperature dependence constant (2400 K)
#* T = Water Temperature (K)
#* T(STP) = Temp at STP (298.15 K)

# Find average water temp for injection

df_avg_water <- filter(df_corr, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:00:00", tz = "UTC"))
avg_water_temp <- mean(df_avg_water$Temp)

#set constants
kH_STP_mol.L.atm = .035
D_K = 2400 
avg_water_temp_K <- avg_water_temp + 273.15
T_STP_K = 298.15

#calculate henry's law constant using 
KH_mol.L.atm <- kH_STP_mol.L.atm * exp(D_K*(1/avg_water_temp_K - 1/T_STP_K))


UatmToatm <- 10^6

#calculate mass equivalence of CO2 in water
co2_table_melt$CO2_water_gCO2asCPerLiter <- (co2_table_melt$value / UatmToatm) * KH_mol.L.atm * gCO2asC

# find load by multiplying by Q

#Load for 10m 
# Q at 10m = 0.003140479
 
for (i in co2_table_melt){
  if(co2_table_melt$vaisala == 'x10m'){
    co2_table_melt$q <- 0.003140479
    co2_table_melt$load <- co2_table_melt$CO2_water_gCO2asCPerLiter * 0.003140479 * 1000
  }
  if(co2_table_melt$vaisala == 'x50m'){
    co2_table_melt$q <- .003311749
    co2_table_melt$load <- co2_table_melt$CO2_water_gCO2asCPerLiter * .003311749 * 1000
  }
  else{
    co2_table_melt$q <- 0
    co2_table_melt$load <- 0
  }
}


#Load for 50m
# Q for 50m = .003311749


# export to excel
#write.csv(co2_table,here::here("Injections/2022-06-06/injection_co2_result.csv"))
```
