---
title: "CO2_CayambeCoca"
author: "KWhitmore"
date: "1/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About
In this file I clean and collect CO2 data collected at the Cayambe Coca field site

### We start by reading in an then cleaning data, file 

```{r cars}
setwd(here::here("Injections/RR 2022-05-26"))
## Read files into R

File_name <- "CO2_02_2021-07-14.csv"

CO2Data <- read.csv(File_name, skip=6, header = TRUE)
CO2Data=CO2Data[,1:3]
colnames(CO2Data) <- c("Date","Time","ppm")

#DOWNLOAD DATA using UNC computer
CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")

#DOWNLOAD DATA using USFQ computer
#CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")


#Clean data
#CO2Data <- CO2Data %>% filter(DateTime < as.POSIXct("2021-10-02 21:45:00", tz = "UTC") | DateTime > as.POSIXct("2021-10-20 13:15:00", tz = "UTC"))


#plot pressure
#plot_ly(CO2_02%>% filter(ppm <  5000), x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'lines+markers')
plot_ly(CO2_03, x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'lines+markers')
plot_ly(CO2Data, x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'lines+markers')

```
# cleaning notes
there are some files that I am suspicious of because they are way too high compared with the rest..

CO2_02 files:
CO2_02_2021-06-30.csv
CO2_02_2021-07-16.csv

## Do loop

```{r pressure, echo=FALSE}

setwd(here::here("Injections/RR 2022-05-26/CO2"))

all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)

#shorten site name by removing underscores

sites_rp = sapply(strsplit(all_files, "_"), function(x) x[4])

site_names=unique(sites_rp) #creates list of site names for following loop
#site_names=site_names[-2]

# rename sites so they are easier to use (getting rid of #s and -s in the front)
### sad im not very good at that 
#xn10m <- "-10m"
#"x0m" <- "0m"
#"x50m" <- "50m"



#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}


```
## Plot CO2 for Mobile Viasala

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(mobile,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Mobile 2 Viasala 
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(mobile2,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for -10m Viasala 
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(xn10m,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for 0m Viasala
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(x0m,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for 50m Viasala
```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(x50m,
  #filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 

```


## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}

## join data frames to make plotting easier?
df = mobile %>% full_join(mobile2, by="DateTime") %>% full_join(xn10m, by="DateTime") %>% full_join(x0m, by="DateTime") %>% full_join(x50m, by="DateTime")

##check data
#plot_ly(mobile2, x = ~DateTime, y = ~ppm,  name = 'Mobile2', type = 'scatter', mode = 'markers')%>%
 #   add_trace(mobile, x = ~DateTime, y = ~ppm, name = 'Mobile', type = 'scatter', mode = 'markers')
            

plot_ly(df, x = ~DateTime, y = ~ppm,  name = 'Mobile2', type = 'scatter', mode = 'markers')
#%>%
 # add_trace(df(mobile), x = ~DateTime, y = ~ppm, name = 'Mobile', type = 'scatter', mode = 'markers')     

#fig <- plot_ly(mobile, x = ~DateTime, y = ~ppm, name = 'Mobile', type = 'scatter', mode = 'markers')
#fig <- fig %>% add_trace(mobile2, x = ~DateTime, y = ~ppm, name = 'Mobile2', type = 'scatter', mode = 'markers', inherit=FALSE)
#fig <- fig %>% add_trace(xn10m, x = ~DateTime, y = ~ppm, name = '-10 m', type = 'scatter', mode = 'markers', inherit=FALSE)
#fig <- fig %>% add_trace(x0m, x = ~DateTime, y = ~ppm, name = '0 m', type = 'scatter', mode = 'markers', inherit=FALSE)
#fig <- fig %>% add_trace(x50m, x = ~DateTime, y = ~ppm, name = '50 m', type = 'scatter', mode = 'markers', inherit=FALSE)
#fig()

#filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC")), 
```
clean data

```{r clean, echo=FALSE}
#CO2_01
CO2_01  <- CO2_01%>%
  filter(DateTime < as.POSIXct("2021-06-09 11:30:00", tz = "UTC") | DateTime >= as.POSIXct("2021-06-09 12:15:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-07-13 10:30:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-16 11:30:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-07-23 10:30:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-27 13:00:00", tz = "UTC"))%>%
#sensor out of water
  filter(DateTime < as.POSIXct("2021-06-19 04:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-25 10:30:00", tz = "UTC"))


#CO2_02
CO2_02  <- CO2_02 %>% 
  filter(DateTime < as.POSIXct("2021-06-11 03:34:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-16 11:52:00", tz = "UTC")) %>%
    filter(DateTime < as.POSIXct("2021-06-29 14:40:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-29 15:00:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-06-30 10:42:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-30 11:45:00", tz = "UTC")) %>%
#  filter(DateTime < as.POSIXct("2021-07-14 11:06:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 11:11:00", tz = "UTC")) %>% 
#  filter(DateTime < as.POSIXct("2021-07-14 13:18:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 14:13:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-07-16 11:56:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-16 11:57:00", tz = "UTC")) %>%
  filter(DateTime != as.POSIXct("2021-07-16 12:00:05", tz = "UTC")) %>% 
  filter(DateTime != as.POSIXct("2021-07-19 10:30:05", tz = "UTC"))  %>%
  filter(DateTime != as.POSIXct("2021-06-25 10:04:00", tz = "UTC"))  %>%
#injection July 13
  filter(DateTime < as.POSIXct("2021-07-13 10:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-13 15:15:00", tz = "UTC"))%>%
#injection July 14
  filter(DateTime < as.POSIXct("2021-07-14 09:00:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 15:30:00", tz = "UTC"))

CO2_02 <- CO2_02
CO2_02$DateTime <- round_date(CO2_02$DateTime,unit="15 minutes")
CO2_02 <- CO2_02 %>% 
  group_by(DateTime) %>% 
  summarise(ppm = mean(ppm))
CO2_02$Station <- "CO2_02"


#CO2_03
CO2_03  <- CO2_03 %>%
  filter(DateTime < as.POSIXct("2021-06-25 13:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-02 12:15:00", tz = "UTC"))

#CO2_04
CO2_04 <- CO2_04%>%
  filter(DateTime != as.POSIXct("2021-06-10 16:00:00", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct("2021-07-12 15:59:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-16 13:00:00", tz = "UTC"))%>%
  filter(DateTime < as.POSIXct("2021-07-28 12:15:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-28 13:15:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2021-10-20 12:45:05", tz = "UTC")) %>%
#injection July 14
  filter(DateTime < as.POSIXct("2021-07-14 09:00:00", tz = "UTC") | DateTime > as.POSIXct("2021-07-14 15:30:00", tz = "UTC"))


CO2_04$DateTime <- round_date(CO2_04$DateTime,unit="15 minutes")
CO2_04 <- CO2_04 %>% 
  group_by(DateTime) %>% 
  summarise(ppm = mean(ppm))
CO2_04$Station <- "CO2_04"

#CO2_Well01
CO2_Well01 <- CO2_Well01 %>%
  filter(DateTime > as.POSIXct("2021-06-25 12:30:00", tz = "UTC"))

#CO2_Well02
CO2_Well02 <- CO2_Well02 %>%
  filter(DateTime > as.POSIXct("2021-06-29 11:00:00", tz = "UTC")) %>%
#  filter(DateTime < as.POSIXct("2021-06-17 20:21:00", tz = "UTC") | DateTime > as.POSIXct("2021-06-18 08:21:00", tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2021-06-30 15:15:00", tz = "UTC")) %>%
  filter(DateTime != as.POSIXct("2021-07-02 12:00:00", tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2021-10-02 21:45:00", tz = "UTC") | DateTime > as.POSIXct("2021-10-20 13:15:00", tz = "UTC"))

CO2_Well02$DateTime <- round_date(CO2_Well02$DateTime,unit="15 minutes")
CO2_Well02 <- CO2_Well02 %>% 
  group_by(DateTime) %>% 
  summarise(ppm = mean(ppm))
CO2_Well02$Station <- "CO2_Well02"

#plot pressure
plot_ly(CO2_01 #%>% filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC"))
        , x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'markers')
plot_ly(CO2_02 #%>%filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC"))
  , x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'markers')
plot_ly(CO2_03 #%>% filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC"))
        , x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'markers')
plot_ly(CO2_04 #%>%filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC"))
        , x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'markers')
plot_ly(CO2_Well01 #%>% filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC"))
        , x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'markers')
plot_ly(CO2_Well02 #%>% filter(DateTime < as.POSIXct("2021-07-30 07:27:00", tz = "UTC"))
        , x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'markers')

```


#bind and plot

```{r plot, echo=FALSE}
stations <- rbind(CO2_01,CO2_02,CO2_03,CO2_04)

wells <- rbind(CO2_Well01,CO2_Well02)


ggplot(data = stations#%>%filter(Station=='CO2_04')
       %>%filter(ppm < 15000)
         , aes(DateTime, ppm)) +
  geom_point(color = "steelblue") +
  labs(#title = "CO2  stations",
       y = "CO2 ppm", x = "") + 
  facet_wrap(~ Station)
#

ggplot(data = wells%>%filter(ppm < 15000), aes(DateTime, ppm)) +
  geom_point(color = "steelblue") +
  #  geom_point(color="steelblue") + 
  labs(#title = "CO2  stations",
    y = "CO2 ppm", x = "") + 
  facet_wrap(~ Station)

plot_ly(stations%>%filter(Station=='CO2_04')
        ,
        x = ~DateTime, y= ~ppm, type = 'scatter', mode = 'lines+markers')

```
