---

title: "CO2_EC"
author: "Kayla Emerson"
date: "7/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About

This file is the template for processing CO2 injection data and calculating k600 

### We start by reading in an then cleaning data, file 

```{r pressure, echo=FALSE}
#enter date of injection wich is also the name of the folder for the injection

folder <- "2022-07-01"

setwd(here::here(paste("Injections/"), folder ,"/CO2"))

all_files=list.files(pattern=".csv")        #pulls out the csv files from CO2 folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)


#shorten site name by removing underscores
sites_rp = sapply(strsplit(all_files, "_"), function(x) x[3])

site_names=unique(sites_rp) #creates list of site names for following loop



#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y%H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
   CO2Data$ppm <- as.numeric(as.character(CO2Data$ppm))
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}
```

## Clean up CO2 data

Select data collected during injection period
```{r pressure, echo=FALSE}

#DateTime when injection ended

#end <-  as.POSIXct("2022-07-01 17:30:00", tz = "UTC")


#xn10m = filter(xn10m, DateTime <= end)

#x0m = filter(x0m, DateTime <= end)

#x25m = filter(x25m, DateTime <= end)

#x50m = filter(x50m, DateTime <= end)

# Now join all sites into a singular data frame so it is easier to analyze 
df_new <- rbind(xn10m, x0m, x25m, x50m)

```

## Notes from the notebook to decipher which viasala box was at each station


x50m is a new Viasala labeled Station 3 
x25m is a new Viasala labeled Box 3
x0m is a new viasala labeled Box 1
xn10m is an old viasala labeled K600



## Correct viasalas temperature and pressure with HOBO data for the time period we collected data
```{r check CO2 data plot, echo=FALSE}


setwd(here::here(paste("Injections/"),folder))


# first, read in WL hobo at -10m 
waterlevel_n10 <- read.csv(here::here(paste("Injections/"), folder ,"/Injection_Temp_xn10_2022-07-01.csv"),skip=1)
waterlevel_n10 <- waterlevel_n10[,c(2:4)]
colnames(waterlevel_n10) <- c("DateTime", "WL_Pressure", "Temp")

# format DateTime in WL 
waterlevel_n10$DateTime <- as.POSIXct(paste(waterlevel_n10$Date, waterlevel_n10$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")

# correct kpa to hpa 
##1 kPa = 10 hPa
##1 kPa = 0.101972 m
waterlevel_n10$WL_Pressure <- waterlevel_n10$WL_Pressure * 10

#full_join to join CO2 data to WL by datetime
df_corr <- full_join(df_new, waterlevel_n10, by = "DateTime" )

# clean data <- remove NA values bc vaisala reads every 1s and WL reads ever 10s
df_corr <- na.omit(df_corr) 


```
## Correct old Vaisalas 
Old vaisalas need to be corrected for temperature and pressure 
Also need to be corrected for individual calibration -- calibration equations are from vaisalacalibration csv
xn10m is old

```{r check CO2 data plot, echo=FALSE}

# Make a new data frame from df_corr but just with old vaisalas

df_oldv <- df_corr %>% 
      filter(Station =='xn10m')

# Now correct the adjusted ppm 
df_oldv$adjusted_ppm <- df_oldv$ppm * (1 + (1013 - df_oldv$WL_Pressure) * 0.0015) * (1 - (25 - df_oldv$Temp) * 0.003)

# Now correct for individual vaisala calibration 

# x10m was an old Viasala labeled K600

df_xn10m <- df_oldv %>% 
      filter(Station =='xn10m')

df_xn10m$adjusted_ppm <-(df_xn10m$adjusted_ppm * 1.06933) -105.52898


```

## Correct new Vaisalas
New vaisalas need to be corrected for just pressure


vaisala @ 0 m
Box 1 New

vaisala @ 25m 
Box 3 new

vaisala @ 50m 
R37391 Station 3

```{r check CO2 data plot, echo=FALSE}
# Make a new data frame from df_corr but just with new vaisalas
df_newv <- df_corr %>% 
      filter(Station =='x0m'|
               Station =='x25m'|
               Station =='x50m')

# Now correct the adjusted ppm 
df_newv$adjusted_ppm <- (df_newv$ppm  )* (1 + (1013 - df_newv$WL_Pressure) * 0.0015)

# Now correct for individual vaisala calibration

# x0m,  Box 1 New
df_x0m <- df_newv %>% 
      filter(Station =='x0m')

df_x0m$adjusted_ppm <- (df_x0m$adjusted_ppm * 1.00054) + 65.15813

# x25m, Box 3 new
df_x25m <- df_newv %>% 
      filter(Station =='x25m')

df_x25m$adjusted_ppm <- (df_x25m$adjusted_ppm * 1.05036) -6.27667


# 50m, R37391 Station 3
df_x50m <- df_newv %>% 
      filter(Station =='x50m')

df_x50m$adjusted_ppm <- (df_x50m$adjusted_ppm * 0.948723) - 13.68636

```

## Plot CO2 for Viasala @ -10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_xn10m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Viasala @ 0m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x0m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```

## Plot CO2 for Viasala @ 25m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x25m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for 50m Viasala
```{r check CO2 data plot, echo=FALSE}
##check data
plot_ly(df_x50m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```






## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}
# join data frames to make plotting easier

df_plot <- rbind(df_xn10m, df_x0m, df_x25m, df_x50m)

# use facet wrap to plot multiple stations

together_plot <- ggplot(df_plot, aes(DateTime, adjusted_ppm, color = Station)) +
  geom_point(size = 2) +
  xlab(NULL) +
  ylab(NULL)

together_plot + facet_wrap(~Station, ncol= 3, scales = "free")

together_plot

```



## Finding the mean for before, during, and after the plateau

EXPORT to excel somehow to make a nice table or something 

```{r plot, echo=FALSE}

# find average for each station before plateau (around 11:20-11:25)

preplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-07-01 11:20:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 11:25:00", tz = "UTC"))
preplat_0 <- filter(df_x0m, DateTime >= as.POSIXct("2022-07-01 11:20:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 11:25:00", tz = "UTC"))
preplat_25 <- filter(df_x25m, DateTime >= as.POSIXct("2022-07-01 11:20:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 11:25:00", tz = "UTC"))
preplat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-07-01 11:20:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 11:25:00", tz = "UTC"))

#calculate mean
preplatmeann10m = mean(preplat_n10$adjusted_ppm)
preplatmean0m = mean(preplat_0$adjusted_ppm)
preplatmean25m = mean(preplat_25$adjusted_ppm)
preplatmean50m = mean(preplat_50$adjusted_ppm)

### Change data frame, date and wanted time frame as needed 
plat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-07-01 12:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:30:00", tz = "UTC"))
plat_0 <- filter(df_x0m, DateTime >= as.POSIXct("2022-07-01 12:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:30:00", tz = "UTC"))
plat_25 <- filter(df_x25m, DateTime >= as.POSIXct("2022-07-01 12:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:30:00", tz = "UTC"))
plat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-07-01 12:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:30:00", tz = "UTC"))

#now find the mean of this filtered subset
platmeann10m = mean(plat_n10$adjusted_ppm)
platmean0m = mean(plat_0$adjusted_ppm)
platmean25m = mean(plat_25$adjusted_ppm)
platmean50m = mean(plat_50$adjusted_ppm)

# find average at each station after the slug

#first, clean up data by focusing on wanted time
postplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-07-01 12:55:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:58:00", tz = "UTC"))
postplat_0 <- filter(df_x0m, DateTime >= as.POSIXct("2022-07-01 12:55:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:58:00", tz = "UTC"))
postplat_25 <- filter(df_x25m, DateTime >= as.POSIXct("2022-07-01 12:55:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:58:00", tz = "UTC"))
postplat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-07-01 12:55:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 12:58:00", tz = "UTC"))

#find mean of post plateau
postplatmeann10m = mean(postplat_n10$adjusted_ppm)
postplatmean0m = mean(postplat_0$adjusted_ppm)
postplatmean25m = mean(postplat_25$adjusted_ppm)
postplatmean50m = mean(postplat_50$adjusted_ppm)

```


## Calculating CO2 in the air (look at data before or after vaisalas went into the water)
```{r plot, echo=FALSE}
# Create new data frames for time when vaisalas are out of water
air_n10 <-filter(df_xn10m, DateTime >= as.POSIXct("2022-07-01 9:40:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 9:53:00", tz = "UTC"))
air_0 <- filter(df_x0m, DateTime >= as.POSIXct("2022-07-01 9:40:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 9:53:00", tz = "UTC"))
air_25 <- filter(df_x25m, DateTime >= as.POSIXct("2022-07-01 9:40:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 9:53:00", tz = "UTC"))
air_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-07-01 9:40:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-01 9:53:00", tz = "UTC"))

# Now find mean for this time frame 
airmean_n10m = mean(air_n10$adjusted_ppm)
airmean_0m = mean(air_0$adjusted_ppm)
airmean_25m = mean(air_25$adjusted_ppm)
airmean_10m = mean(air_50$adjusted_ppm)

```

## Create data table with important objects and export to excel 
focus on calculated vars: pre plateau, plateau, post plateau, and air 
```{r plot, echo=FALSE}
# Create a data frame 
vaisala <- c('xn10m', 'x0m', 'x25m', 'x50m')
air_co2_ppm <- c(airmean_n10m, airmean_0m, airmean_25m, airmean_10m)
pre_plateau_co2_ppm <- c(preplatmeann10m, preplatmean0m, preplatmean25m, preplatmean50m) 
plateau_co2_ppm <- c(platmeann10m, platmean0m, platmean25m, platmean50m)
post_plateau_co2_ppm <- c(postplatmeann10m, postplatmean0m, postplatmean25m, postplatmean50m)

co2_table <- data.frame(vaisala, air_co2_ppm, pre_plateau_co2_ppm, plateau_co2_ppm, post_plateau_co2_ppm)

co2_table

write.csv(co2_table,here::here("Injections/2022-06-06/injection_co2_result.csv"))

# Export table to excel

```
##calc kc02 for river stretch using kriddie's own brain 
I'm going off road, baby

#First comes the flux

We are pulling from methods in stream ecology now 
eq) 31.1  describes decay rate of leaves over time
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: final weight
  wi: initial weight
  t: time
  
adjusted for decay rate of CO2 over meters
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: co2 mass at 50 m (concentration * discharge)
  wi: co2 mass at 0m  (concentration * discharge)
  t: meters

```{r kdub rules the roost}
#convert ppm to mg/l is the easiest thing in the world becaust it is 1:1

#difference between plateau and baseline for upstream and downstream
C_mgperL_0m <- (platmean0m - mean(preplatmean0m,postplatmeann10m))

C_mgperL_50m <- (platmean50m - mean(preplatmean50m))

#Discharge comes from salt injection
#multiply by 1000 to convert from m3/s to L/s
#Q at 0m = 0.07623
Q_0m = 0.07623 * 1000
# Q for 50m = 0.090885
Q_50m = 0.090885 * 1000 

#stream reach length
dist = 65

km <- -log(C_mgperL_50m*Q_50m/(C_mgperL_0m*Q_0m))/dist
#km units: 1/m
```
#convert k in meters to time
kgas,t = kgas,m * v

kgas,t: decay rate over time
kgas,m: decay rate over meters (calculates in chunk above)
v: mean velocity of stream

```{r meters to time }
#mean velocity of stream reach from salt injection is time it took salt to reach peak 
#use data from software 

# discharge at 50m; poured in salt at 12:04, peak at 12:13; 88.7?
# discharge at 50m; poured in salt at 12:47, peak at 12:57; 86.56?


#v = d/t
#t = time peak - time poured
#d = 65m
#find v

#start: 13:26
start <- as.POSIXct("2022-06-06 13:26:00",tz="UTC")
#End: 14:48
end <- as.POSIXct("2022-06-06 14:48:00",tz="UTC")





#find Mean Travel Time (MTT)
x <- sintegral(df$seconds, df$LowRange, n.pts = nrow(df))
df_int <- data.frame(matrix(ncol = 2, nrow = nrow(df)))
colnames(df_int) <- c("sec","sum")
df_int$sec <- x$x
df_int$sum <- x$y
AUC <- x$int

MTT <- df_int[which.min(abs(AUC/2-df_int$sum)),]$sec

dist = 50

v = dist/MTT #units (m/s)
kt = km * v #units (1/s)
kCO2_mperd <- kt*86400
  
```

#k600
convert to k to k600
```{r convert to k6000}

# Find average water temp for injection

df_avg_water <- filter(df_corr, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:00:00", tz = "UTC"))
WaterTempC_ave <- mean(df_avg_water$Temp)

#calc sc
Sc <- 1911.1 - 118.11*WaterTempC_ave + 3.4527*(WaterTempC_ave)^2 - 0.04132*(WaterTempC_ave)^3

K600 <- kCO2_mperd * (600/Sc)^(-0.5)
```
