---
title: "k600_calculation_2024"
author: "Kriddie"
date: "2024-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(dplyr) 
library(tidyr) 
library(ggplot2)
library(cowplot)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(dplyr)
library(lubridate)
library(readr)
```

## gas transfer velocity calculation

we need to figure this shit out

# Read in data


```{r read in data}

df <- read.csv(here::here("Wetlands/Wetland_df_MERGE_2024-04-14.csv"))%>%
  select(Site,DateTime,Date,
         CO2_ppm,CH4_umol.L,CH4_sat,Flux_umol_m2_s,DOC_mg.L,TDN_mg.L,
         AirPress_kpa,AirTemp_c,Watertemp_c,waterTemp_c_day,WaterTemp_c_ave3,waterTemp_c_yearly,
         Baro_kpa,BaroTemp_c,
         Elevation_m,depth_ave_m,surface_area_m2,Volumn_m3,SA_to_Vol_ratio,
         surface_area_day,Volumn_m3_day,
         WS_area_minus_pond,percentpond,percent_DTW,
         PrecipAccuDay_mm,PrecipAccu_mm_PreviousDay,precip_mm_ave2,Precip_mm_ave7, solarrad_W_m2,solarrad_Wm2_daymean,windspeed_m_s, winddirecion)%>%rename(pCO2_ppm=CO2_ppm)

df$DateTime <- as.POSIXct(df$DateTime)

```

#calibrate CO2 sensors
I think I came up with an defense for not calibrating sensors (see text). I really don't want to because the old sensor had a low y-intercept and if I calibrate it then the sites are even lower in co2, wich would mean i'd have to do even more explaining, and I just don't think, science-wise there is a lot to be gained. So i'd like to avoid all that. Anyway, if we find that we need to do all this, look at the script - "CalibrationCode2.r" in the VaisalaCalibration folder. It's actually pretty well organized.

## working with the final data set (synoptic)

output for viasala is:

molecular density - so molecules/volume of gas. Here the volume of the gas is what is inside the cuvette. So, the sensor is basically giving out the number of molecules in the optical path.

```{r the kriddie way for final, echo=FALSE}
#pV=nRT
#p=nRT/V
#R m3⋅Pa⋅K−1⋅mol−1
#R=8.31446261815324 	

#adjust henry to temp: KH = KH(STP) x exp(D(1/T-1/T(STP)))
#use constants in  	Burkholder et al. (2019) and convert to desired units
#  k°H (mol/(kg*bar) = mol/l/atm
#d(ln(kH))/d(1/T) (K)
kH_STP_mol.l.atm = .035*1/0.986923
D_K = 2400 
T_STP_K = 298.15

df$pCO2_air_ppm <- 418.53 # 2022 average manoa


#########
#airpressure was collected at each site, so no need to adjust for elevation

df$air_pressure_atm <- df$AirPress_kpa / 101.3

df$water_pressure_atm <- df$AirPress_kpa / 101.3 + 0.000967841


########

df$pCO2_air_atm <-  df$pCO2_air_ppm / 10^6  * df$air_pressure_atm


df$pCO2_w_atm <- df$pCO2_ppm / 10^6 

#henry's constant adjust for temp
df$KH_mol.l.atm <- kH_STP_mol.l.atm * exp(D_K*(1/(df$Watertemp_c+273.15) - 1/T_STP_K))
df$KH_mol.m3.atm <- df$KH_mol.l.atm * 1000

df$CO2_sat_mol.L <- df$KH_mol.l.atm*df$pCO2_air_atm

df$CO2_mol.L <- df$KH_mol.l.atm*df$pCO2_w_atm
df$CO2_umol.L <- df$CO2_mol.L*10^6


df$CO2_sat_precent <- df$CO2_mol.L/df$CO2_sat_mol.L*100


#change units of flux (umol/m2/s - > mol/m2/d)
#86400 seconds in a day
df$Flux_mol_m2_d <- df$Flux_umol_m2_s / 10^6 * 86400

#now calculate k in m/d
df$k_m_d <- df$Flux_mol_m2_d / (df$KH_mol.m3.atm * (df$pCO2_w_atm -  df$pCO2_air_atm )) 

# Wanninkhof et al. (2014)
df$Sc_co2 <- 1923.6 - 125.06*df$Watertemp_c + 4.3773*(df$Watertemp_c)^2 - 0.085681*(df$Watertemp_c)^3 + 0.00070284 * (df$Watertemp_c)^4


#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
df$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(df$Watertemp_c+273.15)-1/T_STP_K))

#Ambient CH4 concentration ppb	1910.97 	
#average 2021 from Moaa
CH4_air_ppb <- 1910.97 

df$CH4_air_atm <- df$air_pressure_atm * CH4_air_ppb * 10^-9

df$CH4_sat_umol.L <- df$CH4_air_atm*df$KH_CH4_mol.L.atm * 10^6

df$CH4_pSat <- df$CH4_umol.L/df$CH4_sat_umol.L *100

#calculate the partial pressure of ch4

df$pCH4_ppm <- df$CH4_umol.L /df$KH_CH4_mol.L.atm

#One can calculate the gas transfer velocity of one gas (gas1) from another (gas2) using kgas1/kgas2 = (Scgas1/Scgas2)^-n. where Sc is the Schmidt number and n is the Schmidt number exponent, which is generally assigned a value of 1/2 to 2/3 depending on the surface state of the water (Jahne et al. 1987), - Raymond et al 2012

# Wanninkhof et al. (2014)
df$Sc_ch4 <- 1909.4 - 120.78*df$Watertemp_c + 4.1555*(df$Watertemp_c)^2 - 0.080578*(df$Watertemp_c)^3 + 0.00065777**(df$Watertemp_c)^4

df$k_ch4 <- (df$Sc_ch4/df$Sc_co2)^(-2/3) * df$k_m_d

df$K600 <- df$k_m_d * (600/df$Sc_co2)^(-.57)
#df$K600_.67 <- df$k_m_d * (600/df$Sc_co2)^(-2/3)


#df <- df%>%filter(DateTime < "2022-10-01 00:00:00")





p1 <- ggplot(df) + geom_point(aes(x=CO2_ppm,y=K600,color=DateTime)) + scale_x_log10()
p2 <- ggplot(df) + geom_point(aes(x=CO2_ppm,y=k_m_d,color=DateTime)) + scale_x_log10()


#write.csv(df,here::here("ProcessedData/PondPaper_k600.csv"))


```

