---
title: "k600_calculation_2024"
author: "Kriddie"
date: "2024-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(dplyr) 
library(tidyr) 
library(ggplot2)
library(cowplot)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(dplyr)
library(lubridate)
library(readr)
```

##gas transfer velocity calculation

we need to figure this shit out


#calibrate CO2 sensors
I think I came up with an defense for not calibrating sensors (see text). I really don't want to because the old sensor had a low y-intercept and if I calibrate it then the sites are even lower in co2, wich would mean i'd have to do even more explaining, and I just don't think, science-wise there is a lot to be gained. So i'd like to avoid all that. Anyway, if we find that we need to do all this, look at the script - "CalibrationCode2.r" in the VaisalaCalibration folder. It's actually pretty well organized.

## working with the final data set 

output for viasala is:

molecular density - so molecules/volume of gas. Here the volume of the gas is what is inside the cuvette. So, the sensor is basically giving out the number of molecules in the optical path.

pubs that include Johnson as an author describes output as a Volume fraction 
ppmv: parts per million (106) by volume; the fraction of volume of gas occupied by a component multiplied by 1,000,000. If there is 3 ppm of CO2 in a bottle filled with gas, then for every 1,000,000 molecules in the bottle, 3 of those molecules are CO2. 


Atmosphere
manoa lab data is: 
mole fraction
moles per mole (mol/mol or mol*mol−1)

In Johnsen et al. (2010) they describe converting the output of the viasala which is ppmv or ppmV, and converting it to mg/l^-1

*The mass equivalence of dissolved inorganic carbon in the dissolved CO2 form is typically reported as mg l^-1 of CO2-C, and is calculated via Henry’s Law (Plummer and Busenberg, 1982) based on the temperature of the water where the sensor is located and the partial pressure of CO2 in solution. For example, 1000 ppm is equivalent to 2.84 mg CO2-C l^-1 at 5 °C; 2.01 mg CO2-C l^-1 at 15 °C; and 1.50 mg CO2-C l^-1 at 25 °C.*


# Read in data

#All samples
These data sets includes all samples for ch4 and co2

```{r the kriddie way for final, echo=FALSE}

summer_df <- read.csv(here::here("Methane/Methane_df_2023-07-20.csv"))%>% select("Site","Location","Date_collected","CH4_umol_L.1","CH4_.sat","Watertemp_c","AirPress_Field_kPa")%>%
  filter(Site!="Colmillo")%>%filter(Site!="Gavi-main")%>%filter(Site!="Gavi-trib") %>% 
  rename(Date = Date_collected, CH4_umol.L = CH4_umol_L.1, CH4_sat = CH4_.sat,AirPress_kpa = AirPress_Field_kPa)

#remove 2 outliers
summer_df$uniqueID <- paste(summer_df$Site,summer_df$Location,summer_df$Date,sep="_")
summer_df <- summer_df%>%filter(uniqueID!="Wetland_11_3_7/19/22")
summer_df_subset1 <- summer_df%>%filter(uniqueID=="Wetland_10_2_7/8/22"&CH4_umol.L>1)
summer_df_subset2 <- summer_df%>%filter(uniqueID!="Wetland_10_2_7/8/22")
summer_df <- rbind(summer_df_subset1,summer_df_subset2)
rm(summer_df_subset1,summer_df_subset2)
summer_df$Date <- as.Date.character(summer_df$Date,format="%m/%d/%y")


#convert to pCH4
#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
T_STP_K = 298.15
summer_df$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(summer_df$Watertemp_c+273.15)-1/T_STP_K))

#Ambient CH4 concentration ppb	1910.97 	
#average 2021 from Moaa
CH4_air_ppb <- 1910.97 

summer_df$air_pressure_atm <- summer_df$AirPress_kpa / 101.3

summer_df$water_pressure_atm <- summer_df$AirPress_kpa / 101.3 + 0.000967841

summer_df$CH4_air_atm <- summer_df$air_pressure_atm * CH4_air_ppb * 10^-9

summer_df$CH4_sat_umol.L <- summer_df$CH4_air_atm*summer_df$KH_CH4_mol.L.atm * 10^6

summer_df$CH4_pSat <- summer_df$CH4_umol.L/summer_df$CH4_sat_umol.L *100


#calculate the partial pressure of ch4

summer_df$CH4_mol.L <- summer_df$CH4_umol.L / 10^6
summer_df$pCH4_w_atm <- summer_df$CH4_mol.L/summer_df$KH_CH4_mol.L.atm
summer_df$pCH4_w_uatm <- summer_df$pCH4_w_atm * 10^6
summer_df$pCH4_ppm <- summer_df$pCH4_w_atm * 10^6 / summer_df$water_pressure_atm

#now calculate the mean of everything for further analysis

#summer data
CH4_summary <- summer_df%>%group_by(Site,Date,Location)%>%
dplyr::summarize(
  CH4_umol.L = mean(CH4_umol.L), 
  CH4_sat = mean(CH4_sat),
  Watertemp_c = mean(Watertemp_c),
  AirPress_kpa = mean(AirPress_kpa),
  KH_CH4_mol.L.atm = mean(KH_CH4_mol.L.atm),
  air_pressure_atm = mean(air_pressure_atm),
  water_pressure_atm = mean(water_pressure_atm),
  CH4_air_atm = mean(CH4_air_atm),
  CH4_sat_umol.L = mean(CH4_sat_umol.L),
  CH4_pSat = mean(CH4_pSat),
  CH4_mol.L = mean(CH4_mol.L),
  pCH4_w_atm = mean(pCH4_w_atm),
  pCH4_w_uatm = mean(pCH4_w_uatm),
  pCH4_ppm = mean(pCH4_ppm),
  n = n())%>%rename(rep=n)

CH4_summary2 <- CH4_summary %>%group_by(Site,Date)%>%
dplyr::summarize(
    pCH4_w_uatm_sd = sd(pCH4_w_uatm),
 CH4_umol.L = mean(CH4_umol.L), 
  CH4_sat = mean(CH4_sat),
  Watertemp_c = mean(Watertemp_c),
  AirPress_kpa = mean(AirPress_kpa),
  KH_CH4_mol.L.atm = mean(KH_CH4_mol.L.atm),
  air_pressure_atm = mean(air_pressure_atm),
  water_pressure_atm = mean(water_pressure_atm),
  CH4_air_atm = mean(CH4_air_atm),
  CH4_sat_umol.L = mean(CH4_sat_umol.L),
  CH4_pSat = mean(CH4_pSat),
  CH4_mol.L = mean(CH4_mol.L),
  pCH4_w_atm = mean(pCH4_w_atm),
  pCH4_w_uatm = mean(pCH4_w_uatm),
  pCH4_ppm = mean(pCH4_ppm),
  n = n()
 )

#############
#############
#############


#fall samples
fall_df <- read.csv(here::here("Methane/Methane_fall2022_update.csv"))%>%
  select("Site","Location","Date_collected","CH4_umol.L","CH4_sat","Watertemp_Field_c","AirPress_Field_kpa")%>%
  rename(Date = Date_collected,Watertemp_c=Watertemp_Field_c,AirPress_kpa = AirPress_Field_kpa)%>%
  filter(Site!="Chakanas")%>%filter(Site!="Gavilan")
fall_df$Date <- as.Date.character(fall_df$Date,format="%m/%d/%y")
#convert to pCH4
#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
fall_df$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(fall_df$Watertemp_c+273.15)-1/T_STP_K))

fall_df$air_pressure_atm <- fall_df$AirPress_kpa / 101.3

fall_df$water_pressure_atm <- fall_df$AirPress_kpa / 101.3 + 0.000967841

fall_df$CH4_air_atm <- fall_df$air_pressure_atm * CH4_air_ppb * 10^-9

fall_df$CH4_sat_umol.L <- fall_df$CH4_air_atm*fall_df$KH_CH4_mol.L.atm * 10^6

fall_df$CH4_pSat <- fall_df$CH4_umol.L/fall_df$CH4_sat_umol.L *100


#calculate the partial pressure of ch4

fall_df$CH4_mol.L <- fall_df$CH4_umol.L / 10^6
fall_df$pCH4_w_atm <- fall_df$CH4_mol.L/fall_df$KH_CH4_mol.L.atm
fall_df$pCH4_w_uatm <- fall_df$pCH4_w_atm * 10^6
fall_df$pCH4_ppm <- fall_df$pCH4_w_atm * 10^6 / fall_df$water_pressure_atm

#summarise
CH4_fall_summary2 <- fall_df %>%group_by(Site,Date)%>%
dplyr::summarize(
    pCH4_w_uatm_sd = sd(pCH4_w_uatm),
 CH4_umol.L = mean(CH4_umol.L), 
  CH4_sat = mean(CH4_sat),
  Watertemp_c = mean(Watertemp_c),
  AirPress_kpa = mean(AirPress_kpa),
  KH_CH4_mol.L.atm = mean(KH_CH4_mol.L.atm),
  air_pressure_atm = mean(air_pressure_atm),
  water_pressure_atm = mean(water_pressure_atm),
  CH4_air_atm = mean(CH4_air_atm),
  CH4_sat_umol.L = mean(CH4_sat_umol.L),
  CH4_pSat = mean(CH4_pSat),
  CH4_mol.L = mean(CH4_mol.L),
  pCH4_w_atm = mean(pCH4_w_atm),
  pCH4_w_uatm = mean(pCH4_w_uatm),
  pCH4_ppm = mean(pCH4_ppm),
  n = n()
 )


#bind 
all_df <- rbind(CH4_summary2,CH4_fall_summary2)

all_df$Site <- gsub("_","",all_df$Site)

all_df$New.Name <- all_df$Site
#make column with new name to reflect elevation. S stands for "site"
all_df <- all_df%>%mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8','Wetland06' ~ 'S5','Wetland07' ~ 'S7','Wetland08' ~ 'S12','Wetland09' ~ 'S10','Wetland10' ~ 'S11','Wetland11' ~ 'S6','Wetland12' ~ 'Wetland'))



#read out ch4 data

#write.csv(all_df,here::here("ProcessedData/CH4samples_summary_June829.csv"))


```

#this is CO2 data


```{r CO2 data, echo=FALSE}


df_CO2 <- read.csv(here::here("Wetlands/CO2_intrapondvariance_reviewJune2025.csv"))%>%select(Wetland,Location,Date,Time,ppm_NOTcorrected_review)
df_CO2$Date <- as.Date(df_CO2$Date,format="%m/%d/%y")
df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))
df$Date <- as.Date(df$Date,format="%Y-%m-%d")
df_merge <- df%>%select(Site,Date,Watertemp_c,AirPress_kpa)%>%rename(Wetland=Site)
df_CO2 <- left_join(df_CO2,df_merge,by=c("Wetland","Date"))
rm(df,df_merge)

df_CO2 <- df_CO2%>%rename(Site="Wetland")%>%
  mutate(Location = case_when(Location == 1 ~ "edge",
                              Location == 2 ~ "middle",
                              Location == 3 ~ "edge",
                                   TRUE ~ NA_character_))
df_CO2$Site <- as.factor(df_CO2$Site)


#calc pCO2
kH_STP_mol.l.atm = .035*1/0.986923
D_K = 2400 
T_STP_K = 298.15

df_CO2$pCO2_air_ppm <- 418.53 # 2022 average manoa
df_CO2$air_pressure_atm <- df_CO2$AirPress_kpa / 101.3
df_CO2$water_pressure_atm <- df_CO2$AirPress_kpa / 101.3 + 0.000967841
df_CO2$pCO2_air_atm <-  df_CO2$pCO2_air_ppm / 10^6  * df_CO2$air_pressure_atm
df_CO2$pCO2_air_uatm <-  df_CO2$pCO2_air_ppm * df_CO2$air_pressure_atm

df_CO2$ppm_Corrected <- df_CO2$ppm_NOTcorrected_review * (1 + (1013 - (df_CO2$AirPress_kpa+2*0.0980665)*10) * 0.0015) * (1 - (25 - df_CO2$Watertemp_c) * 0.003)
df_CO2$pCO2_w_atm <- df_CO2$ppm_Corrected /10^6* df_CO2$water_pressure_atm 
df_CO2$pCO2_w_uatm <- df_CO2$ppm_Corrected * df_CO2$water_pressure_atm 

##we need to calculate CO2 in uatm

#henry's constant adjust for temp
df_CO2$KH_mol.l.atm <- kH_STP_mol.l.atm * exp(D_K*(1/(df_CO2$Watertemp_c+273.15) - 1/T_STP_K))
df_CO2$KH_mol.m3.atm <- df_CO2$KH_mol.l.atm * 1000

df_CO2$CO2_sat_mol.L <- df_CO2$KH_mol.l.atm*df_CO2$pCO2_air_atm

df_CO2$CO2_mol.L <- df_CO2$KH_mol.l.atm*df_CO2$pCO2_w_atm
df_CO2$CO2_umol.L <- df_CO2$CO2_mol.L*10^6


df_CO2$CO2_sat_precent <- df_CO2$CO2_mol.L/df_CO2$CO2_sat_mol.L*100

##summarise

CO2_summary <- df_CO2%>%drop_na(ppm_Corrected)%>%group_by(Site,Date)%>%
dplyr::summarize(
    n = n(),
    pCO2_w_uatm_sd = sd(pCO2_w_uatm,na.rm=TRUE),
     pCO2_w_uatm = mean(pCO2_w_uatm,na.rm=TRUE),
    pCO2_ppm = mean(ppm_Corrected,na.rm=TRUE),
      Watertemp_c = mean(Watertemp_c,na.rm=TRUE),
  AirPress_kpa = mean(AirPress_kpa,na.rm=TRUE),
 pCO2_air_ppm = mean(pCO2_air_ppm,na.rm=TRUE),
 air_pressure_atm = mean(air_pressure_atm,na.rm=TRUE),
 water_pressure_atm = mean(water_pressure_atm,na.rm=TRUE),
 pCO2_air_atm = mean(pCO2_air_atm,na.rm=TRUE),
 pCO2_air_uatm= mean(pCO2_air_uatm,na.rm=TRUE),
   pCO2_w_atm = mean(pCO2_w_atm,na.rm=TRUE),
 KH_CO2_mol.L.atm = mean(KH_mol.l.atm,na.rm=TRUE),
 KH_CO2_mol.m3.atm = mean(KH_mol.m3.atm,na.rm=TRUE),
 CO2_sat_mol.L = mean(CO2_sat_mol.L,na.rm=TRUE),
 CO2_mol.L= mean(CO2_mol.L,na.rm=TRUE),
 CO2_umol.L = mean(CO2_umol.L,na.rm=TRUE),
 CO2_sat_precent = mean(CO2_sat_precent,na.rm=TRUE),
 )


CO2_summary$New.Name <- CO2_summary$Site
#make column with new name to reflect elevation. S stands for "site"
CO2_summary <- CO2_summary%>%mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8','Wetland06' ~ 'S5','Wetland07' ~ 'S7','Wetland08' ~ 'S12','Wetland09' ~ 'S10','Wetland10' ~ 'S11','Wetland11' ~ 'S6','Wetland12' ~ 'Wetland'))

df_CO2$New.Name <- df_CO2$Site
#make column with new name to reflect elevation. S stands for "site"
df_CO2 <- df_CO2%>%mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8','Wetland06' ~ 'S5','Wetland07' ~ 'S7','Wetland08' ~ 'S12','Wetland09' ~ 'S10','Wetland10' ~ 'S11','Wetland11' ~ 'S6','Wetland12' ~ 'Wetland'))

#write.csv(df_CO2,here::here("ProcessedData/All_CO2_samples_June23.csv"))
```



#wetland data

```{r wetland data, echo=FALSE}


drone_GHG <- read.csv(here::here("ProcessedData/Drone_Gavi_sampling_GHG.csv"))%>%select(Lat,Lon,Site, Site2, Date, AirPress_kpa,Watertemp_c,CO2_ppm,CH4_umol.L, CO2_umol.L)%>%rename(pCO2_ppm=CO2_ppm)

#cal uatm for both ch4 and co2
#adjust henry to temp: KH = KH(STP) x exp(D(1/T-1/T(STP)))
#use constants in  	Burkholder et al. (2019) and convert to desired units
#  k°H (mol/(kg*bar) = mol/l/atm
#d(ln(kH))/d(1/T) (K)
kH_STP_mol.l.atm = .035*1/0.986923
D_K = 2400 
T_STP_K = 298.15

drone_GHG$pCO2_air_ppm <- 418.53 # 2022 average manoa


#########
#airpressure was collected at each site, so no need to adjust for elevation

drone_GHG$air_pressure_atm <- drone_GHG$AirPress_kpa / 101.3

drone_GHG$water_pressure_atm <- drone_GHG$AirPress_kpa / 101.3 + 0.000967841


########

drone_GHG$pCO2_air_atm <-  drone_GHG$pCO2_air_ppm / 10^6  * drone_GHG$air_pressure_atm
drone_GHG$pCO2_air_uatm <-  drone_GHG$pCO2_air_ppm * drone_GHG$air_pressure_atm
drone_GHG$pCO2_w_atm <- drone_GHG$pCO2_ppm / 10^6 * drone_GHG$water_pressure_atm 
drone_GHG$pCO2_w_uatm <-  drone_GHG$pCO2_ppm * drone_GHG$water_pressure_atm 

#henry's constant adjust for temp
drone_GHG$KH_mol.l.atm <- kH_STP_mol.l.atm * exp(D_K*(1/(drone_GHG$Watertemp_c+273.15) - 1/T_STP_K))
drone_GHG$KH_mol.m3.atm <- drone_GHG$KH_mol.l.atm * 1000

drone_GHG$CO2_sat_mol.L <- drone_GHG$KH_mol.l.atm*drone_GHG$pCO2_air_atm

drone_GHG$CO2_mol.L <- drone_GHG$KH_mol.l.atm*drone_GHG$pCO2_w_atm
drone_GHG$CO2_umol.L <- drone_GHG$CO2_mol.L*10^6


drone_GHG$CO2_sat_precent <- drone_GHG$CO2_mol.L/drone_GHG$CO2_sat_mol.L*100


#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
drone_GHG$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(drone_GHG$Watertemp_c+273.15)-1/T_STP_K))

#Ambient CH4 concentration ppb	1910.97 	
#average 2021 from Moaa
CH4_air_ppb <- 1910.97 

drone_GHG$CH4_air_atm <- drone_GHG$air_pressure_atm * CH4_air_ppb * 10^-9

drone_GHG$CH4_sat_umol.L <- drone_GHG$CH4_air_atm*drone_GHG$KH_CH4_mol.L.atm * 10^6

drone_GHG$CH4_pSat <- drone_GHG$CH4_umol.L/drone_GHG$CH4_sat_umol.L *100

#calculate the partial pressure of ch4

drone_GHG$CH4_mol.L <- drone_GHG$CH4_umol.L / 10^6
drone_GHG$pCH4_w_atm <- drone_GHG$CH4_mol.L/drone_GHG$KH_CH4_mol.L.atm
drone_GHG$pCH4_w_uatm <- drone_GHG$pCH4_w_atm * 10^6
drone_GHG$pCH4_ppm <- drone_GHG$pCH4_w_atm * 10^6 / drone_GHG$water_pressure_atm

#write.csv(drone_GHG,here::here("ProcessedData/Drone_Gavi_sampling_GHG_june6.csv"),row.names = FALSE)

```

# environmental variables

```{r read in data}

df <- read.csv(here::here("Wetlands/Wetland_df_MERGE_2024-04-14.csv"))

df$New.Name <- df$Site
#make column with new name to reflect elevation. S stands for "site"
df <- df%>%mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8','Wetland06' ~ 'S5','Wetland07' ~ 'S7','Wetland08' ~ 'S12','Wetland09' ~ 'S10','Wetland10' ~ 'S11','Wetland11' ~ 'S6','Wetland12' ~ 'Wetland'))


df <- df%>%
  select(Site,New.Name,DateTime,Date,
         CO2_ppm,CH4_umol.L,CH4_sat,Flux_umol_m2_s,DOC_mg.L,TDN_mg.L,
         AirPress_kpa,AirTemp_c,Watertemp_c,waterTemp_c_day,WaterTemp_c_ave3,waterTemp_c_yearly,
         Baro_kpa,BaroTemp_c,
         Elevation_m,depth_ave_m,surface_area_m2,Volumn_m3,SA_to_Vol_ratio,
         surface_area_day,Volumn_m3_day,
         WS_area_minus_pond,percentpond,percent_DTW,
         PrecipAccuDay_mm,PrecipAccu_mm_PreviousDay,precip_mm_ave2,Precip_mm_ave7, solarrad_W_m2,solarrad_Wm2_daymean,windspeed_m_s, winddirecion)%>%rename(pCO2_ppm=CO2_ppm)

df$DateTime <- as.POSIXct(df$DateTime)


#there was one sample for Wetland11 that needed to be removed. So I just want to replace the values for that.
CH4_df<- read.csv(here::here("ProcessedData/All_CH4_samples_May29.csv"))

CH4_df$uniqueID <- paste(CH4_df$Site,CH4_df$Location,CH4_df$Date,sep="_")
CH4_df <- CH4_df%>%filter(uniqueID!="Wetland11_3_2022-07-19")
CH4_df <- CH4_df%>%filter(uniqueID!="Wetland10_2_2022-07-08")

ggplot(CH4_df,aes(x=New.Name,y=CH4_umol.L,color=Date))+geom_point() + scale_y_log10()

#summer data
CH4_reps <- CH4_df%>%group_by(Site,Location,Date)%>%
dplyr::summarize(
  min = min(pCH4_w_uatm), max = max(pCH4_w_uatm),
  mean = mean(pCH4_w_uatm),
  sd = sd(pCH4_w_uatm),
  n = n())%>%
  filter(n>1)
CH4_reps$se <-  CH4_reps$sd / sqrt(2)
CH4_reps$type <- "reps"

CH4_se <- CH4_df%>%group_by(Site,Date)%>%
dplyr::summarize(
  min = min(pCH4_w_uatm), max = max(pCH4_w_uatm),
  mean = mean(pCH4_w_uatm),
  sd = sd(pCH4_w_uatm),
  n = n())
CH4_se$se <-  CH4_se$sd / sqrt(2)
CH4_se$type <- "allsamples"


CH4_summary <- rbind(CH4_reps,CH4_se)

```


```{r 2025 calculation in revison, echo=FALSE}
#pV=nRT
#p=nRT/V
#R m3⋅Pa⋅K−1⋅mol−1
#R=8.31446261815324 	

#adjust henry to temp: KH = KH(STP) x exp(D(1/T-1/T(STP)))
#use constants in  	Burkholder et al. (2019) and convert to desired units
#  k°H (mol/(kg*bar) = mol/l/atm
#d(ln(kH))/d(1/T) (K)
kH_STP_mol.l.atm = .035*1/0.986923
D_K = 2400 
T_STP_K = 298.15

df$pCO2_air_ppm <- 418.53 # 2022 average manoa


#########
#airpressure was collected at each site, so no need to adjust for elevation

df$air_pressure_atm <- df$AirPress_kpa / 101.3

df$water_pressure_atm <- df$AirPress_kpa / 101.3 + 0.000967841


########

df$pCO2_air_atm <-  df$pCO2_air_ppm / 10^6  * df$air_pressure_atm
df$pCO2_air_uatm <-  df$pCO2_air_ppm * df$air_pressure_atm
df$pCO2_w_atm <- df$pCO2_ppm / 10^6 * df$water_pressure_atm 
df$pCO2_w_uatm <-  df$pCO2_ppm * df$water_pressure_atm 

#henry's constant adjust for temp
df$KH_mol.l.atm <- kH_STP_mol.l.atm * exp(D_K*(1/(df$Watertemp_c+273.15) - 1/T_STP_K))
df$KH_mol.m3.atm <- df$KH_mol.l.atm * 1000

df$CO2_sat_mol.L <- df$KH_mol.l.atm*df$pCO2_air_atm

df$CO2_mol.L <- df$KH_mol.l.atm*df$pCO2_w_atm
df$CO2_umol.L <- df$CO2_mol.L*10^6


df$CO2_sat_precent <- df$CO2_mol.L/df$CO2_sat_mol.L*100


#change units of flux (umol/m2/s - > mol/m2/d)
#86400 seconds in a day
df$Flux_mol_m2_d <- df$Flux_umol_m2_s / 10^6 * 86400

#now calculate k in m/d
df$k_m_d <- df$Flux_mol_m2_d / (df$KH_mol.m3.atm * (df$pCO2_w_atm -  df$pCO2_air_atm )) 

# Wanninkhof et al. (2014)
df$Sc_co2 <- 1923.6 - 125.06*df$Watertemp_c + 4.3773*(df$Watertemp_c)^2 - 0.085681*(df$Watertemp_c)^3 + 0.00070284 * (df$Watertemp_c)^4


#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
df$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(df$Watertemp_c+273.15)-1/T_STP_K))

#Ambient CH4 concentration ppb	1910.97 	
#average 2021 from Moaa
CH4_air_ppb <- 1910.97 

df$CH4_air_atm <- df$air_pressure_atm * CH4_air_ppb * 10^-9

df$CH4_sat_umol.L <- df$CH4_air_atm*df$KH_CH4_mol.L.atm * 10^6

df$CH4_pSat <- df$CH4_umol.L/df$CH4_sat_umol.L *100

#calculate the partial pressure of ch4

df$CH4_mol.L <- df$CH4_umol.L / 10^6
df$pCH4_w_atm <- df$CH4_mol.L/df$KH_CH4_mol.L.atm
df$pCH4_w_uatm <- df$pCH4_w_atm * 10^6
df$pCH4_ppm <- df$pCH4_w_atm * 10^6 / df$water_pressure_atm

#One can calculate the gas transfer velocity of one gas (gas1) from another (gas2) using kgas1/kgas2 = (Scgas1/Scgas2)^-n. where Sc is the Schmidt number and n is the Schmidt number exponent, which is generally assigned a value of 1/2 to 2/3 depending on the surface state of the water (Jahne et al. 1987), - Raymond et al 2012

# Wanninkhof et al. (2014)
df$Sc_ch4 <- 1909.4 - 120.78*df$Watertemp_c + 4.1555*(df$Watertemp_c)^2 - 0.080578*(df$Watertemp_c)^3 + 0.00065777**(df$Watertemp_c)^4

df$k_ch4 <- (df$Sc_ch4/df$Sc_co2)^(-2/3) * df$k_m_d

df$K600 <- df$k_m_d * (600/df$Sc_co2)^(-.57)

p1 <- ggplot(df) + geom_point(aes(x=pCO2_ppm,y=K600,color=DateTime)) + scale_x_log10()
p2 <- ggplot(df) + geom_point(aes(x=pCO2_ppm,y=k_m_d,color=DateTime)) + scale_x_log10()


#write.csv(df,here::here("ProcessedData/PondPaper_k600_May29.csv"))

```
