---
title: "Pond Paper Figures"
author: "Kriddie"
date: "2024-04-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(lubridate)
library(dplyr)
library(ggplot2)
library(reshape2)
library("ggpubr")
library(rstatix)
library(devtools)
library(PMCMRplus)
library(lme4)
library(lmerTest)
library(jtools)
library(extraoperators)
library(JWileymisc)
library(multilevelTools)
library(broom)
#library(tidyverse)


```

#site descriptors
this includes:
> ave SA
> ave depth
> ave vol
> cathment size
> elevation
> percent change in SA
> percent change in vol
> percent veg
> DOC/TDN

```{r table 1}
WL_df <- read.csv(here::here("Wetlands/WaterLevel_FINAL/WL_Wetland_all_FINAL.csv"))%>%select(DateTime,Station,WLTemp_c,depth_ave_m,surface_area_m2,Volumn_m3)%>%rename(Site=Station)%>%rename(WaterTemp_c=WLTemp_c)
WL_df$Site <- gsub(".*_","",WL_df$Site)


WL_df_sum <- WL_df%>%group_by(Site)%>%
  dplyr::summarise(
    SA_mean = mean(surface_area_m2,na.rm=TRUE),
    SA_max = max(surface_area_m2,na.rm=TRUE),
    SA_min = min(surface_area_m2,na.rm=TRUE),
    depth_mean = mean(depth_ave_m,na.rm=TRUE),
    vol_mean = mean(Volumn_m3,na.rm=TRUE),
    vol_max = max(Volumn_m3,na.rm=TRUE),
    vol_min = min(Volumn_m3,na.rm=TRUE),
  )
WL_df_sum$SA_diff <- (WL_df_sum$SA_max - WL_df_sum$SA_min)/(WL_df_sum$SA_max) * 100
WL_df_sum$vol_diff <- (WL_df_sum$vol_max - WL_df_sum$vol_min)/(WL_df_sum$vol_max) * 100


sum_table <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))%>%select(Site,Elevation_m,WS_area_minus_pond,DOC_mg.L,TDN_mg.L)
sum_table <- sum_table%>%group_by(Site)%>%
  dplyr::summarise(
    Elevation_m = mean(Elevation_m,na.rm=TRUE),
    Catchment_size = max(WS_area_minus_pond,na.rm=TRUE),
    DOC_mg.L = min(DOC_mg.L,na.rm=TRUE),
    TDN_mg.L = mean(TDN_mg.L,na.rm=TRUE)
  )


table1 <- full_join(sum_table,WL_df_sum,by="Site")

#write.csv(table1,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/table1.csv")
```


## Variance within wetlands

First - how do I report the variance found in ponds? we have reps and we have 3 sample location (and then 2 sample locations)

do i use standard error? how do I report standard error? 

below I have some code as a starting point


```{r analysis 1}
#this script takes the methane data and summarizes it 
#now this is included in Merge_WetlandDATA.R

CH4_summer_df <- read.csv(here::here("Methane/Methane_df_2023-07-20.csv"))%>% select("Site","Location","Date_collected","CH4_umol_L.1","CH4_.sat")%>%
  filter(Site!="Colmillo")%>%filter(Site!="Gavi-main")%>%filter(Site!="Gavi-trib") %>% 
  rename(Date = Date_collected, CH4_umol.L = CH4_umol_L.1, CH4_sat = CH4_.sat)
CH4_summer_df$Date <- as.Date.character(CH4_summer_df$Date,format="%m/%d/%y")


#fall samples
CH4_fall_df <- read.csv(here::here("Methane/Methane_fall2022_update.csv"))%>%
  select("Site","Location","Date_collected","CH4_umol.L","CH4_sat")%>%
  rename(Date = Date_collected)%>%
  filter(Site!="Chakanas")%>%filter(Site!="Gavilan")
CH4_fall_df$Date <- as.Date.character(CH4_fall_df$Date,format="%m/%d/%y")

#for the fall we did not have the same sampling strategy of site #2 being in the middle (I think), but we did do reps. so lets see what the variance is in reps to see if its the same

CH4_df <- rbind(CH4_summer_df,CH4_fall_df)

CH4_reps <- CH4_df%>%group_by(Site,Location,Date)%>%
dplyr::summarize(
  min = min(CH4_umol.L), max = max(CH4_umol.L),
  mean = mean(CH4_umol.L),
  sd = sd(CH4_umol.L),
  n = n())%>%
  filter(n>1)
CH4_reps$se <-  CH4_reps$sd / sqrt(2)
CH4_reps$type <- "reps"

CH4_se <- CH4_df%>%group_by(Site,Date)%>%
dplyr::summarize(
  min = min(CH4_umol.L), max = max(CH4_umol.L),
  mean = mean(CH4_umol.L),
  sd = sd(CH4_umol.L),
  n = n())
CH4_se$se <-  CH4_se$sd / sqrt(2)
CH4_se$type <- "allsamples"


CH4_summary <- rbind(CH4_reps,CH4_se)

CH4_summary$dif_prec <- (CH4_summary$max-CH4_summary$min)/CH4_summary$mean * 100


ggplot(CH4_summary, aes(x=Site, y=log(se),color=type)) + 
  geom_boxplot()

##now look at differences between wetland positon (this can only be done for spring samples)

ggplot(CH4_summer_df,aes(x=as.factor(Location),y=log(CH4_umol.L))) + geom_point()
ggplot(CH4_fall_df,aes(x=as.factor(Location),y=log(CH4_umol.L))) + geom_point()

## we also have the data to do this for CO2
df_CO2 <- read.csv(here::here("Wetlands/CO2_intrapondvariance.csv"))
df_CO2 <- df_CO2%>% 
  mutate(Location = case_when(Location == 1 ~ "edge",
                              Location == 2 ~ "middle",
                              Location == 3 ~ "edge",
                                   TRUE ~ NA_character_))
df_CO2$Date <- as.Date.character(df_CO2$Date,format="%m/%d/%y")

C02_reps <- df_CO2 %>%group_by(Wetland,Location,Date)%>%
dplyr::summarize(
  min = min(ppm_Corrected), max = max(ppm_Corrected),
  mean = mean(ppm_Corrected),
  sd = sd(ppm_Corrected),
  n = n())%>%
  filter(n>1)
C02_reps$se <-  C02_reps$sd / sqrt(2)
C02_reps$type <- "reps"

CO2_se <- df_CO2%>%group_by(Wetland,Date)%>%
dplyr::summarize(
  min = min(ppm_Corrected), max = max(ppm_Corrected),
  mean = mean(ppm_Corrected),
  sd = sd(ppm_Corrected),
  n = n())
CO2_se$se <-  CO2_se$sd / sqrt(2)
CO2_se$type <- "allsamples"


CO2_summary <- rbind(C02_reps,CO2_se)

CO2_summary$dif_prec <- (CO2_summary$max-CO2_summary$min)/CO2_summary$mean * 100


ggplot(CO2_summary, aes(x=Wetland, y=log(se),color=type)) + 
  geom_boxplot()

ggplot(df, aes(x=Site, y=log(CO2_mol.L),color=Date)) + 
  geom_point()
```

## Variance between sites

1. are locations at the edge of pond significantly different from locations in the middle?

> findings:
  1. 9 waterbodies fit parametric model assumptions, so we ran 1-way anova
  2. Site 2, 7, 11 do not, so we ran kusker-Wallis
  3. effect of location was insignificnat EXCEPT for W07
  
We will report mean and standard deviation for each wetland by day 
for wetland 7, we report both center and edge

```{r location variance, echo=FALSE}

CH4_df2 <- CH4_df
CH4_df2$Location[CH4_df2$Location == 3] <- 1
CH4_df3 <- CH4_df2%>%filter(Location == 1 | Location == 2)
CH4_df2 <- CH4_df3%>%filter(Date< "2022-10-01")

#now run stats
#not normal: wetland 2 & 7 & 11 
#all other wetland meet assumptions and also location is not significant

result <- aov(log1p(CH4_umol.L) ~ Location , data = CH4_df2%>%filter(Site=="Wetland_12"))
summary(result)

# Check normality of residuals
res <- residuals(result)
qqnorm(res) 
qqline(res)
shapiro.test(res) #normality
bartlett.test(log1p(CH4_umol.L)  ~ Location, data = CH4_df2%>%filter(Site=="Wetland_12"))  #monovariance

#run kuskerwallis on other wetland 2 & 7 & 11 
kruskal.test(log1p(CH4_umol.L) ~ Location , data = CH4_df2%>%filter(Site=="Wetland_07"))

#wetland 07 failed the test
W_07 <- CH4_df2%>%filter(Date<"2022-10-01")%>%filter(Site=="Wetland_07")%>%group_by(Location)%>%summarise(
  mean=mean(CH4_umol.L),
  median = median(CH4_umol.L)
)

ggplot(CH4_df%>%filter(Date<"2022-10-01")%>%filter(Site=="Wetland_07"),aes(x=as.factor(Location),y=log(CH4_umol.L),color=Site)) + geom_point() + facet_grid(~Site)

ggplot(CH4_df2%>%filter(Date>"2022-10-01"),aes(x=as.factor(Location),y=log(CH4_umol.L),color=Site)) + geom_point() + facet_grid(~Site)

ggplot(CH4_df2#%>%filter(Date<"2022-10-01")
         ,aes(x=as.factor(Location),y=log(CH4_umol.L),color=Site)) + geom_point() + facet_grid(~Site)


CH4_summary <- CH4_df%>%group_by(Site,Date)%>%
summarize(
  mean = mean(CH4_umol.L),
  sd = sd(CH4_umol.L),
  n = n())

CH4_summary_W07 <- CH4_df3%>%filter(Site=="Wetland_07")%>%group_by(Site,Date,Location)%>%
summarize(
  mean = mean(CH4_umol.L),
  sd = sd(CH4_umol.L),
  n = n())

```

#variance between sites
now we test for variance between sites

```{r site variance, echo=FALSE}

df <- read.csv(here::here("Wetlands/Wetland_df_MERGE_2024-04-14.csv"))
df$New.Name <- df$Site

#,ake column with new name to reflect elevation. S stands for "site"
df <- df%>%
  mutate(New.Name = case_match(New.Name, 
                      'Wetland01' ~ 'S1', 
                      'Wetland02' ~ 'S2',
                      'Wetland03' ~ 'S3',
                      'Wetland04' ~ 'S4',
                      'Wetland05' ~ 'S8',
                      'Wetland06' ~ 'S5',
                      'Wetland07' ~ 'S7',
                      'Wetland08' ~ 'S12',
                      'Wetland09' ~ 'S10',
                      'Wetland10' ~ 'S11',
                      'Wetland11' ~ 'S6',
                      'Wetland12' ~ 'S9'
                ))

options(scipen = 100)
#methane
CH4_model <- aov(log1p(CH4_umol.L) ~ New.Name , data = df)
summary(CH4_model)

# Check normality of residuals
res <- residuals(CH4_model)
qqnorm(res) 
qqline(res)
shapiro.test(res) #normality
bartlett.test(log(CH4_umol.L)  ~ Site, data = df) 

#non-parametric
kruskal.test(log1p(CH4_umol.L) ~ Site , data = df)
#this on is good
conver_results_CH4<- kwAllPairsConoverTest(log1p(CH4_umol.L) ~ as.factor(New.Name), data = df, p.adjust="bonferroni")
conver_results_CH4 <- conver_results_CH4$p.value
conver_results_CH4[conver_results_CH4>.05]<-NA


##co2

CO2_model <- aov(log1p(CO2_umol.L) ~ New.Name , data = df)
summary(CO2_model)
# Check assumptions
res <- residuals(CO2_model)
qqnorm(res) 
qqline(res)
shapiro.test(res) #normality
bartlett.test(log1p(CO2_umol.L)  ~ Site, data = df) 

conver_results_CO2<- kwAllPairsConoverTest(log(CO2_umol.L) ~ as.factor(Site), data = df, p.adjust="bonferroni")
conver_results_CO2 <- conver_results_CO2$p.value

#co2 passes assumptions, but CH4 does not
tuk <- TukeyHSD(CO2_model)
tuk_df <- data.frame(tuk$New.Name)
tuk_df <- tuk_df%>%filter(p.adj<.05)

co2_sum <- df%>%group_by(New.Name)%>%summarise(
  mean_cO2 =mean(CO2_umol.L),
  mean_size = mean(surface_area_m2)
)

ggplot(df,aes(x=reorder(New.Name,surface_area_m2,median),y=log(CH4_umol.L),color=Site)) + geom_point(size=3) 

ggplot(df,aes(x=as.factor(Site),y=log(CH4_umol.L),color=Site)) + geom_point(size=3) 
ggplot(df,aes(x=as.factor(Site),y=log(CO2_umol.L),color=Site)) + geom_point(size=3) 

elev_df <- df%>%select(Site,Elevation_m)


#now you can do the figure
p.ch4 <- ggplot(df,aes(x=reorder(New.Name,surface_area_m2,median),y=CH4_umol.L)) +
   geom_point(size=2) +
  stat_summary(geom = "point", fun = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  scale_y_log10() +
   ylab(expression(CH[4] ~'('~mu*'mol' ~ l^-1~')')) + xlab("") +
  theme_bw(base_size = 16) +
  theme(axis.text.x=element_blank()) +
  annotate("text", x = "S10", y = 20, label = "A") +
  annotate("text", x = "S6", y = 20, label = "BCEFG") +
  annotate("text", x = "S11", y = 20, label = "A") +
  annotate("text", x = "S12", y = 20, label = "AC") +
  annotate("text", x = "S5", y = 20, label = "BCEFG") +
  annotate("text", x = "S4", y = 20, label = "AF") +
  annotate("text", x = "S7", y = 20, label = "DG") +
  annotate("text", x = "S8", y = 20, label = "AB") +
  annotate("text", x = "S3", y = 20, label = "DE") +
  annotate("text", x = "S2", y = 20, label = "D") +
  annotate("text", x = "S9", y = 20, label = "BCDFG") +
  annotate("text", x = "S1", y = 20, label = "D") 



p.co2 <- ggplot(df,aes(x=reorder(New.Name,surface_area_m2,median),y=CO2_umol.L)) +
   geom_point(size=2) +
  stat_summary(geom = "point", fun = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  scale_y_log10() +
  ylab(expression(CO[2] ~'('~mu*'mol' ~ l^-1~')')) + xlab("Site") +
theme_bw(base_size = 16) +
  annotate("text", x = "S1", y = 900, label = "BE") +
  annotate("text", x = "S10", y = 900, label = "ACD") +
  annotate("text", x = "S11", y = 900, label = "C") +
  annotate("text", x = "S12", y = 900, label = "D") +
  annotate("text", x = "S2", y = 900, label = "E") +
  annotate("text", x = "S3", y = 900, label = "BE") +
  annotate("text", x = "S4", y = 900, label = "B") +
  annotate("text", x = "S5", y = 900, label = "BE") +
  annotate("text", x = "S6", y = 900, label = "BE") +
  annotate("text", x = "S7", y = 900, label = "BE") +
  annotate("text", x = "S8", y = 900, label = "BE") +
  annotate("text", x = "S9", y = 900, label = "AC") 

p.all <- ggarrange(p.ch4, p.co2, labels = c("A", "B"),ncol = 1, nrow = 2)

```

# model results

I'm not sure how to report these. But I think a table of selected models could work


```{r model tables, echo=FALSE}

df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))

#without wetland 12 
df_1 <- df%>%filter(Site!="Wetland12")

#(Intercept), scale(waterTemp_c_yearly), scale(log(SA_to_Vol_ratio)), scale(percent_DTW), scale(Elevation_m)

M_AICc_CH4 <- lmer(log(CH4_umol.L) ~ 
                  scale(waterTemp_c_yearly)+ 
                  scale(log(SA_to_Vol_ratio)) +
                scale(percent_DTW) +
                scale(Elevation_m) +
                  (1 |Site), data =df_1,REML = FALSE)
sum_AICc_CH4 <- summary(M_AICc_CH4)
sum_AICc_CH4_coefficients <- sum_AICc_CH4$coefficients
modelPerformance(M_AICc_CH4)

#without wetland 12
#(Intercept), (Intercept), scale(log(SA_to_Vol_ratio)), scale(Elevation_m)
M_BIC_CH4 <- lmer(log(CH4_umol.L) ~ 
                scale(log(SA_to_Vol_ratio)) + 
                scale(Elevation_m)+
                  (1 |Site), data =df_1,REML = FALSE)
sum_BIC_CH4 <- summary(M_BIC_CH4)
sum_BIC_CH4_coefficients <- sum_BIC_CH4$coefficients
modelPerformance(M_BIC_CH4)

#CO2 AICc 
#AICc: (Intercept), scale(Watertemp_c), scale(waterTemp_c_yearly), scale(percent_DTW), scale(Elevation_m)
M_AICc_CO2 <- lmer(log(CO2_umol.L) ~ 
                  scale(Watertemp_c)+ 
                  scale(waterTemp_c_yearly) +
                  scale(percent_DTW) +
                  scale(Elevation_m) +
                  (1 |Site), data =df_1,REML = FALSE)
sum_AICc_CO2 <- summary(M_AICc_CO2)
sum_AICc_CO2_coefficients <- sum_AICc_CO2$coefficients
modelPerformance(M_AICc_CO2)

#CO2 BIC
M_BIC_CO2 <- lmer(log(CO2_umol.L) ~ 
                scale(percent_DTW) +
                scale(Elevation_m) +
                  (1 |Site), data =df_1,REML = FALSE)
sum_BIC_CO2 <- summary(M_BIC_CO2)
sum_BIC_CO2_coefficients <- sum_BIC_CO2$coefficients
modelPerformance(M_BIC_CO2)

write.csv(sum_AICc_CH4_coefficients,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/AICc_CH4_coefficients.csv")
write.csv(sum_BIC_CH4_coefficients,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/BIC_CH4_coefficients.csv")
write.csv(sum_AICc_CO2_coefficients,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/AICc_CO2_coefficients.csv")
write.csv(sum_BIC_CO2_coefficients,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/BIC_CO2_coefficients.csv")

sum_AICc_CH4_coefficients <- read.csv("~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/AICc_CH4_coefficients.csv")%>%rename(
  variable=X,std_err=Std..Error,pvalue=Pr...t..)
sum_BIC_CH4_coefficients <- read.csv("~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/BIC_CH4_coefficients.csv")%>%rename(
  variable=X,std_err=Std..Error,pvalue=Pr...t..)
sum_AICc_CO2_coefficients <- read.csv("~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/AICc_CO2_coefficients.csv")%>%rename(
  variable=X,std_err=Std..Error,pvalue=Pr...t..)
sum_BIC_CO2_coefficients <- read.csv("~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/BIC_CO2_coefficients.csv")%>%rename(
  variable=X,std_err=Std..Error,pvalue=Pr...t..)
sum_AICc_CH4_coefficients$Model <- "AICc"
sum_AICc_CH4_coefficients$gas <- "CH4"
sum_BIC_CH4_coefficients$Model <- "BIC"
sum_BIC_CH4_coefficients$gas <- "CH4"
sum_AICc_CO2_coefficients$Model <- "AICc"
sum_AICc_CO2_coefficients$gas <- "CO2"
sum_BIC_CO2_coefficients$Model<- "BIC"
sum_BIC_CO2_coefficients$gas <- "CO2"

model_df <- rbind(sum_AICc_CH4_coefficients,sum_BIC_CH4_coefficients,sum_AICc_CO2_coefficients,sum_BIC_CO2_coefficients)

model_df <- model_df%>% filter(variable!="(Intercept)")%>% 
  mutate(Low=Estimate-std_err,High=Estimate+std_err)%>%
  mutate(across(c(gas, Model), factor))


ann_text <- data.frame(Model=as.factor(c(replicate(5,"AICc"),replicate(5,"BIC"),replicate(5,"AICc"),replicate(5,"BIC"))),
gas=as.factor(c(replicate(10,"CH4"),replicate(10,"CO2"))),
#gas <- as.factor(gas)
Estimate = c(NA,0.4605, 0.6486,-0.3270,-1.7371,#ch4 AIC
               NA,NA,NA,-0.4165,-1.6359,#ch4 BIC
               0.12238,-0.21030,0.28209,NA,-1.12876, #CO2 AIC
               NA,NA,0.34398,NA,-1.11051),#CO2 BIC
variable = as.factor(replicate(4, c("scale(Watertemp_c)","scale(waterTemp_c_yearly)","scale(percent_DTW)","scale(log(SA_to_Vol_ratio))","scale(Elevation_m)"))),
sig = c(NA,".","*","*","***", #ch4 AIC
               NA,NA,NA,"*","***", #ch4 BIC
               ".","*","*",NA,"***", #CO2 AIC
               NA,NA,"**",NA,"***") #CO2 BIC
)


p.model <- ggplot(data=model_df, aes(x=variable, y=Estimate)) +
  facet_grid(as.factor(gas)~as.factor(Model)) +
    geom_text(aes(variable,Estimate, label=sig), data = ann_text,vjust=-.75 ) + 
  geom_point() + geom_errorbar(aes(ymin=Low,ymax=High),width=0)+
    geom_hline(yintercept = 0, linetype="dashed",color="red",linewidth=1) +
  coord_flip() + theme_bw(base_size = 16) +
  theme(axis.title.y=element_blank()) +
    scale_x_discrete(labels = c("scale(Elevation)","scale(surface area : volume)","scale(% DTW < 1)","scale(yearly water temp.)", "scale(water temp.)")) 

```

#plot k and co2 as drivers of flux


```{r co2 v flux and co2 v k600, echo=FALSE}

k_df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))

k_df$New.Name <- k_df$Site

#,ake column with new name to reflect elevation. S stands for "site"
k_df <- k_df%>%
  mutate(New.Name = case_match(New.Name, 
                      'Wetland01' ~ 'S1', 
                      'Wetland02' ~ 'S2',
                      'Wetland03' ~ 'S3',
                      'Wetland04' ~ 'S4',
                      'Wetland05' ~ 'S8',
                      'Wetland06' ~ 'S5',
                      'Wetland07' ~ 'S7',
                      'Wetland08' ~ 'S12',
                      'Wetland09' ~ 'S10',
                      'Wetland10' ~ 'S11',
                      'Wetland11' ~ 'S6',
                      'Wetland12' ~ 'S9'
                ))

k_df$DateTime <- as.POSIXct(k_df$DateTime)
k_df <- k_df%>%filter(DateTime < "2022-10-01 00:00:00")


M1 <- lmer(log(Flux_umol_m2_s) ~ 
             scale(k_m_d)+ 
             scale(log(CO2_umol.L))+
   #         scale(Watertemp_c) +
             (1 |Site), data =k_df)
summary(M1)
modelPerformance(M1)

M1 <- lm(log(Flux_umol_m2_s) ~ 
         #    scale(k_m_d)+ 
             scale(log(CO2_umol.L)),
   #         scale(Watertemp_c) +
             data =k_df)

k_df$New.Name <- factor(k_df$New.Name, levels = c("S1", "S2", "S3","S4","S5","S6","S7","S8","S9","S10","S11","S12"))

p1 <- ggplot(k_df,aes(x=CO2_umol.L,y=Flux_umol_m2_s,color=New.Name)) + geom_point(aes(),size=3) +  
   geom_smooth(method='lm', color='black') + guides(color=guide_legend(title="Site"))+
  theme_bw(base_size = 16) +
  scale_x_log10() + scale_y_log10()

p2 <- ggplot(k_df,aes(x=CO2_umol.L,y=K600,color=New.Name)) + geom_point(aes(),size=3) +  guides(color=guide_legend(title="Site")) +
  theme_bw(base_size = 16) +
  scale_x_log10()


fig <- ggarrange(p1, p2, common.legend = TRUE, legend="bottom")


```
#modeling k or k600

sirface are and solar radiation where both chosen for being significant in lmer model. Solar radiation is the more significant variable, and if removed, surface area is no longer selected

```{r co2 v flux and co2 v k600, echo=FALSE}

k_df_1 <- k_df%>%filter(Site!="Wetland12")

k_df$water_minus_air <- k_df$Watertemp_c - k_df$AirTemp_c
M1 <- lmer(K600 ~ 
#             scale(water_minus_air) +
                  scale(log(surface_area_m2)) +
   # scale(windspeed_m_s) +
              #    scale(solarrad_W_m2) +
             (1|Site), data =k_df ,REML=FALSE)

summary(M1)
modelPerformance(M1)


k_df$BelowSat <- NA
k_df$BelowSat <- ifelse(k_df$CO2_mol.L < k_df$CO2_sat_mol.L, "*", NA)


p2 <- ggplot(k_df) + geom_point( aes(x=surface_area_m2,y=K600,fill=log(CO2_umol.L)), shape=21,size=3)  + geom_text(aes(x=surface_area_m2,y=K600,label=BelowSat),vjust=-0.1,hjust=-.5,color="red",size=7) +
  geom_hline(aes(yintercept = median(K600)), color="blue", linetype="dashed") +
  theme_bw(base_size = 16) +
  scale_fill_gradientn(colours = terrain.colors(10)) +
  scale_x_log10()

```

```{r meank calc, echo=FALSE}
#first identify and remove outliers
k_df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))
k_df$DateTime <- as.POSIXct(k_df$DateTime)
k_df <- k_df%>%filter(DateTime < "2022-10-01 00:00:00")

ggplot(k_df, aes(x=Site, y=K600)) + 
  geom_boxplot(outlier.colour="red", outlier.shape=8,
                outlier.size=4) +
  geom_hline(aes(yintercept = median(K600)), color="blue")


ggplot(k_df) + geom_point(aes(x=water_minus_air,y=k_m_d,color=DateTime)) #+ scale_x_log10()
#Grubbs test for two opposite outliers

```
