---
title: "Pond Paper Figures"
author: "Kriddie"
date: "2024-04-15"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(lubridate)
library(dplyr)
library(ggplot2)
library(reshape2)
library("ggpubr")
library(rstatix)
library(devtools)
library(PMCMRplus)
library(lme4)
library(lmerTest)
library(jtools)
library(extraoperators)
library(JWileymisc)
library(multilevelTools)
library(broom)
#library(tidyverse)
library(tidyr)
library(stringr)
library(scales)

```

#site descriptors this includes: \> ave SA \> ave depth \> ave vol \>
cathment size \> elevation \> percent change in SA \> percent change in
vol \> percent veg \> DOC/TDN

```{r table 1}
WL_df <- read.csv(here::here("Wetlands/WaterLevel_FINAL/WL_Wetland_all_FINAL.csv"))%>%select(DateTime,Station,WLTemp_c,depth_ave_m,surface_area_m2,Volumn_m3)%>%
  rename(Site=Station)%>%rename(WaterTemp_c=WLTemp_c)
WL_df$Site <- gsub(".*_","",WL_df$Site)
WL_df$WaterTemp_c <- ifelse(WL_df$WaterTemp_c < 0, 0, WL_df$WaterTemp_c)


WL_df_sum <- WL_df%>%group_by(Site)%>%
  dplyr::summarise(
    SA_mean = mean(surface_area_m2,na.rm=TRUE),
    SA_max = max(surface_area_m2,na.rm=TRUE),
    SA_min = min(surface_area_m2,na.rm=TRUE),
    depth_mean = mean(depth_ave_m,na.rm=TRUE),
    vol_mean = mean(Volumn_m3,na.rm=TRUE),
    vol_max = max(Volumn_m3,na.rm=TRUE),
    vol_min = min(Volumn_m3,na.rm=TRUE),
  )
WL_df_sum$SA_diff <- (WL_df_sum$SA_max - WL_df_sum$SA_min)/(WL_df_sum$SA_max) * 100
WL_df_sum$vol_diff <- (WL_df_sum$vol_max - WL_df_sum$vol_min)/(WL_df_sum$vol_max) * 100


sum_table <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))%>%select(Site,Elevation_m,WS_area_minus_pond,DOC_mg.L,TDN_mg.L)
sum_table <- sum_table%>%group_by(Site)%>%
  dplyr::summarise(
    Elevation_m = mean(Elevation_m,na.rm=TRUE),
    Catchment_size = max(WS_area_minus_pond,na.rm=TRUE),
    DOC_mg.L = min(DOC_mg.L,na.rm=TRUE),
    TDN_mg.L = mean(TDN_mg.L,na.rm=TRUE)
  )


table1 <- full_join(sum_table,WL_df_sum,by="Site")

#write.csv(table1,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/Tables/table1.csv")
```

#med-deli plot this graph shows the hydrology of the system

```{r med deli plot,echo=FALSE}

#I want to make a 12 panel figure with 2 axis depth and surface area

WL_df <- read.csv(here::here("Wetlands/WaterLevel_FINAL/WL_Wetland_all_FINAL.csv"))
#we don't have depth for wetland 12 but we can use water level to plot
WL_df[WL_df$Station=="WL_Wetland12",]$depth_ave_m <- WL_df[WL_df$Station=="WL_Wetland12",]$WaterLevel_m
WL_df <- WL_df[c("DateTime","Station","Baro_kpa","BaroTemp_c","WLTemp_c","depth_ave_m","surface_area_m2","Volumn_m3","SA_to_Vol_ratio")]
WL_df$DateTime <- as.POSIXct(WL_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
#WL_df$Station_2 <- paste("Wetland",as.numeric(gsub("\\D", "", WL_df$Station)))
WL_df$Station <- str_sub(WL_df$Station,4)
#WL_df$Station <- stringr::str_replace_all(WL_df$Station, " ", "")

#read in elevation data to merge with WL
df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))%>%select(Site,Elevation_m)
df <- unique(df)

#med deli plot

Summary_df <- WL_df%>%
 group_by(Station)%>%
  summarise(
    SA_max = max(surface_area_m2, na.rm = TRUE),
    SA_min = min(surface_area_m2, na.rm = TRUE),
    SA_mean = mean(surface_area_m2, na.rm = TRUE),
    
    depth_max = max(depth_ave_m, na.rm = TRUE),
    depth_min = min(depth_ave_m, na.rm = TRUE),
    depth_mean = mean(depth_ave_m, na.rm = TRUE)
  )%>%rename(Site=Station)

Summary_df <- full_join(Summary_df,df,by="Site")

p2 <- ggplot(data=Summary_df,aes(x=SA_mean,y=depth_mean, fill=Elevation_m)) +
  geom_point(shape=22,size=5) +
  geom_segment(aes(x = SA_min, y = depth_mean, xend = SA_max, yend = depth_mean), color="grey25",linewidth=.5) +
  geom_segment(aes(x = SA_mean, y = depth_min, xend = SA_mean, yend = depth_max), color="grey25",linewidth=.5) +
  scale_y_log10() + scale_x_log10() +
  theme_classic() +
  theme(text=element_text(size=20)) + guides(fill=guide_legend(title="Elevation (m)")) +
  theme(
    axis.text.x = element_text(color="black"),
    axis.ticks = element_line(color = "black")) +
  xlab(expression('Surface Area ('~m^2~')')) + ylab("Depth (m)") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.text.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))
)

p3 <- p2 + annotation_logticks(
  base = 10,
  sides = "bl",
  outside = TRUE,
  scaled = TRUE,
  short = unit(0.1, "cm"),
  mid = unit(0.2, "cm"),
  long = unit(0.3, "cm"),
  colour = "black",
  linewidth = 0.5,
  linetype = 1,
  alpha = 1,
  color = "grey40"
) + coord_cartesian(clip = "off")

```

# i want to make a plot the shows water temp over time for all sites

probably delete this because it doesn't look the way I want

```{r water temp plot}
df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))
df$New.Name <- df$Site
GHGsummary_df<-df %>%group_by(New.Name,Site,Elevation_m,percent_DTW,WS_area_minus_pond,waterTemp_c_yearly)%>%
  summarise(mean_ch4 = mean(pCH4_ppm),
            mean_co2 = mean(pCO2_ppm),
            mean_watertemp = mean(Watertemp_c),
            mean_airtemp = mean(AirTemp_c),
            mean_SA = mean(surface_area_m2),
            mean_vol = mean(Volumn_m3),
            mean_vol_to_SA = mean(SA_to_Vol_ratio),
            mean_depth = mean(depth_ave_m))


df_watertemp <- left_join(WL_df%>%rename(Site=Station),GHGsummary_df%>%select(Site,Elevation_m,mean_ch4,mean_co2),by="Site")

ggplot() + geom_line(data=df_watertemp,aes(x=WLTemp_c,y=mean_ch4,color=Site)) + geom_point(data=df,aes(x=Watertemp_c,y=mean(pCH4_ppm),shape=Site),color="blue")
  scale_y_continuous(trans="log")
  
  ggplot() + geom_point(data=WL_df,aes(x=WLTemp_c,y=surface_area_m2,color=Station)) +
  scale_y_continuous(trans="log")
  
    ggplot() + geom_point(data=WL_df%>%filter(Station=="Wetland03"),aes(x=DateTime,y=WLTemp_c,color=Station)) +
  scale_y_continuous(trans="log")
    
library(plotly)
plot_ly(data=WL_df%>%filter(Station=="Wetland02"),x=~DateTime,y=~WLTemp_c)
    
```

## Variance within wetlands

First - how do I report the variance found in ponds? we have reps and we
have 3 sample location (and then 2 sample locations)

do i use standard error? how do I report standard error?

below I have some code as a starting point

```{r analysis 1}
#this script takes the methane data and summarizes it 
#now this is included in Merge_WetlandDATA.R

#I need to convert ch4 to pch4

CH4_summer_df <- read.csv(here::here("Methane/Methane_df_2023-07-20.csv"))%>% select("Site","Location","Date_collected","CH4_umol_L.1","CH4_.sat","Watertemp_c")%>%
  filter(Site!="Colmillo")%>%filter(Site!="Gavi-main")%>%filter(Site!="Gavi-trib") %>% 
  rename(Date = Date_collected, CH4_umol.L = CH4_umol_L.1, CH4_sat = CH4_.sat)
CH4_summer_df$Date <- as.Date.character(CH4_summer_df$Date,format="%m/%d/%y")
#convert to pCH4
#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
CH4_summer_df$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(CH4_summer_df$Watertemp_c+273.15)-1/T_STP_K))
CH4_summer_df$pCH4_ppm <- CH4_summer_df$CH4_umol.L /CH4_summer_df$KH_CH4_mol.L.atm


#fall samples
CH4_fall_df <- read.csv(here::here("Methane/Methane_fall2022_update.csv"))%>%
  select("Site","Location","Date_collected","CH4_umol.L","CH4_sat","Watertemp_Field_c")%>%
  rename(Date = Date_collected)%>%rename(Watertemp_c=Watertemp_Field_c)%>%
  filter(Site!="Chakanas")%>%filter(Site!="Gavilan")
CH4_fall_df$Date <- as.Date.character(CH4_fall_df$Date,format="%m/%d/%y")
#convert to pCH4
#add henry's constant CH4
kH_STP_mol.L.atm = .0014182
dlnHcppersperK = 1600
CH4_fall_df$KH_CH4_mol.L.atm <- kH_STP_mol.L.atm*exp(dlnHcppersperK*(1/(CH4_fall_df$Watertemp_c+273.15)-1/T_STP_K))
CH4_fall_df$pCH4_ppm <- CH4_fall_df$CH4_umol.L /CH4_fall_df$KH_CH4_mol.L.atm

#for the fall we did not have the same sampling strategy of site #2 being in the middle (I think), but we did do reps. so lets see what the variance is in reps to see if its the same

CH4_df <- rbind(CH4_summer_df,CH4_fall_df)



CH4_reps <- CH4_df%>%group_by(Site,Location,Date)%>%
dplyr::summarize(
  min = min(pCH4_ppm), max = max(pCH4_ppm),
  mean = mean(pCH4_ppm),
  sd = sd(pCH4_ppm),
  n = n())%>%
  filter(n>1)
CH4_reps$se <-  CH4_reps$sd / sqrt(2)
CH4_reps$type <- "reps"

CH4_se <- CH4_df%>%group_by(Site,Date)%>%
dplyr::summarize(
  min = min(pCH4_ppm), max = max(pCH4_ppm),
  mean = mean(pCH4_ppm),
  sd = sd(pCH4_ppm),
  n = n())
CH4_se$se <-  CH4_se$sd / sqrt(2)
CH4_se$type <- "allsamples"


CH4_summary <- rbind(CH4_reps,CH4_se)

CH4_summary$dif_prec <- (CH4_summary$max-CH4_summary$min)/CH4_summary$mean * 100

## we also have the data to do this for CO2 - I made a mistake and didn't include the corrected co2 values, so I'll need to calculate here
df_CO2 <- read.csv(here::here("Wetlands/CO2_intrapondvariance.csv"))
df_CO2$Date <- as.Date(df_CO2$Date,format="%m/%d/%y")
df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))
df$Date <- as.Date(df$Date,format="%Y-%m-%d")
df_merge <- df%>%select(Site,Date,Watertemp_c,AirPress_kpa)%>%rename(Wetland=Site)
df_CO2 <- left_join(df_CO2,df_merge,by=c("Wetland","Date"))

df_CO2$ppm_Corrected <- df_CO2$ppm_NOTcorrected * (1 + (1013 - (df_CO2$AirPress_kpa+2*0.0980665)*10) * 0.0015) * (1 - (25 - df_CO2$Watertemp_c) * 0.003)

df_CO2 <- df_CO2%>%rename(Site="Wetland")%>%
  mutate(Location = case_when(Location == 1 ~ "edge",
                              Location == 2 ~ "middle",
                              Location == 3 ~ "edge",
                                   TRUE ~ NA_character_))
df_CO2$Site <- as.factor(df_CO2$Site)
df_CO2$Date <- as.Date.character(df_CO2$Date,format="%m/%d/%y")

C02_middle <- df_CO2%>%filter(Location=="middle")%>%select(Site,Location,Date,ppm_Corrected)

C02_edge <- df_CO2 %>%group_by(Site,Date,Location)%>%filter(Location!="middle")%>%
dplyr::summarise(
  ppm_Corrected = mean(ppm_Corrected,rm.na=TRUE))

CO2_summary <- rbind(C02_middle,C02_edge)


ggplot(CO2_summary, aes(x=as.factor(Site), y=log(ppm_Corrected),color=Location)) + 
  geom_point()


##make table 2
CH4_table <- CH4_df%>%group_by(Site,Date)%>%
dplyr::summarize(
  mean = mean(pCH4_ppm),
  sd = sd(pCH4_ppm),
  n = n())

#write.csv(CH4_table,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/ch4_summarytable.csv")
#write.csv(CH4_table,here::here("Kriddie/ch4_summarytable_ppm.csv"))


CO2_table <- CO2_summary %>%group_by(Site,Date)%>%
dplyr::summarise(
  mean = mean(ppm_Corrected, rm.na=TRUE),
  sd = sd(ppm_Corrected, rm.na=TRUE),
  n = n())

#write.csv(CO2_table,"~/OneDrive - University of North Carolina at Chapel Hill/Dissertation papers/Wetland GHG/co2_summarytable.csv")
#write.csv(CO2_table,here::here("Kriddie/CO2_summarytable_ppm.csv"))
```

## Variance between sample locations within a pond

1.  are locations at the edge of pond significantly different from
    locations in the middle?

> findings: 1. 9 waterbodies fit parametric model assumptions, so we ran
> 1-way anova 2. Site 2, 7, 11 do not, so we ran kusker-Wallis 3. effect
> of location was insignificnat EXCEPT for W07

We will report mean and standard deviation for each wetland by day for
wetland 7, we report both center and edge

```{r location variance, echo=FALSE}

CH4_df2 <- CH4_df
CH4_df2$Location[CH4_df2$Location == 3] <- 1
CH4_df3 <- CH4_df2%>%filter(Location == 1 | Location == 2)
CH4_df2 <- CH4_df3%>%filter(Date< "2022-10-01")

# Check normality of residuals
#Shapiro-Wilk Test: if value is greater than 0.05, the data is normal. If it is below 0.05, the data significantly deviate from a normal distribution
#Bartlett's test tests the hypothesis that our samples have equal variances. If the Chi- Square test is significant (p < . 05), then we can reject the null hypothesis and assume that variances are unequal.
result <- aov(log(pCH4_ppm) ~ Location , data = CH4_df2%>%filter(Site=="Wetland_12"))
res <- residuals(result)
qqnorm(res) 
qqline(res)
shapiro.test(res) #normality
bartlett.test(log1p(pCH4_ppm)  ~ Location, data = CH4_df2%>%filter(Site=="Wetland_01"))  

#normal: wetland 3,4,5,6,7, 8,9,10, 12
#not normal: wetland 1,2  & 11 

#now run stats
result <- aov(log(pCH4_ppm) ~ Location , data = CH4_df2%>%filter(Site=="Wetland_12"))
summary(result)
#results: significant difference in 7

#run kuskerwallis on other wetland 1 & 2 & 11 
kruskal.test(log(pCH4_ppm) ~ Location , data = CH4_df2%>%filter(Site=="Wetland_11"))
#results: none are significant

#wetland 07 failed the test
W_07 <- CH4_df2%>%filter(Date<"2022-10-01")%>%filter(Site=="Wetland_07")%>%group_by(Location)%>%summarise(
  mean=mean(pCH4_ppm),
  median = median(pCH4_ppm)
)

ggplot(CH4_df%>%filter(Date<"2022-10-01")%>%filter(Site=="Wetland_07"),aes(x=as.factor(Location),y=log(pCH4_ppm),color=Site)) + geom_point() + facet_grid(~Site)

ggplot(CH4_df2%>%filter(Date>"2022-10-01"),aes(x=as.factor(Location),y=log(pCH4_ppm),color=Site)) + geom_point() + facet_grid(~Site)

ggplot(CH4_df2#%>%filter(Date<"2022-10-01")
         ,aes(x=as.factor(Location),y=log(pCH4_ppm),color=Site)) + geom_point() + facet_grid(~Site)


CH4_summary <- CH4_df%>%group_by(Site,Date)%>%
summarize(
  mean = mean(pCH4_ppm),
  sd = sd(pCH4_ppm),
  n = n())

CH4_summary_W07 <- CH4_df3%>%filter(Site=="Wetland_07")%>%group_by(Site,Date,Location)%>%
summarize(
  mean = mean(pCH4_ppm),
  sd = sd(pCH4_ppm),
  n = n())

```

#within pond variance for CO2

normal & non significan 12

```{r location variance CO2, echo=FALSE}

CO2_df2 <- CO2_summary

# Check normality of residuals
result <- aov(log(ppm_Corrected) ~ Location , data = CO2_df2 %>%filter(Site=="1"))
res <- residuals(result)
qqnorm(res) 
qqline(res)
shapiro.test(res) #normality
bartlett.test(log(ppm_Corrected)  ~ Location, data = CO2_df2%>%filter(Site=="1"))  #monovariance

summary(result)
#results:
#normal and not significant: 12,10,8,7,5,4,3,2,1
#not normal: none
#not enough data 11, 9, 6
#all other wetland meet assumptions and also location is not significant


CO2_summary <- CO2_df2%>%group_by(Site,Date)%>%
summarise(
  mean = mean(ppm_Corrected,na.rm=TRUE)
 # sd = sd(CH4_umol.L),
  #n = n()
 )


```

# variance between sites 

now we test for variance between sites

```{r site variance, echo=FALSE}
 
df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))
df$New.Name <- df$Site
GHGsummary_df<-df %>%group_by(New.Name,Site,Elevation_m,percent_DTW,WS_area_minus_pond,waterTemp_c_yearly)%>%
  summarise(mean_ch4 = mean(pCH4_ppm),
            mean_co2 = mean(pCO2_ppm),
            mean_watertemp = mean(Watertemp_c),
            mean_airtemp = mean(AirTemp_c),
            mean_SA = mean(surface_area_m2),
            mean_vol = mean(Volumn_m3),
            mean_vol_to_SA = mean(SA_to_Vol_ratio),
            mean_depth = mean(depth_ave_m))


#make column with new name to reflect elevation. S stands for "site"
df <- df%>%
  mutate(New.Name = case_match(New.Name, 
                      'Wetland01' ~ 'S1', 
                      'Wetland02' ~ 'S2',
                      'Wetland03' ~ 'S3',
                      'Wetland04' ~ 'S4',
                      'Wetland05' ~ 'S8',
                      'Wetland06' ~ 'S5',
                      'Wetland07' ~ 'S7',
                      'Wetland08' ~ 'S12',
                      'Wetland09' ~ 'S10',
                      'Wetland10' ~ 'S11',
                      'Wetland11' ~ 'S6',
                      'Wetland12' ~ 'Wetland'
                ))

options(scipen = 100)
#methane
CH4_model <- aov(log1p(pCH4_ppm) ~ New.Name , data = df)
summary(CH4_model)

# Check normality of residuals
res <- residuals(CH4_model)
qqnorm(res) 
qqline(res)
shapiro.test(res) #normality
bartlett.test(log(pCH4_ppm)  ~ Site, data = df) 

#non-parametric
kruskal.test(log1p(pCH4_ppm) ~ Site , data = df)
#this on is good
conver_results_CH4<- kwAllPairsConoverTest(log1p(pCH4_ppm) ~ as.factor(New.Name), data = df, p.adjust="bonferroni")
conver_results_CH4 <- conver_results_CH4$p.value
#conver_results_CH4[conver_results_CH4>.05]<-NA


##co2

CO2_model <- aov(log(pCO2_ppm) ~ New.Name , data = df)
summary(CO2_model)
# Check assumptions
res <- residuals(CO2_model)
qqnorm(res) 
qqline(res)
shapiro.test(res) #normality
bartlett.test(log(pCO2_ppm)  ~ Site, data = df) 

df <- df[order(df$New.Name),]
conver_results_CO2<- kwAllPairsConoverTest(log(pCO2_ppm) ~ as.factor(New.Name), data = df, p.adjust="bonferroni")
conver_results_CO2 <- conver_results_CO2$p.value

#co2 passes assumptions, but CH4 does not
tuk <- TukeyHSD(CO2_model)
tuk_df <- data.frame(tuk$New.Name)
tuk_df <- tuk_df%>%filter(p.adj<.05)

co2_sum <- df%>%group_by(New.Name)%>%summarise(
  mean_pCO2 =mean(pCO2_ppm),
  mean_size = mean(surface_area_m2)
)

ggplot(df,aes(x=reorder(New.Name,surface_area_m2,median),y=log(pCH4_ppm),color=Site)) + geom_point(size=3) 

ggplot(df,aes(x=as.factor(Site),y=log(pCH4_ppm),color=Site)) + geom_point(size=3) 
ggplot(df,aes(x=as.factor(Site),y=log(pCO2_ppm),color=Site)) + geom_point(size=3) 

elev_df <- df%>%select(Site,Elevation_m)


#now you can do the figure
p.ch4 <- ggplot(df,aes(x=reorder(New.Name,Elevation_m,median,decreasing = TRUE),y=pCH4_ppm)) +
   geom_point(size=2) +
    geom_boxplot(fill="grey"#outlier.colour="red", outlier.shape=8,outlier.size=2
     ) +
  stat_summary(geom = "point", fun = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  scale_y_log10() +
   ylab(expression(italic(p)~CH[4] ~'(ppm)')) + xlab("") +
  theme_bw(base_size = 16) +
  theme(axis.text.x=element_blank()) +
  annotate("text", x = "S1", y = 15000, label = "A") +
  annotate("text", x = "S2", y = 15000, label = "A") +
  annotate("text", x = "S3", y = 15000, label = "AB") +
  annotate("text", x = "S4", y = 15000, label = "C") +
  annotate("text", x = "S5", y = 15000, label = "BCD") +
  annotate("text", x = "S6", y = 15000, label = "BCE") +
  annotate("text", x = "S7", y = 15000, label = "ADE") +
  annotate("text", x = "S8", y = 15000, label = "C") +
  annotate("text", x = "Wetland", y = 15000, label = "AF") +
  annotate("text", x = "S10", y = 15000, label = "C") +
  annotate("text", x = "S11", y = 15000, label = "C") +
  annotate("text", x = "S12", y = 15000, label = "CF")



p.co2 <- ggplot(df,aes(x=reorder(New.Name,Elevation_m,median,decreasing = TRUE),y=pCO2_ppm)) +
#  ggplot(df,aes(x=Elevation_m,,y=pCO2_ppm)) +
   geom_point(size=2) +
  geom_boxplot(fill="grey") +
  stat_summary(geom = "point", fun = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  scale_y_log10() +
  ylab(expression(italic(p)~CO[2] ~'(ppm)')) + xlab("Site") +
theme_bw(base_size = 16) +
  annotate("text", x = "S1", y = 15000, label = "AB") + 
  annotate("text", x = "S2", y = 15000, label = "B") +
  annotate("text", x = "S3", y = 15000, label = "AB") +
  annotate("text", x = "S4", y = 15000, label = "AC") +
  annotate("text", x = "S5", y = 15000, label = "AB") +
  annotate("text", x = "S6", y = 15000, label = "AB") +
  annotate("text", x = "S7", y = 15000, label = "AB") +
  annotate("text", x = "S8", y = 15000, label = "ABC") +
  annotate("text", x = "Wetland", y = 15000, label = "CD") +
  annotate("text", x = "S10", y = 15000, label = "D") +
  annotate("text", x = "S11", y = 15000, label = "D") +
  annotate("text", x = "S12", y = 15000, label = "E")


###now do it ordering by elevation, not surface area


p.all <- ggarrange(p.ch4, p.co2, labels = c("A", "B"),ncol = 1, nrow = 2)

```

# Water temp as a driver of GHG

```{r site variance, echo=FALSE}
#plot water temp as driver of CO2

df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))
df$New.Name <- df$Site
#make column with new name to reflect elevation. S stands for "site"
df <- df%>%mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8','Wetland06' ~ 'S5','Wetland07' ~ 'S7','Wetland08' ~ 'S12','Wetland09' ~ 'S10','Wetland10' ~ 'S11','Wetland11' ~ 'S6','Wetland12' ~ 'Wetland'))

ch4_sum<-df%>%group_by(New.Name,Elevation_m)%>%
  summarise(mean_co2 = mean(pCO2_ppm),mean_ch4 = mean(pCH4_ppm),mean_temp = mean(Watertemp_c),median_ch4 = median(pCH4_ppm))
#What is the relationship between water temp and pco2?

M_CO2_temp <- lmer(log(pCO2_ppm) ~ 
                    Watertemp_c+ 
                     (1 |Site), data =df,REML = FALSE)
summary(M_CO2_temp)
modelPerformance(M_CO2_temp)

M_CO2_temp <- lm(log(mean_co2) ~ 
                    log(mean_temp), data =ch4_sum)
summary(M_CO2_temp)

xlab <- "Water Temperature (°C)"
p.co2 <- ggplot(df,aes(x=Watertemp_c,y=pCO2_ppm,color=reorder(New.Name,Elevation_m,median,decreasing = TRUE)) ) + 
  geom_point(size=2)+
  geom_smooth(method='lm',formula = "y ~ x",se=FALSE) +
    ylab(expression(italic(p)~CO[2] ~'(ppm)')) + xlab(xlab) +
  scale_color_discrete(name="Site") +
  scale_y_continuous(transform="log",breaks=c(300,1000,3000,10000)) +
  scale_x_continuous(transform="log") +
  theme_bw(base_size = 18)

#What is the relationship between water temp and pch4?
M_CH4_temp <- lmer(log(pCH4_ppm) ~ 
                    log(Watertemp_c) + 
                     (1 |Site), data =df)
summary(M_CH4_temp)
modelPerformance(M_CH4_temp)


M_CH4_temp <- lm(log(mean_ch4) ~ 
                    log(mean_temp), data =ch4_sum)
summary(M_CH4_temp)

p.ch4 <- ggplot(df,aes(x=Watertemp_c,y=pCH4_ppm,color=reorder(New.Name,Elevation_m,median,decreasing = TRUE)) ) + 
  geom_point(size=2)+
  geom_smooth(method='lm',formula = "y ~ x",se=FALSE) +
    ylab(expression(italic(p)~CH[4] ~'(ppm)')) + xlab(xlab) +
  scale_color_discrete(name="Site") +
    scale_y_continuous(transform="log",breaks = c(1,3,10,30,100,300,1000,3000)) +scale_x_continuous(transform="log") +
  theme_bw(base_size = 18)

p.ch4 <- ggplot(ch4_sum,aes(x=mean_temp,y=mean_ch4,color=reorder(New.Name,Elevation_m,median,decreasing = TRUE)) ) + 
  geom_point(size=2)+
 # geom_smooth(method='lm',formula = "y ~ x",se=FALSE) +
    ylab(expression(italic(p)~CH[4] ~'(ppm)')) + xlab(xlab) +
  scale_color_discrete(name="Site") +
    scale_y_continuous(transform="log",breaks = c(1,3,10,30,100,300,1000,3000)) +scale_x_continuous(transform="log") +
  theme_bw(base_size = 18)




```

# What other things might drive GHG concntrations? Here are our options:

> -   Elevation
>
> -   %DTW
>
> -   Catchment size
>
> -   surface area
>
> -   volume
>
> -   volume to surface area ratio
>
> -   depth
>
> -   air temp
>
> -   water temp

```{r GHG drviers, echo=FALSE}
df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))
df$New.Name <- df$Site
GHGsummary_df<-df %>%group_by(New.Name,Site,Elevation_m,percent_DTW,WS_area_minus_pond,waterTemp_c_yearly)%>%
  summarise(mean_ch4 = mean(pCH4_ppm),
            mean_co2 = mean(pCO2_ppm),
            mean_watertemp = mean(Watertemp_c),
            mean_airtemp = mean(AirTemp_c),
            mean_SA = mean(surface_area_m2),
            mean_vol = mean(Volumn_m3),
            mean_vol_to_SA = mean(SA_to_Vol_ratio),
            mean_depth = mean(depth_ave_m))


m1 <- lmer(log(pCO2_ppm) ~ 
             scale(Watertemp_c) +
             scale(AirTemp_c) +
             scale(log(surface_area_m2)) +
             scale(log(Volumn_m3)) +
             scale(SA_to_Vol_ratio) +
             scale(depth_ave_m) +
            scale(Elevation_m)+
             scale(percent_DTW) +
            scale(WS_area_minus_pond)+
                     (1 |Site), data =df)

m2 <- lm(log(mean_co2) ~ 
          scale(mean_watertemp) +
       #   scale(mean_airtemp) +
      #     scale(log(mean_SA)) +
      #    scale(log(mean_vol)) +
      #    scale(mean_vol_to_SA) + 
      #    scale(mean_depth) +
      #     scale(Elevation_m)+
          scale(percent_DTW) #+
      #    scale(WS_area_minus_pond)
        ,
         data =GHGsummary_df)

summary(m1)
summary(m2)

m2 <- lm(log(mean_ch4) ~
         mean_watertemp +
           percent_DTW,
         data =GHGsummary_df)

m2 <- lm(percent_DTW ~ 
         mean_watertemp,
         data =GHGsummary_df)



ggplot(summary,aes(x=Elevation_m,y=mean_ch4,color=Site))+geom_point()
ggplot(summary,aes(x=Elevation_m,y=waterTemp_c_yearly,color=Site))+geom_point()

```

# plot k and co2 as drivers of flux

```{r co2 v flux and co2 v k600, echo=FALSE}

k_df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))

k_df$New.Name <- k_df$Site

k_df$pCO2_air_uatm <- k_df$pCO2_air_atm*10^6

#,ake column with new name to reflect elevation. S stands for "site"
k_df <- k_df%>%
  mutate(New.Name = case_match(New.Name, 
                      'Wetland01' ~ 'S1', 
                      'Wetland02' ~ 'S2',
                      'Wetland03' ~ 'S3',
                      'Wetland04' ~ 'S4',
                      'Wetland05' ~ 'S8',
                      'Wetland06' ~ 'S5',
                      'Wetland07' ~ 'S7',
                      'Wetland08' ~ 'S12',
                      'Wetland09' ~ 'S10',
                      'Wetland10' ~ 'S11',
                      'Wetland11' ~ 'S6',
                      'Wetland12' ~ 'wetland'
                ))

k_df$DateTime <- as.POSIXct(k_df$DateTime)
k_df <- k_df%>%filter(DateTime < "2022-10-01 00:00:00")


M1 <- lm(log(Flux_umol_m2_s) ~ 
         #    scale(k_m_d)+ 
             scale(log1p(pCO2_ppm)),
   #         scale(Watertemp_c) +
             data =k_df)
summary(M1)
modelPerformance(M1)

k_df$New.Name <- factor(k_df$New.Name, levels = c("S1", "S2", "S3","S4","S5","S6","S7","S8","wetland","S10","S11","S12"))

CO2_air_max <- max(k_df$pCO2_air_uatm,na.rm = TRUE)
CO2_air_min <- min(k_df$pCO2_air_uatm,na.rm = TRUE)
CO2_air_ave <- mean(k_df$pCO2_air_uatm,na.rm = TRUE)

p1 <- ggplot(k_df,aes(x=pCO2_ppm,y=Flux_umol_m2_s*10^-6*60*60*24)) + geom_point(aes(fill=New.Name),shape=21,size=3) +  
   geom_smooth(method='lm', color='black') + guides(fill=guide_legend(title="Site name"))+
  geom_rect(aes(xmin=CO2_air_min, xmax=CO2_air_max, ymin=0, ymax=Inf),fill="red",alpha=.5) +
      ylab(expression(paste("CO"[2] ,"  Evasion (mol ", m^-2," ", d^-1,")"))) +
  xlab(substitute(paste(italic('p'),CO[2], " (ppm)"))) +
  scale_x_continuous(transform = "log10") + scale_y_continuous(transform = "log10") +
  theme_bw(base_size = 18) 


```

# Modeling k or k600

surface area and solar radiation where both chosen for being significant
in lmer model. Solar radiation is the more significant variable, and if
removed, surface area is no longer selected

```{r co2 v flux and co2 v k600, echo=FALSE}


M1 <- lmer(K600 ~ 
                  scale(log(surface_area_m2)) +
             scale(log(pCO2_ppm)) +
   # scale(windspeed_m_s) +
              #    scale(solarrad_W_m2) +
             (1|Site), data =k_df ,REML=FALSE)

#mean(k_df$K600)
p2.1 <- ggplot(k_df) + geom_point(
  aes(x=surface_area_m2,y=K600),fill="#31a354",
  shape=21,size=3)  + 
  geom_hline(aes(yintercept = median(K600)), color="blue", linetype="dashed") +
  theme_bw(base_size = 16) +
  scale_x_log10() +
  xlab(expression(paste("Surface Area (",m^2, ")"))) +
    ylab(expression(paste(italic('k')[600]," (m ", d^-1,")"))) 

p2.2 <- ggplot(k_df) + geom_point(
  aes(x=pCO2_ppm,y=K600),fill="#31a354",
  shape=21,size=3)  + 
  geom_hline(aes(yintercept = median(K600)), color="blue", linetype="dashed") +
  theme_bw(base_size = 16) +
  scale_x_log10() +
 xlab(substitute(paste(italic('p'),CO[2], " (ppm)"))) +    ylab(expression(paste(italic('k')[600]," (m ", d^-1,")"))) 

p2.full <- ggarrange(p2.1,p2.2)

```

# Flux over time 

now that we have our models of CO2 and CH4, lets try plotting them over
time

```{r co2 and ch4 flux over time, echo=FALSE}
modeled_GHG_df <- read.csv(here::here("ProcessedData/modeled_GHG_df.csv"))%>%
  select(Site,DateTime,WaterTemp_c,
         M_AICc_CO2,M_BIC_CO2,CO2_umol.L_mean,
         M_AICc_CH4,M_BIC_CH4,CH4_umol.L_mean,
         F_umol.m2.s_AICc_CO2,F_umol.m2.s_BIC_CO2,F_umol.m2.s_mean_CO2,
         F_umol.m2.s_AICc_CH4,F_umol.m2.s_BIC_CH4,F_umol.m2.s_mean_CH4,
         F_umol.s_AICc_CO2,F_umol.s_BIC_CO2,F_umol.s_mean_CO2,
         F_umol.s_AICc_CH4,F_umol.s_BIC_CH4,F_umol.s_mean_CH4)
modeled_GHG_df$DateTime <- as.POSIXct(modeled_GHG_df$DateTime,format="%Y-%m-%d %H:%M:%S",tz="UTC")
modeled_GHG_df <- modeled_GHG_df%>%filter(DateTime > "2022-07-06 00:00:00" & DateTime < "2023-07-06 00:00:00")
modeled_GHG_df$New.Name <- modeled_GHG_df$Site
#,ake column with new name to reflect elevation. S stands for "site"
modeled_GHG_df <- modeled_GHG_df%>%
  mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8', 'Wetland06' ~ 'S5', 'Wetland07' ~ 'S7', 'Wetland08' ~ 'S12', 'Wetland09' ~ 'S10', 'Wetland10' ~ 'S11', 'Wetland11' ~ 'S6','Wetland12' ~ 'wetland'))
modeled_GHG_df$New.Name <- factor(modeled_GHG_df$New.Name, levels = c("S1", "S2", "S3","S4","S5","S6","S7","S8","wetland","S10","S11","S12"))

seq_df <- seq(as.POSIXct("2022-07-06 00:00:00"), as.POSIXct("2023-07-06 00:00:00"), by="hour")
seq_df <- as.data.frame(seq_df)
colnames(seq_df) <- "DateTime"

modeled_GHG_df_2 <- left_join(seq_df,modeled_GHG_df,by=c("DateTime"))
modeled_GHG_df_2 <- modeled_GHG_df_2%>%drop_na(Site)%>%select(Site,New.Name, DateTime,WaterTemp_c,F_umol.m2.s_AICc_CO2,F_umol.m2.s_BIC_CO2,F_umol.m2.s_mean_CO2,F_umol.m2.s_AICc_CH4,F_umol.m2.s_BIC_CH4,F_umol.m2.s_mean_CH4)


 melted_data <- modeled_GHG_df_2 %>%
    pivot_longer(
      cols = -c(Site,New.Name, DateTime,WaterTemp_c),  # Columns to be melted
      names_to = "Variable",      # Name of the new key column
      values_to = "Value"         # Name of the new value column
    )
melted_data$Model <- melted_data$Variable

melted_data$Model <- gsub("^[^_]*_[^_]*_", "", melted_data$Model)
melted_data$Model <- gsub("_.*", "", melted_data$Model)
  

####

p.F.co2 <- ggplot(modeled_GHG_df_2) + 
  geom_line(aes(x=DateTime,y=F_umol.m2.s_AICc_CO2),linetype = "solid",color="#1b9e77") +
  geom_line(aes(x=DateTime,y=F_umol.m2.s_BIC_CO2),linetype="solid",color="#d95f02") + 
  geom_line(aes(x=DateTime,y=F_umol.m2.s_mean_CO2),linetype="solid",color="#7570b3") + 
  facet_grid(rows = vars(New.Name), scales = "free") +
    ylab(CO[2]~(mu*mol~m^-2~s^-1)) +
  theme_bw(base_size = 14) 

p.F.ch4 <- ggplot(modeled_GHG_df_2) + 
  geom_line(aes(x=DateTime,y=F_umol.m2.s_AICc_CH4),linetype = "solid",color="#1b9e77") +
  geom_line(aes(x=DateTime,y=F_umol.m2.s_BIC_CH4),linetype="solid",color="#d95f02") + 
  geom_line(aes(x=DateTime,y=F_umol.m2.s_mean_CH4),linetype="solid",color="#7570b3") + 
  facet_grid(rows = vars(New.Name), scales = "free") +
  ylab(expression(CH[4]~(mu*mol~m^-2~s^-1))) +
  theme_bw(base_size = 14) 


############
round_numbers <- function(numbers) {
  rounded <- numeric(length(numbers))
  for (i in 1:length(numbers)) {
    if (numbers[i] < 10) {
      rounded[i] <- 0
    } else if (numbers[i] <= 99) {
      rounded[i] <- ceiling(numbers[i] / 1) * 1
    } else if (numbers[i] <= 999) {
      rounded[i] <- ceiling(numbers[i] / 10) * 10
    } else if (numbers[i] <= 9999) {
      rounded[i] <- ceiling(numbers[i] / 100) * 100
    }
  }
  return(rounded)
}
# defining the breaks function, 
# s is the scaling factor (cf. multiplicative expand)
equal_breaks_origional <- function(n = 3, s = 0.05, ...){
  function(x){
    # rescaling
    d <- s * diff(range(x)) / (1+2*s)
    #round_numbers(
    round_numbers(seq(min(x)+d, max(x)-d, length=n))
    #)
  }
}

equal_breaks <- function(x){
    breaks <- round_numbers(c(min(x),((max(x)-min(x))/2),max(x)))
 #   names(breaks) <- attr(breaks,"labels")
    breaks
}


p.F.ch4 <- ggplot(melted_data %>%filter(Variable=="F_umol.m2.s_AICc_CH4"|Variable=="F_umol.m2.s_BIC_CH4"|Variable=="F_umol.m2.s_mean_CH4")%>%filter(WaterTemp_c<15))+
  geom_point(aes(x=DateTime,y=Value*60*60,color=Model),size=.1) +
  facet_grid(rows = vars(New.Name), scales = "free") +
    ylab(expression(CH[4]~evasion~~(mu*mol~m^-2~s^-1))) + xlab("Date Time") + scale_y_continuous(breaks=breaks_pretty(n=3)) +
  theme_bw(base_size = 12) + guides(color = guide_legend(override.aes = list(size=3)))

p.F.CO2 <- ggplot(melted_data%>%filter(Variable=="F_umol.m2.s_AICc_CO2"|Variable=="F_umol.m2.s_BIC_CO2"|Variable=="F_umol.m2.s_mean_CO2")) + 
  geom_point(aes(x=DateTime,y=Value*60*60,color=Model),size=.1) +
  facet_grid(New.Name ~ ., switch = "y",scales = "free") +  ylab(expression(CO[2]~evasion~~(mu*mol~m^-2~s^-1))) + xlab("Date Time") +
  scale_y_continuous(breaks=breaks_pretty(n=3),position = "right") + 
theme_bw(base_size = 12)+
 theme(strip.placement = "outside")

full_1 <- ggarrange(p.F.ch4, p.F.CO2, ncol = 2, nrow = 1,common.legend = TRUE)
```

# High temp ch4 flux

this is script to figure our how to talk about ch4 flux at S2 and S3

```{r high temp flux, echo=FALSE}
test <- modeled_GHG_df%>%#filter(WaterTemp_c>15)%>%
filter(Site=="Wetland02")%>%drop_na(WaterTemp_c)
test <- modeled_GHG_df%>%filter(WaterTemp_c>15)%>%filter(Site=="Wetland04")%>%drop_na(WaterTemp_c)
#wetland 2
```

# Extrapolated flux bargraph

```{r sum flux, echo=FALSE}
modeled_GHG_sum_df <- modeled_GHG_df%>%
  select(Site,DateTime,
         F_umol.s_AICc_CO2,F_umol.s_BIC_CO2,F_umol.s_mean_CO2,
         F_umol.s_AICc_CH4,F_umol.s_BIC_CH4,F_umol.s_mean_CH4)
modeled_GHG_sum_df$month_Day <-  format(as.Date(modeled_GHG_sum_df$DateTime,format="%Y-%m-%d"), format = "%m-%d")
modeled_GHG_sum_df_2 <- modeled_GHG_sum_df%>%group_by(Site,month_Day)%>%
  summarise(
    F_AICc_CO2_umol.day = mean(F_umol.s_AICc_CO2,na.rm=TRUE),
    F_BIC_CO2_umol.day = mean(F_umol.s_BIC_CO2,na.rm=TRUE),
    F_mean_CO2_umol.day = mean(F_umol.s_mean_CO2,na.rm=TRUE),
    F_AICc_CH4_umol.day = mean(F_umol.s_AICc_CH4,na.rm=TRUE),
    F_BIC_CH4_umol.day = mean(F_umol.s_BIC_CH4,na.rm=TRUE),
    F_mean_CH4_umol.day = mean(F_umol.s_mean_CH4,na.rm=TRUE)
  )
modeled_GHG_sum_df_2$F_AICc_CO2_umol.day <- modeled_GHG_sum_df_2$F_AICc_CO2_umol.day*60*60*24
modeled_GHG_sum_df_2$F_BIC_CO2_umol.day <- modeled_GHG_sum_df_2$F_BIC_CO2_umol.day*60*60*24
modeled_GHG_sum_df_2$F_mean_CO2_umol.day <- modeled_GHG_sum_df_2$F_mean_CO2_umol.day*60*60*24
modeled_GHG_sum_df_2$F_AICc_CH4_umol.day <- modeled_GHG_sum_df_2$F_AICc_CH4_umol.day*60*60*24
modeled_GHG_sum_df_2$F_BIC_CH4_umol.day <- modeled_GHG_sum_df_2$F_BIC_CH4_umol.day*60*60*24
modeled_GHG_sum_df_2$F_mean_CH4_umol.day <- modeled_GHG_sum_df_2$F_mean_CH4_umol.day*60*60*24

modeled_GHG_sum_df_3 <- modeled_GHG_sum_df_2%>%group_by(Site)%>%
  summarise(
    F_AICc_CO2_umol.year = mean(F_AICc_CO2_umol.day,na.rm=TRUE),
    F_BIC_CO2_umol.year = mean(F_BIC_CO2_umol.day,na.rm=TRUE),
    F_mean_CO2_umol.year = mean(F_mean_CO2_umol.day,na.rm=TRUE),
    F_AICc_CH4_umol.year = mean(F_AICc_CH4_umol.day,na.rm=TRUE),
    F_BIC_CH4_umol.year = mean(F_BIC_CH4_umol.day,na.rm=TRUE),
    F_mean_CH4_umol.year = mean(F_mean_CH4_umol.day,na.rm=TRUE)
  )

modeled_GHG_sum_df_3$F_AICc_CO2_umol.year <- modeled_GHG_sum_df_3$F_AICc_CO2_umol.year * 365 
modeled_GHG_sum_df_3$F_BIC_CO2_umol.year <- modeled_GHG_sum_df_3$F_BIC_CO2_umol.year * 365
modeled_GHG_sum_df_3$F_mean_CO2_umol.year <- modeled_GHG_sum_df_3$F_mean_CO2_umol.year * 365
modeled_GHG_sum_df_3$F_AICc_CH4_umol.year <- modeled_GHG_sum_df_3$F_AICc_CH4_umol.year * 365
modeled_GHG_sum_df_3$F_BIC_CH4_umol.year <- modeled_GHG_sum_df_3$F_BIC_CH4_umol.year * 365
modeled_GHG_sum_df_3$F_mean_CH4_umol.year <- modeled_GHG_sum_df_3$F_mean_CH4_umol.year * 365

#convert to mol and then to gC-CO2
 melted_data_2 <- modeled_GHG_sum_df_3 %>%
    pivot_longer(
      cols = -c(Site),  # Columns to be melted
      names_to = "Model",      # Name of the new key column
      values_to = "umol.year"         # Name of the new value column
    )
 
 melted_data_2$New.Name <- melted_data_2$Site
#,ake column with new name to reflect elevation. S stands for "site"
melted_data_2 <- melted_data_2%>%
  mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8', 'Wetland06' ~ 'S5', 'Wetland07' ~ 'S7', 'Wetland08' ~ 'S12', 'Wetland09' ~ 'S10', 'Wetland10' ~ 'S11', 'Wetland11' ~ 'S6','Wetland12' ~ 'wetland'))
melted_data_2$New.Name <- factor(melted_data_2$New.Name, levels = c("S10","S6","S11","S12","S5","S4","S7","S8","S3","S2","wetland","S1"))

 
melted_data_2$Variable <- melted_data_2$Model

melted_data_2$Model <- gsub("^[^_]*_", "", melted_data_2$Model)
melted_data_2$Model <- gsub("_.*$", "", melted_data_2$Model)
 
melted_data_2$mol.year <- melted_data_2$umol.year/10^6

melted_data_2_co2 <- melted_data_2%>%filter(Variable=="F_AICc_CO2_umol.year"|Variable=="F_BIC_CO2_umol.year"|Variable=="F_mean_CO2_umol.year")
melted_data_2_ch4 <- melted_data_2%>%filter(Variable=="F_AICc_CH4_umol.year"|Variable=="F_BIC_CH4_umol.year"|Variable=="F_mean_CH4_umol.year")

melted_data_2_co2$gCasCO2.year <- melted_data_2_co2$mol.year*12
  
melted_data_2_ch4$gCasCH4.year <- melted_data_2_ch4$mol.year*12

#plot


p.ch4 <- ggplot(data=melted_data_2_ch4, aes(x=New.Name, y=gCasCH4.year, fill=Model)) +
geom_bar(stat="identity", color="black", position=position_dodge()) +
    theme_bw(base_size = 16) +
    ylab(expression("grams of"~CH[4]~"as C"~~year^-1)) +
  xlab("") +  theme(legend.position = "top")

p.co2<- ggplot(melted_data_2_co2) + aes(x = New.Name, y = gCasCO2.year, fill=Model) +
  geom_bar(stat="identity", color="black", position=position_dodge())+
  ylab(expression("grams of"~CO[2]~"as C"~~year^-1)) +
  xlab("Site \n(ordered by increasing surface area)") +
  scale_y_cut(breaks=c(.8*10^5), which=c(1, 2), scales=c(0.5, 3)) +
  theme_bw(base_size = 16) + theme(legend.position = "none")


library(cowplot)


full_2 <- ggarrange(p.ch4, p.co2, ncol = 1, nrow = 2,common.legend = TRUE)


##calcuate % difference 
co2_sum <- melted_data_2_co2 %>%select(Model,Site,gCasCO2.year)%>%
  pivot_wider(names_from = c(Model), values_from = gCasCO2.year)
co2_sum$meanvAIC <- (co2_sum$AICc - co2_sum$mean)/(co2_sum$AICc + co2_sum$mean)/2 * 100
co2_sum$meanvBIC <- (co2_sum$BIC - co2_sum$mean)/(co2_sum$BIC + co2_sum$mean)/2 * 100
co2_sum_2 <- co2_sum%>%filter(Site!="Wetland01")

ch4_sum <- melted_data_2_ch4 %>%select(Model,Site,gCasCH4.year)%>%
  pivot_wider(names_from = c(Model), values_from = gCasCH4.year)
ch4_sum$meanvAIC <- (ch4_sum$AICc - ch4_sum$mean)/(ch4_sum$AICc + co2_sum$mean)/2 * 100
ch4_sum$meanvBIC <- (ch4_sum$BIC - ch4_sum$mean)/(ch4_sum$BIC + co2_sum$mean)/2 * 100

mean(ch4_sum$meanvAIC,na.rm=TRUE)
mean(ch4_sum$meanvBIC,na.rm=TRUE)
```

```{r holgerson and raymond, echo=FALSE}

df_merge <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))%>%rename("Site_Name"="Site")
df_merge$Area_ha <-  df_merge$surface_area_m2 / 10000
df_merge$Reference <- "This Study"
df_merge$Location <- "La Virgen"
df_merge$latitude <- -0.324311
df_merge$longitude <- -78.1995
df_merge$Study.Years <- 2022
df_merge <- df_merge%>%select(Reference,Site_Name,Location,latitude,longitude,Study.Years,CH4_umol.L,CO2_umol.L,Area_ha,Watertemp_c)

#read in Holgerston & Raymond data set
df_Holg <- read.csv(here::here("Wetlands/Holgerson&Raymond_data1.csv"))%>%rename("Site_Name"="Site.Name","CH4_umol.L"="ch4..umol.L.","CO2_umol.L"="co2..umol.L.","Area_ha"="area..ha.","Watertemp_c"="temp..C.")%>%select(Reference,Site_Name,Location,latitude,longitude,Study.Years,CH4_umol.L,CO2_umol.L,Area_ha,Watertemp_c)

df_Holg <- rbind(df_Holg,df_merge)
df_Holg$CH4_umol.L <- as.numeric(df_Holg$CH4_umol.L)
df_Holg$CO2_umol.L <- as.numeric(df_Holg$CO2_umol.L)
df_Holg$Watertemp_c <- as.numeric(df_Holg$Watertemp_c)

df_Holg$New.Name <- df_Holg$Site_Name
df_Holg <- df_Holg%>%
  mutate(New.Name = case_match(New.Name, 'Wetland01' ~ 'S1', 'Wetland02' ~ 'S2','Wetland03' ~ 'S3','Wetland04' ~ 'S4','Wetland05' ~ 'S8', 'Wetland06' ~ 'S5', 'Wetland07' ~ 'S7', 'Wetland08' ~ 'S12', 'Wetland09' ~ 'S10', 'Wetland10' ~ 'S11', 'Wetland11' ~ 'S6','Wetland12' ~ 'wetland'))
df_Holg$New.Name <- factor(df_Holg$New.Name, levels = c("S1", "S2", "S3","S4","S5","S6","S7","S8","wetland","S10","S11","S12"))

#summarize for discussion
df_Holg_test <- df_Holg%>%filter(Area_ha < .6)
df_Holg_test2 <- df_Holg%>%filter(Area_ha < .6)%>%filter(Reference != "This Study")
df_Holg_test_sum <- df_Holg_test%>%group_by(Reference)%>%
  summarise(
    max_CH4 = max(CH4_umol.L,na.rm=TRUE),
    min_CH4 = min(CH4_umol.L,na.rm=TRUE),
    ave_CH4 = mean(CH4_umol.L,na.rm=TRUE),
    std_CH4 = sd(CH4_umol.L,na.rm=TRUE),
    var_CH4 = var(CH4_umol.L,na.rm=TRUE),
    max_CO2 = max(CO2_umol.L,na.rm=TRUE),
    min_CO2 = min(CO2_umol.L,na.rm=TRUE),
    ave_CO2 = mean(CO2_umol.L,na.rm=TRUE),
    stdv_CO2 = sd(CO2_umol.L,na.rm=TRUE),
    var_CO2 = var(CO2_umol.L,na.rm=TRUE),
    n()
  
)

df_Holg_test2 <- df_Holg%>%filter(Area_ha < .6)%>%filter(Reference == "Bastviken et al. (2004)")

p.test <- ggplot() +
  geom_point(data=df_Holg ,aes(x=Watertemp_c,y=CO2_umol.L),color='grey',size=3) +
  geom_point(data=df_Holg_test2%>%filter(Area_ha < .6),
             aes(x=Watertemp_c,y=CO2_umol.L),color="black",size=3) +
  geom_point(data=df_Holg%>%filter(Reference=="This Study"),
             aes(x=Watertemp_c,y=CO2_umol.L,color=New.Name),size=3) +
  scale_y_log10() + scale_x_log10() + scale_color_discrete(name = "Site") +
  theme_bw(base_size = 16) 


#log co2 v ch4
p <- ggplot() +
  geom_point(data=df_Holg,aes(x=CO2_umol.L,y=CH4_umol.L),color='grey',size=3) +
  geom_point(data=df_Holg_test2%>%filter(Area_ha < .6),
             aes(x=CO2_umol.L,y=CH4_umol.L),color="black",size=3) +
  geom_point(data=df_Holg%>%filter(Reference=="This Study"),
             aes(x=CO2_umol.L,y=CH4_umol.L,color=New.Name),size=3) +
    xlab(expression(paste("CO"[2] ," (",mu,"mol ", L^-1,")"))) +
    ylab(expression(paste("CH"[4] ," (",mu,"mol ", L^-1,")"))) +
  scale_y_log10() + scale_x_log10() + scale_color_discrete(name = "Site") +
  theme_bw(base_size = 16) 

```

#summary \> most of our sites lower than in Hamilton et al. (1994) The
studyarea was locatedin the high boreal and low subarcticwetlandregionof
the HudsonBay Lowland with the baseof operations at Moosonee, Ontario
TheHBL is comprised of approximately 85-90%wetlandareas[Pala and
Boissonneau,1982] and the entire area is underlain with impermeable
glacial moraineclays and silts

> our sites mostly lower in Kankaala et al. (2013) Kokema¨ enjoki
> drainage basin, southern Finland (Fig. 1). The lakes are rather
> shallow (maximum depth [z m ] 5–32 m, mean depth 2.4–10 m. Coniferous
> forests with Norway spruce (Picea abies) and Scots pine (Pinus
> sylvestris) cover 55–80% while peatlands cover , 20% of the catchment
> areas of the lakes

> our sites, all lower than Holgerson (2015)

```         
> research forest in Tolland and Windham Counties, Connecticut, USA. The ponds are located in mixed deciduous-coniferous forest with minimal human disturbance. The soil types are Charlton-Chatfield Complex (Blacksmith, E8, Quarry, Woodpile Ponds) and Hinckley gravelly sandy loam
```

> Higher or within range of Laurion et al. (2010) subarctic
> discontinuous permafrost region, in the arctic continuous permafrost
> region. The subarctic thaw ponds are surrounded by dense shrubs
> (Betula glandulosa, Salix sp., Alnus sp., Myrica gale) and sparse
> trees (Picea mariana, Picea glauca, Larix laricina), with some areas
> colonized by Sphagnum spp. mosses. These thermokarst ponds are formed
> in depressions (1–3-m deep) left after the ice has melted below
> mineral mounds.

> Pelletier et al. (2014) where in the middle of our sites boreal
> peatland

> Shirokova et al. 2013 ocupied a ery similar range to our sites forest,
> forest-tundra, and tundra landscape that has been developed on
> discontinuous and sporadic permafrost; the discontinuous permafrost
> exists over Neocene sand and clay deposits, and is covered by a peat
> layer of 1–2 m. The ponds and lakes in this study originate from
> permafrost melt (soil subsidence)

> Bastviken et al. (2004)'s one sample is lower in methane

> ours sites similar range to 3 points in Delveccia et al 2019 (co2
> only)

```         
> Mexican Cut Nature Preserve in the Elk Mountains of central Colorado, a pristine, subalpine wilderness area
```

# Wetland sampling

```{r gavi wetland, echo=FALSE}
gavi_df <- read.csv(here::here("ProcessedData/PondPaper_k600.csv"))%>%filter(Site=="Wetland12")%>%select(Site, Date, CH4_umol.L, CO2_umol.L, Watertemp_c)
gavi_df$Date <- as.Date(gavi_df$Date,format = "%Y-%m-%d")
gavi_df$Location <- "center"
gavi_df$Site2 <- NA
gavi_df$Lat <- -0.328064
gavi_df$Lon <- -78.200203
 
drone_GHG <- read.csv(here::here("ProcessedData/Drone_Gavi_sampling_GHG.csv"))%>%select(Lat,Lon,Site, Site2, Date, CH4_umol.L, CO2_umol.L, Watertemp_c)

##pecent diff of dups
drone_GHG_summ2 <- drone_GHG%>%group_by(Site,Date,Site2)%>%summarise(
  CH4_min = min(CH4_umol.L),
  CH4_max = max(CH4_umol.L))
drone_GHG_summ2$percent_diff <-  (drone_GHG_summ2$CH4_max-drone_GHG_summ2$CH4_min)/
(drone_GHG_summ2$CH4_max+drone_GHG_summ2$CH4_min)/2 *100
percent_diff_ave <- (sum(drone_GHG_summ2$percent_diff,na.rm=TRUE)+0) / 13
##pecent diff of dups

drone_GHG_summ <- drone_GHG%>%group_by(Lat,Lon,Site,Date,Site2)%>%summarise(
  CH4_umol.L = mean(CH4_umol.L,rm.na=TRUE),
  CO2_umol.L = mean(CO2_umol.L,rm.na=TRUE),
  Watertemp_c = mean(Watertemp_c,rm.na=TRUE)
)


drone_GHG_summ$Date <- as.Date(drone_GHG_summ$Date,format = "%m/%d/%y")
drone_GHG_summ$Location <- "margins"

df <- rbind(gavi_df,drone_GHG_summ)
df_melt <- df %>%select(Location,Date,Site2,CH4_umol.L,CO2_umol.L)%>%
    pivot_longer(
      cols = -c(Location,Date,Site2),  # Columns to be melted
      names_to = "gas",      # Name of the new key column
      values_to = "umol.L"         # Name of the new value column
    )
 

p2 <- ggplot(df_melt,aes(x=gas, y=umol.L,fill=Location)) +
  geom_boxplot() +
  geom_point(shape=21,color="black",position = position_jitterdodge(jitter.width = .25, jitter.height = 0, dodge.width = 0.75)) +   ylab(expression(paste("(",mu,"mol ", L^-1,")"))) +
  scale_fill_discrete(labels=c("open-water \ntransect","wetland \nmargins")) + 
    scale_x_discrete(labels=c("CH4_umol.L" = expression(paste("CH"[4] )), "CO2_umol.L" = expression(paste("CO"[2] )))) +
  scale_y_log10() + theme_bw(base_size = 24) + theme(legend.position="top")

###export to make fig in gavi
df <- rbind(gavi_df%>%filter(Date==as.Date("2022-10-16")),drone_GHG_summ)%>%drop_na(CH4_umol.L)


#write.csv(df,here::here("ProcessedData/GaviSample_toExport.csv"))
```

```{r gavi wetland, echo=FALSE}

ggplot(df_merge) + geom_point(aes(x=log(DOC_mg.L),y=log(TDN_mg.L),color=Site_Name))

```
