---
title: "Water Level and Discharge at Cayambe Coca"
author: "KWhitmore"
date: "06/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate) #package for our date parsing
library(here)
library(dplyr)
library(ggplot2)
library(reshape2)
library(purrr)
library(sjmisc)
library(plotly)
#theme_set(theme_bw())

```

## Water Level at Cayambe Coca
In this R markdown, I document processing of Water Level Data collected at Cayambe Coca in 2021. This script is used in the development of a discharge rating curve

This is the final version of Rscript "WLBaroCorrected_2021-12-14" 

### First I will read in the water levels that are collected by Hobo sensors

```{r Hobo WL}
#First the Hobos

setwd(here::here("Water_Level/Stations"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = site_names[site_names != "WL_01"]

#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      WLData <- read.csv(file, skip=11, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(WLData[1,3],"Abs Pres, psi")){
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*6.89476
        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000

      } else { 
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        }
      
#      WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
    WLData$DateTime <- as.POSIXct(WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
    }
    if (exists("WLData")){
      Temp_WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
#      
      
      if(str_contains(Temp_WLData[1,3],"Abs Pres, psi")){
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*6.89476
        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        
        
      } else { 
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        }
      
#      Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, format="%m/%d/%y %I:%M:%S %p", tz="UTC")
          Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, tz="UTC",
           tryFormats = c("%m/%d/%y %I:%M:%S %p",
                          "%m/%d/%Y %H:%M"))
      
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData$DateTime <- round_date(WLData$DateTime, "15 mins")
  WLData$Station <- site
  WLData=unique(WLData)
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}
```

### Now read in solinst
We collect water level using hobo and solinst, so we need two differnt loops

```{r Solinst, echo=FALSE}

setwd(here::here("Water_Level/Stations"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop

site_names = "WL_01"

#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      Trash_WLData <- read.csv(file, skip=1, header = TRUE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(Trash_WLData[6,1],"m")){
        print("m")
        WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                    quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        colnames(WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*9.8064
#        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000
        } else { 
        print("kPa")
        WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
            quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        colnames(WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
      }
    }
    if (exists("WLData")){
      Trash_WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      if(str_contains(Trash_WLData[6,1],"m")){
        print("m")
        Temp_WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        Temp_WLData <- Temp_WLData[c(-1),]
        colnames(Temp_WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*9.8064
#        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        } else { 
        print("kpa")
        Temp_WLData <- read.csv(file, skip=11, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")
        Temp_WLData <- Temp_WLData[c(-1),]
        colnames(Temp_WLData)=c("Date","Time","ms","WLPres_kpa","WLTemp_c")
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
      }
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData=unique(WLData)
  WLData$DateTime <- paste(WLData$Date, WLData$Time)
  WLData$DateTime <- as.POSIXct(WLData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  WLData$DateTime <- round_date(WLData$DateTime, "5 mins")
  WLData <- WLData[,c("DateTime","WLPres_kpa","WLTemp_c")]
  WLData$Station <- site
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}


```

## plot 
plot the water level so that each station data can be cleaned

```{r plot, echo=FALSE}

##clean data
plot_ly(WL_01, x = ~DateTime, y = ~WLPres_kpa, type = 'scatter', mode = 'markers') 

```

### clean
this script is for cleaning each station. There may be additional lines written for each data file downloaded

```{r clean, echo=FALSE}

```
### bind
bind all sites together

```{r bind, echo=FALSE}

All_WL <- rbind(WL_01,WL_02,WL_03,WL_04,WL_05,WL_06)

```
## barometric data
now read in the barometric data

```{r baro loop, echo=FALSE}

###merge data with baro data###
setwd(here::here("Water_Level/BaroPress"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
site_names="Baro" #creates list of site names for following loop

#rm old files, if they exsist
rm(BaroData)
rm(Temp_BaroData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("BaroData")){
      BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
    }
    if (exists("BaroData")){
      Temp_BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      BaroData <- rbind(BaroData, Temp_BaroData)
      rm(Temp_BaroData)
    }
    
  }
  colnames(BaroData)=c("Date","Time","ms","Baro_kpa","BaroTemp_c")
  BaroData=unique(BaroData)
  BaroData$DateTime <- paste(BaroData$Date, BaroData$Time)
  BaroData$DateTime <- as.POSIXct(BaroData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  BaroData$DateTime <- round_date(BaroData$DateTime, "15 mins")
  BaroData$ms <- NULL
  BaroData$Date <- NULL
  BaroData$Time <- NULL
  BaroData <- BaroData[,c(3,1,2)]
  BaroData=unique(BaroData)
  assign((paste(site,sep="_")),BaroData) #creates object with new appended data
  rm(BaroData) #removes WLdata so that multiple sites aren't appended together
}
```
### clean baro
```{r clean baro, echo=FALSE}

##clean BaroData
plot_ly(Baro%>%filter(DateTime > as.POSIXct("2021-06-11 00:00:00", tz = "UTC")), x = ~DateTime, y = ~Baro_kpa, type = 'scatter', mode = 'markers') 

Baro <- Baro%>%filter(DateTime > as.POSIXct("2021-06-11 13:30:00", tz = "UTC"))

```

### correct for barometric pressure
```{r baro correct, echo=FALSE}

#correct for baro 

plot_ly(Baro, x = ~DateTime, y = ~Baro_kpa, type = 'scatter', mode = 'markers') 

Baro_corrected <- left_join(Baro,All_WL,by="DateTime")

Baro_corrected$Corrected_kpa <- Baro_corrected$WLPres_kpa - Baro_corrected$Baro_kpa

#calculate total pressure to correct viasala readings
Baro_corrected$Total_kpa <- 
  Baro_corrected$WLPres_kpa
#Baro_corrected <- Baro_corrected %>% filter(DateTime > "2021-06-10")

#convert kpa to meters of water
# constant, 1 kpa = 0.101972 m water
Baro_corrected$WL_m <- Baro_corrected$Corrected_kpa * 0.101972
Baro_corrected$Corrected_kpa <- NULL

```

## plot final data

```{r plot final, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

ggplot(data = Baro_corrected %>% filter(DateTime > "2021-01-01"), 
       aes(DateTime, WL_m)) +
  geom_line(color = "steelblue") +
  labs(#title = "CO2  stations",
    y = "meter water", x = "") + 
  facet_wrap(~ Station)


plot_ly(Baro_corrected %>% filter(Station == "WL_01"), x = ~DateTime, y = ~Total_kpa, type = 'scatter', mode = 'markers') 
```
## build curve
this line of script can be easily altered to find  water levels at select points in time
```{r build curve, echo=FALSE}
Baro_corrected %>% filter(DateTime == as.POSIXct("2022-07-27 09:45:00", tz = "UTC") &
                            Station == "WL_02")

```

## Discharge Rating Curve
these equations were developed using excel software. 
Find equations in Discharge> Rating curve folder

```{r Discharge, echo=FALSE}
#stations 1 and 2
  #use stn 2 WL for both
#Q = 1.2949*WL_m^2 - 0.1622*WL_m + 0.0041
    #R² = 0.957


```
### bind together again

```{r bind again, echo=FALSE}

All_WL <- rbind(WL_01,WL_02,WL_03)

#All_Well <- Baro_corrected %>% filter(Station == "WL_Well01"|Station == "WL_Well02")
#All_Well <- All_Well[,c("DateTime","BaroTemp_c","WLTemp_c","Station","WL_m","Total_kpa")]
#All_Well$Q_m3s <- NA

#All_WL_wide <- 

```

# plot discharge

```{r plot Q, echo=FALSE}

##Now we can graph 
    ## will need to change the right limit accordingly

#ggplot(data = All_WL %>% filter(DateTime > "2021-06-10"), 
#       aes(DateTime, Q_m3s)) +
 # geom_line(color = "steelblue") +
  #labs(#title = "Discharge",
   # y = "Discharge m^3 s^-1", x = "") + 
  #facet_wrap(~ Station)

#plot_ly(All_WL%>%filter(Station == "WL_01"), x = ~DateTime, y = ~Total_kpa, type = 'scatter', mode = 'markers') 

```

```{r write, echo=FALSE}


```