---
title: "Rating Curves"
author: "Andrew"
date: "10/30/2019"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(here)
library(plotly)
```

# Can we interpolate the missing data?
```{r loadData}
# Sensor data with water level -  we will add discharge to this
df <- read.csv(here("data_4_analysis/All_Stream_Data.csv"))

# Discharge Data - we will create rating curves with this
discharge <- read.csv(here("data_4_analysis/recorded_discharge.csv"))
discharge$DateTime <-as.POSIXct(paste0(discharge$Date,"",discharge$Time),format = "%m/%d/%Y %H:%M")
discharge <- discharge%>%
  select(DateTime,Stn,Level,Discharge)
```

# Now let's work on the rating curves
```{r discharge}
discharge <- read.csv(here("data_4_analysis/recorded_discharge.csv"))
discharge$DateTime <-as.POSIXct(paste0(discharge$Date,"",discharge$Time),format = "%m/%d/%Y %H:%M")
discharge <- discharge%>%
  select(DateTime,Stn,Level,Discharge)

ggplot(discharge)+
  geom_point(aes(x = Discharge, y = Level, col = Stn), size = 3)
```

## Station 1 Rating Curve
Set up variables:
```{r stn1var, echo=FALSE, warning=FALSE}
stn1 <- discharge%>%
  filter(Stn == "Station 1")%>%
  na.omit()%>%
  arrange(Level)

x<-stn1$Level
y<-stn1$Discharge
```

### Exponential model (Station 1)
Test exponential model for station 1:
```{r stn1Exp}

exponential.model <- lm(log(y)~ x)  # Create the model
exp.predict <- exp(predict(exponential.model,list(Level=x)))  # Create predicted values for recorded discharge values

ggplot()+
  geom_point(aes(x,y))+
  geom_line(aes(x,exp.predict),col = 'red')+
  labs(x = "Level (m)", y = expression(paste("Discharge ", m^{3}/s^{-1})), title ="Station 1 Exponential Model ")

# Print the Summary
summary(exponential.model)
```

### Quadratic Model (Station 1)
Test Quadratic model for station 1:
```{r stn1Quad}

x2 <- x^2
quadratic.model <-lm(y ~ x + x2)

# Use the model to predict values for the rating curve
quadPred <- predict(quadratic.model,list(Level=x, Level2=x^2))

# plot the predicted(line) vs observed (points)
ggplot()+
  geom_point(aes(x,y))+
  geom_line(aes(x,quadPred),col = 'red')+
  labs(x = "Level (m)", y = expression(paste("Discharge ", m^{3}/s^{-1})), title ="Station 1 Quadratic Model ")

# Print the summary of the quadratic model
summary(quadratic.model)
```


### Kriddie Model (Station 1)
```{r}
#df$stn1_Q_kw <- 0.8823-10.3227*(df$lvl_421_m)+32.2560*(df$lvl_421_m)^2
```



### Decide on model and write it to dataset
Units here are liters per second
```{r stn1Choice}
# Exponential Model:
#df$stn1_Q <- exp(predict(exponential.model,data.frame(x=df$lvl_436_m)))*1000

# Quadratic Model
#df$stn1_Q <- predict(quadratic.model,list(x=df$lvl_436_m, x2=df$lvl_436_m^2))*1000

# Kriddies way
df$stn1_Q <- (0.8823-10.3227*(df$lvl_421_m)+32.2560*(df$lvl_421_m)^2)*1000

#plot(df$stn1_Q~df$stn1_Q_kw)
```

## Station 2 Rating Curve
Set up variables:
```{r stn2var, echo=FALSE, warning=FALSE}
stn2 <- discharge%>%
  filter(Stn == "Station 2")%>%
  na.omit()%>%
  arrange(Level)

x<-stn2$Level
y<-stn2$Discharge
```

### Exponential model (Station 2)
Test exponential model for station 2:
```{r stn2Exp}

exponential.model <- lm(log(y)~ x)  # Create the model
exp.predict <- exp(predict(exponential.model,list(Level=x)))  # Create predicted values for recorded discharge values

plot_ly(x = x, y=y)%>%
  add_markers()%>%
  add_lines(x = x, y=exp.predict)%>%
  layout(
    xaxis = list(title = "Water Level (m)", type = "log"),
    yaxis = list(title = "Discharge")
  )

# Print the Summary
summary(exponential.model)
```

### Quadratic Model (Station 2)
Test Quadratic model for station 2:
```{r stn2Quad}

x2 <- x^2
quadratic.model <-lm(y ~ x + x2)

# Use the model to predict values for the rating curve
quadPred <- predict(quadratic.model,list(Level=x, Level2=x^2))

# plot the predicted(line) vs observed (points)
ggplot()+
  geom_point(aes(x,y))+
  geom_line(aes(x,quadPred),col = 'red')+
  labs(x = "Level (m)", y = expression(paste("Discharge ", m^{3}/s^{-1})), title ="Station 2 Quadratic Model ")

# Print the summary of the quadratic model
summary(quadratic.model)
```

### Kriddie Model (Station 2)
```{r}
#df$stn2_Q_kw <- (0.8823-10.3227*(df$lvl_421_m)+32.2560*(df$lvl_421_m)^2)*1000
```

### Decide on model and write it to dataset
Units here are liters per second
```{r stn2Choice}
# Exponential Model:
#df$stn2_Q <- exp(predict(exponential.model,data.frame(x=df$lvl_436_m))) *1000

# kriddie's way
df$stn2_Q <- (0.8823-10.3227*(df$lvl_421_m)+32.2560*(df$lvl_421_m)^2)*1000
```

## Station 3 Rating Curve
Set up variables:
```{r stn3var, echo=FALSE, warning=FALSE}
stn3 <- discharge%>%
  filter(Stn == "Station 3")%>%
  na.omit()%>%
  arrange(Level)

x<-stn3$Level
y<-stn3$Discharge
```

### Exponential model (Station 3)
Test exponential model for station 3:
```{r stn3Exp}

exponential.model <- lm(log(y)~ x)  # Create the model
exp.predict <- exp(predict(exponential.model,list(Level=x)))  # Create predicted values for recorded discharge values

ggplot()+
  geom_point(aes(x,y))+
  geom_line(aes(x,exp.predict),col = 'red')+
  labs(x = "Level (m)", y = expression(paste("Discharge ", m^{3}/s^{-1})), title ="Station 3 Exponential Model ")

# Print the Summary
summary(exponential.model)
```

### Quadratic Model (Station 3)
Test Quadratic model for station 3:
```{r stn3Quad}

x2 <- x^2
quadratic.model <-lm(y ~ x + x2)

# Use the model to predict values for the rating curve
quadPred <- predict(quadratic.model,list(Level=x, Level2=x^2))

# plot the predicted(line) vs observed (points)
ggplot()+
  geom_point(aes(x,y))+
  geom_line(aes(x,quadPred),col = 'red')+
  labs(x = "Level (m)", y = expression(paste("Discharge ", m^{3}/s^{-1})), title ="Station 3 Quadratic Model ")

# Print the summary of the quadratic model
summary(quadratic.model)
```

### Kriddie Model (Station 3)
```{r}
#df$stn3_Q_kw <-(0.3427-4.5198*(df$lvl_421_m)+17.0234*(df$lvl_421_m)^2)*1000
```

### Decide on model and write it to dataset
Units here are liters per second
```{r stn3Choice}
# Exponential Model:
#df$stn3_Q <- exp(predict(exponential.model,data.frame(x=df$lvl_421_m)))*1000

# kriddie model
df$stn3_Q <-(0.3427-4.5198*(df$lvl_421_m)+17.0234*(df$lvl_421_m)^2)*1000

#plot(df$stn3_Q~df$stn3_Q_kw)
```

## Station 4 Rating Curve
Set up variables:
```{r stn4var, echo=FALSE, warning=FALSE}
stn4 <- discharge%>%
  filter(Stn == "Station 4")%>%
  na.omit()%>%
  arrange(Level)

x<-stn4$Level
y<-stn4$Discharge
```

### Exponential model (Station 4)
Test exponential model:
```{r stn4Exp}

exponential.model <- lm(log(y)~ x)  # Create the model
exp.predict <- exp(predict(exponential.model,list(Level=x)))  # Create predicted values for recorded discharge values

ggplot()+
  geom_point(aes(x,y))+
  geom_line(aes(x,exp.predict),col = 'red')+
  labs(x = "Level (m)", y = expression(paste("Discharge ", m^{3}/s^{-1})), title ="Station 4 Exponential Model ")

# Print the Summary
summary(exponential.model)
```


### Quadratic Model (Station 4)
Test Quadratic model for station 4:
```{r stn4Quad}

x2 <- x^2
quadratic.model <-lm(y ~ x + x2)

# Use the model to predict values for the rating curve
quadPred <- predict(quadratic.model,list(Level=x, Level2=x^2))

# plot the predicted(line) vs observed (points)
ggplot()+
  geom_point(aes(x,y))+
  geom_line(aes(x,quadPred),col = 'red')+
  labs(x = "Level (m)", y = expression(paste("Discharge ", m^{3}/s^{-1})), title ="Station 4 Quadratic Model ")

# Print the summary of the quadratic model
summary(quadratic.model)
```

### Kriddie Model (Station 4)
```{r}
#df$stn4_Q_kw <- (0.02759-1.4345*(df$lvl_421_m)+9.84825*(df$lvl_421_m)^2)*1000
```

### Decide on model and write it to dataset
Units here are liters per second
```{r stn4Choice}
# Exponential Model:
#df$stn4_Q <- exp(predict(exponential.model,data.frame(x=df$lvl_421_m)))*1000

# KW model
df$stn4_Q <- (0.02759-1.4345*(df$lvl_421_m)+9.84825*(df$lvl_421_m)^2)*1000

#plot(df$stn4_Q_kw~df$stn4_Q)
```



## Export the updated data
```{r}
write.csv(df,here("data_4_analysis/All_Stream_Data_2020-02-25.csv"))
```



## Let's plot the discharge over time
```{r dischargePlot}
df.sub <- df%>%
  select(DateTime,stn1_Q,stn2_Q,stn3_Q,stn4_Q)%>%
  gather(Station,Discharge,-DateTime)
df.sub$DateTime <- as.POSIXct(df.sub$DateTime)
ggplot(df.sub)+
  geom_point(aes(x=DateTime, y=Discharge, col=Station))

```


