---

title: "CO2_EC"
author: "Kayla Emerson"
date: "12/07/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
```

## About

This file is the template for processing CO2 injection data and calculating k600 

Date:
07/21/2022
Gavi-trib

### We start by reading in an then cleaning data, file 

start: 9:18
end: 

CO2 injection 
start: 10:16
end: 11:20

#salt
dist: 
time: 10:45
mass (g): 101.7

dist:
time: 11:13
mass (g): 298.51

```{r pressure, echo=FALSE}
#enter date of injection wich is also the name of the folder for the injection

folder <- "2022-07-21"

setwd(here::here(paste("Injections/"), folder ,"/CO2"))

all_files=list.files(pattern=".csv")        #pulls out the csv files from CO2 folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)


#shorten site name by removing underscores
sites_rp = sapply(strsplit(all_files, "_"), function(x) x[3])

site_names=unique(sites_rp) #creates list of site names for following loop



#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y%H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
   CO2Data$ppm <- as.numeric(as.character(CO2Data$ppm))
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}
```

## Clean up CO2 data

Select data collected during injection period
```{r pressure, echo=FALSE}

#DateTime when injection ended
end <-  as.POSIXct("2022-07-21 17:03:00", tz = "UTC")

xn10m = filter(xn10m, DateTime <= end)

x0m = filter(x0m, DateTime <= end)

x15m = filter(x15m, DateTime <= end)

x30m = filter(x30m, DateTime <= end)

# Now join all sites into a singular data frame so it is easier to analyze 
df_new <- rbind(xn10m, x0m, x15m, x30m)

```

## Notes from the notebook to decipher which viasala box was at each station


xn10m is an old viasala labeled k600
x0m is an new Viasala labeled Box 1
x25m is an new viasala labeled Box 3
x50m is an new viasala labeled Station 3



## Correct viasalas temperature and pressure with HOBO data for the time period we collected data
```{r check CO2 data plot, echo=FALSE}


setwd(here::here(paste("Injections/"),folder))


# first, read in WL hobo at -10m 
waterlevel_n10 <- read.csv("Injection_Temp_xn10m_2022-07-21.csv", skip = 1)
waterlevel_n10 <- waterlevel_n10[,c(2:4)]
colnames(waterlevel_n10) <- c("DateTime", "WL_Pressure", "Temp")

# format DateTime in WL 
waterlevel_n10$DateTime <- as.POSIXct(paste(waterlevel_n10$Date, waterlevel_n10$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")

# correct kpa to hpa 
##1 kPa = 10 hPa
##1 kPa = 0.101972 m
waterlevel_n10$WL_Pressure <- waterlevel_n10$WL_Pressure * 10

#full_join to join CO2 data to WL by datetime
df_corr <- full_join(df_new, waterlevel_n10, by = "DateTime" )

# clean data <- remove NA values bc vaisala reads every 1s and WL reads ever 10s
df_corr <- na.omit(df_corr) 


```
## Correct old Vaisalas 
Old vaisalas need to be corrected for temperature and pressure 
Also need to be corrected for individual calibration -- calibration equations are from vaisalacalibration csv
x10m and x50m are old 

```{r check CO2 data plot, echo=FALSE}

# Make a new data frame from df_corr but just with old vaisalas

df_oldv <- df_corr %>% 
      filter(Station =='xn10m')

# Now correct the adjusted ppm 
df_oldv$adjusted_ppm <- df_oldv$ppm * (1 + (1013 - df_oldv$WL_Pressure) * 0.0015) * (1 - (25 - df_oldv$Temp) * 0.003)

# Now correct for individual vaisala calibration 

# xn10m was an old Viasala labeled K600

df_xn10m <- df_oldv %>% 
      filter(Station =='xn10m')

df_xn10m$adjusted_ppm <-(df_xn10m$adjusted_ppm * 1.06933) -105.52898


```

## Correct new Vaisalas
New vaisalas need to be corrected for just pressure

vaisala @ 0 m
Box 1 New

vaisala @ 25m 
Box 3 new

vaisala @ 50m 
R37391 Station 3

```{r check CO2 data plot, echo=FALSE}
# Make a new data frame from df_corr but just with new vaisalas
df_newv <- df_corr %>% 
      filter(Station =='x0m'|
               Station =='x15m'|
               Station =='x30m')

# Now correct the adjusted ppm 
df_newv$adjusted_ppm <- (df_newv$ppm  )* (1 + (1013 - df_newv$WL_Pressure) * 0.0015)

# Now correct for individual vaisala calibration

# x0m,  Box 1 New
df_x0m <- df_newv %>% 
      filter(Station =='x0m')

df_x0m$adjusted_ppm <- (df_x0m$adjusted_ppm * 1.00054) + 65.15813

# x25m, Box 3 new
df_x15m <- df_newv %>% 
      filter(Station =='x15m')

df_x15m$adjusted_ppm <- (df_x15m$adjusted_ppm * 1.05036) -6.27667


# 50m, R37391 Station 3
df_x30m <- df_newv %>% 
      filter(Station =='x30m')

df_x30m$adjusted_ppm <- (df_x30m$adjusted_ppm * 0.948723) - 13.68636

```

## Plot CO2 for Viasala @ -10m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_xn10m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```

## Plot CO2 for Viasala @ 0m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x0m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Viasala @ 25m

```{r check CO2 data plot, echo=FALSE}

##check data
plot_ly(df_x15m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```




## Plot CO2 for 50m Viasala
```{r check CO2 data plot, echo=FALSE}
##check data
plot_ly(df_x30m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```






## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}
# join data frames to make plotting easier

df_plot <- rbind(df_xn10m, df_x0m, df_x15m, df_x30m)

# use facet wrap to plot multiple stations

together_plot <- ggplot(df_plot, aes(DateTime, adjusted_ppm, color = Station)) +
  geom_point(size = 2) +
  xlab(NULL) +
  ylab(NULL)

together_plot + facet_wrap(~Station, ncol= 3, scales = "free")

together_plot

```



## Finding the mean for before, during, and after the plateau

EXPORT to excel somehow to make a nice table or something 

```{r plot, echo=FALSE}

# find average for each station before plateau

preplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-07-21 09:45:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 10:00:00", tz = "UTC"))
preplat_0 <- filter(df_x0m, DateTime >= as.POSIXct("2022-07-21 09:45:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 10:00:00", tz = "UTC"))
preplat_15 <- filter(df_x15m, DateTime >= as.POSIXct("2022-07-21 10:15:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 10:17:00", tz = "UTC"))
preplat_30 <- filter(df_x30m, DateTime>= as.POSIXct("2022-07-21 10:15:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 10:17:00", tz = "UTC"))

#calculate mean
preplatmeann10m = mean(preplat_n10$adjusted_ppm)
preplatmean0m = mean(preplat_0$adjusted_ppm)
preplatmean15m = mean(preplat_15$adjusted_ppm)
preplatmean30m = mean(preplat_30$adjusted_ppm)

### Change data frame, date and wanted time frame as needed 
plat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-07-21 11:19:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 11:29:00", tz = "UTC"))
plat_0 <- filter(df_x0m, DateTime >= as.POSIXct("2022-07-21 11:19:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 11:29:00", tz = "UTC"))
plat_15 <- filter(df_x15m, DateTime >= as.POSIXct("2022-07-21 11:25:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 11:30:00", tz = "UTC"))
plat_30 <- filter(df_x30m, DateTime >= as.POSIXct("2022-07-21 11:02:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 11:06:00", tz = "UTC"))

#now find the mean of this filtered subset
platmeann10m = mean(plat_n10$adjusted_ppm)
platmean0m = mean(plat_0$adjusted_ppm)
platmean15m = mean(plat_15$adjusted_ppm)
platmean30m = mean(plat_30$adjusted_ppm)

# find average at each station after the slug

#first, clean up data by focusing on wanted time
postplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-07-21 11:25:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 11:28:00", tz = "UTC"))
postplat_0 <- filter(df_x0m, DateTime >= as.POSIXct("2022-07-21 12:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 12:02:00", tz = "UTC"))
postplat_15 <- filter(df_x15m, DateTime >= as.POSIXct("2022-07-21 12:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 12:02:00", tz = "UTC"))
#no post plataue
#postplat_30 <- filter(df_x30m, DateTime >=  as.POSIXct("2022-07-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-06 13:02:00", tz = "UTC"))

#find mean of post plateau
postplatmeann10m = mean(postplat_n10$adjusted_ppm)
postplatmean0m = mean(postplat_0$adjusted_ppm)
postplatmean15m = mean(postplat_15$adjusted_ppm)
#postplatmean30m = mean(postplat_30$adjusted_ppm)
postplatmean30m = NA
```


## Calculating CO2 in the air (look at data before or after vaisalas went into the water)
```{r plot, echo=FALSE}
# Create new data frames for time when vaisalas are out of water
air_n10 <-filter(df_xn10m, DateTime >= as.POSIXct("2022-07-21 09:12:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 09:15:00", tz = "UTC"))
#air_0 <-filter(df_x0m, DateTime >= as.POSIXct("2022-07-06 09:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-06 09:35:00", tz = "UTC"))
#air_15 <-filter(df_x15m, DateTime >= as.POSIXct("2022-07-06 09:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-06 09:35:00", tz = "UTC"))
air_30 <-filter(df_x30m, DateTime >= as.POSIXct("2022-07-21 09:12:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-21 09:15:00", tz = "UTC"))


# Now find mean for this time frame 
airmean_n10m = mean(air_n10$adjusted_ppm)
#airmean_0m = mean(air_0$adjusted_ppm)
airmean_0m = NA
#airmean_15m = mean(air_15$adjusted_ppm)
airmean_15m = NA
airmean_30m = mean(air_30$adjusted_ppm)

```

## Create data table with important objects and export to excel 
focus on calculated vars: pre plateau, plateau, post plateau, and air 
```{r plot, echo=FALSE}
# Create a data frame 
vaisala <- c('xn10m', 'x0m','x15m', 'x30m')
air_co2_ppm <- c(airmean_n10m, airmean_0m, airmean_15m, airmean_30m)
pre_plateau_co2_ppm <- c(preplatmeann10m, preplatmean0m,preplatmean15m, preplatmean30m) 
plateau_co2_ppm <- c(platmeann10m, platmean0m, platmean15m, platmean30m)
post_plateau_co2_ppm <- c(postplatmeann10m, postplatmean0m, postplatmean15m, postplatmean30m)

co2_table <- data.frame(vaisala, air_co2_ppm, pre_plateau_co2_ppm, plateau_co2_ppm, post_plateau_co2_ppm)

co2_table

write.csv(co2_table,here::here("Injections/2022-07-21/injection_co2_result.csv"))

# Export table to excel

```
##calc kc02 for river stretch using kriddie's own brain 
I'm going off road, baby

#First comes the flux

We are pulling from methods in stream ecology now 
eq) 31.1  describes decay rate of leaves over time
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: final weight
  wi: initial weight
  t: time
  
adjusted for decay rate of CO2 over meters
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: co2 mass at 50 m (concentration * discharge)
  wi: co2 mass at 10m  (concentration * discharge)
  t: meters
  
#salt slug info

time: 10:45
dist: -10m
weight: 101.7

x0
Q = 3.96
peak at 10:45:52 
x15
Q = 5.08
Peak at  7/21/2022  10:47:30 AM
x30
Q = 9.82
Peak at 7/21/2022  10:49:09 AM

-------

time: 11:13
dist: -10m
weight: 298.51

x0
Q = 3.58 L/s
peak at 7/21/2022  11:13:56 AM
x15
Q = 5.4
Peak at  7/21/2022  11:15:33 AM
x30
Q = 9.99 L/s
Peak at  7/21/22 7/21/2022  11:17:36 AM

```{r kdub rules the roost}
#convert ppm to mg/l is the easiest thing in the world becaust it is 1:1

#difference between plateau and baseline for upstream and downstream
C_mgperL_0m <- (platmean0m - mean(preplatmean0m,postplatmeann10m))

C_mgperL_25m <- (platmean25m - mean(postplatmean25m))

C_mgperL_50m <- (platmean50m - mean(preplatmean50m,postplatmean50m))

#Discharge comes from hand held
#multiply by 1000 to convert from m3/s to L/s
#Q at 0m = 
Q_0m = 
# Q for 50m = 
Q_50m =

#stream reach length
dist = 50

km <- -log(C_mgperL_50m*Q_50m/(C_mgperL_0m*Q_0m))/dist
#km units: 1/m
```
#convert k in meters to time
kgas,t = kgas,m * v

kgas,t: decay rate over time
kgas,m: decay rate over meters (calculates in chunk above)
v: mean velocity of stream

```{r meters to time }
#mean velocity of stream reach from salt injection is time it took salt to reach peak 
#used data from handwritten data 

# Slug One
#discharge at 50m; poured in salt at 11:50 Peak at  7/6/22 11:52:30
#start: 1
# velocity in m/s
dist_salt = 60
diff_one <- 2.5 * 60
velocity_one <- dist_salt / diff_one


avg_v <- mean(velocity_one)



kt = km * avg_v #units (1/s)
kCO2_mperd <- kt*86400
  
```

#k600
convert to k to k600
```{r convert to k6000}

# Find average water temp for injection

df_avg_water <- filter(df_corr, DateTime >= as.POSIXct("2022-07-06 11:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-07-06 13:00:00", tz = "UTC"))
WaterTempC_ave <- mean(df_avg_water$Temp)

#calc sc
Sc <- 1911.1 - 118.11*WaterTempC_ave + 3.4527*(WaterTempC_ave)^2 - 0.04132*(WaterTempC_ave)^3

K600 <- kCO2_mperd * (600/Sc)^(-0.5)

print(K600)
```
