---

title: "CO2_EC"
author: "Kayla Emerson"
date: "6/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)
library(Bolstad2)
```

## About

In this file I clean and collect CO2 data collected at Cayambe Coca, EC salt injection from June 6, 2022
Injection in mainstem of Gavilan

Start:
CO2 @ 13:00
Salt @ 13:26 - salt continuous injection

#Salt

### We start by reading in an then cleaning data, file 

```{r pressure, echo=FALSE}
setwd(here::here("Injections/2022-06-06/CO2"))

all_files=list.files(pattern=".csv")        #pulls out the csv files from WL folder in HOBOware folder

#sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to select only desired files
#sites_rp = sub('_[^_]+$', '', all_files)


#shorten site name by removing underscores
sites_rp = sapply(strsplit(all_files, "_"), function(x) x[3])

site_names=unique(sites_rp) #creates list of site names for following loop



#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){

  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=7, sep = ",", dec = ".", header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=7,sep = ",", dec = ".", header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%y %H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed

  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
  CO2Data$ppm <- as.numeric(as.character(CO2Data$ppm))
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}
```

## Clean up CO2 data- remove everything after 16:30 on 2022-06-06
This is when we stopped collecting data
We flipped station 10m and 50m because they were most likely mixed up when downloading data. We are also not analyzing the viasala data from 100m because it the CO2 slug did not make it through. But, the data is here if we want to use it at some point. 

```{r pressure, echo=FALSE}
xn10m = filter(xn10m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

x10m = filter(x10m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

x50m = filter(x50m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

x100m = filter(x100m, DateTime <= as.POSIXct("2022-06-06 17:00:00", tz = "UTC"))

# Now join all sites into a singular data frame so it is easier to analyze 
df_new <- rbind(xn10m, x10m, x50m,x100m)

```

## Notes from the notebook to decipher which viasala box was at each station

x50m is an old Viasala labeled box 1 
x10m is an old viasala labeled box 6
xn10m is a new viasala labeled box 1



## Correct viasalas temperature and pressure with HOBO data for the time period we collected data
```{r check CO2 data plot, echo=FALSE}

setwd(here::here("Injections/2022-06-06"))


# first, read in WL hobo at -10m 
waterlevel_n10 <- read.csv("Inj_TEMP_-10m_2022-06-06.csv", skip = 1)
waterlevel_n10 <- waterlevel_n10[,c(2:4)]
colnames(waterlevel_n10) <- c("DateTime", "WL_Pressure", "Temp")

# format DateTime in WL 
waterlevel_n10$DateTime <- as.POSIXct(paste(waterlevel_n10$Date, waterlevel_n10$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")

# correct kpa to hpa 
##1 kPa = 10 hPa
##1 kPa = 0.101972 m
waterlevel_n10$WL_Pressure <- waterlevel_n10$WL_Pressure * 10

#join CO2 data to WL by datetime
df_corr <- right_join(df_new, waterlevel_n10, by = "DateTime" )

# clean data <- remove NA values bc vaisala reads every 1s and WL reads ever 10s
df_corr <- na.omit(df_corr) 

# create a new column for adjusted ppm
df_corr$adjusted_ppm <- 0
df_corr$adjusted_ppm <- as.numeric(df_corr$adjusted_ppm)
df_corr$ppm <- as.numeric(df_corr$ppm)


```
## Correct old Vaisalas 
Old vaisalas need to be corrected for temperature and pressure 
Also need to be corrected for individual calibration -- calibration equations are from vaisalacalibration csv
x10m and x50m are old 

```{r check CO2 data plot, echo=FALSE}

# Make a new data frame from df_corr but just with old vaisalas

df_oldv <- df_corr %>% 
      filter(Station =='x10m' | Station == 'x50m')

# Now correct the adjusted ppm 
df_oldv$adjusted_ppm <- df_oldv$ppm * (1 + (1013 - df_oldv$WL_Pressure) * 0.0015) * (1 - (25 - df_oldv$Temp) * 0.003)

# Now correct for individual vaisala calibration 

# x50m was an old viasala labeled box 6

df_x50m <- df_oldv %>% 
      filter(Station =='x50m')

df_x50m$adjusted_ppm <-  (df_x50m$adjusted_ppm * 0.99484) - 252.9031

# x10m was an old Viasala labeled K600

df_x10m <- df_oldv %>% 
      filter(Station =='x10m')

df_x10m$adjusted_ppm <- (df_x10m$adjusted_ppm * 1.06933) - 105.52898

```

## Correct new Vaisalas
New vaisalas need to be corrected for just pressure 
Also need to be corrected for individual calibaration
xn10m is new, ignore x100m

```{r check CO2 data plot, echo=FALSE}
# Make a new data frame from df_corr but just with new vaisalas
df_newv <- df_corr %>% 
      filter(Station =='xn10m'|Station =='x100m')

# Now correct the adjusted ppm 
df_newv$adjusted_ppm <- (df_newv$ppm)* (1 + (1013 - df_newv$WL_Pressure) * 0.0015)

# Now correct for individual vaisala calibration

# xn10m a new viasala labeled box 1
df_xn10m <- df_newv %>% 
      filter(Station =='xn10m')

#x100m might by new vaisala, though honestly I'm not sure
df_x100m <- df_newv %>% 
      filter(Station =='x100m')

df_xn10m$adjusted_ppm <- (df_xn10m$adjusted_ppm * 1.00054) + 65.15813


#not sure about the correction here so I'm using the same as above
df_x100m$adjusted_ppm <- (df_x100m$adjusted_ppm * 1.00054) + 65.15813

```

## Plot CO2 for Viasala @ -10m

```{r check CO2 data plot df_xn10m, echo=FALSE}

##check data
plot_ly(df_xn10m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```


## Plot CO2 for Viasala @ 10m

```{r check CO2 data plot df_x10m, echo=FALSE}

##check data
plot_ly(df_x10m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 

```



## Plot CO2 for 50m Viasala
```{r check CO2 data plot df_x50m, echo=FALSE}
##check data
plot_ly(df_x50m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```

## Plot CO2 for 100m Viasala
```{r check CO2 data plot df_x50m, echo=FALSE}
##check data
plot_ly(df_x100m,
    x = ~DateTime, y = ~adjusted_ppm, type = 'scatter', mode = 'markers') 
```

## Plot all CO2 data together 
```{r check CO2 data plot, echo=FALSE}
# join data frames to make plotting easier

df_plot <- rbind(df_xn10m, df_x10m, df_x50m,df_x100m)
df_plot <- df_plot%>%filter(DateTime>as.POSIXct("2022-06-06 13:00:00",tz="UTC"))
# use facet wrap to plot multiple stations

together_plot <- ggplot(df_plot, aes(DateTime, adjusted_ppm, color = Station)) +
  geom_point(size = 2) +
  xlab(NULL) +
  ylab(NULL)

together_plot + facet_wrap(~Station, ncol= 3, scales = "free")


together_plot

#write out data 
#write.csv(df_plot,here::here("ProcessedData/Inj_CO2_2022-06-06.csv"))

```



## Finding the mean for before, during, and after the plateau

EXPORT to excel somehow to make a nice table or something 

```{r plot, echo=FALSE}

# find average for each station before plateau

preplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:05:00", tz = "UTC"))
preplat_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:05:00", tz = "UTC"))
preplat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 13:05:00", tz = "UTC"))

#calculate mean
preplatmeann10m = mean(preplat_n10$adjusted_ppm)
preplatmean10m = mean(preplat_10$adjusted_ppm)
preplatmean50m = mean(preplat_50$adjusted_ppm)

### Change data frame, date and wanted time frame as needed 
plat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))
plat_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 14:30:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 14:45:00", tz = "UTC"))
plat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 14:45:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:00:00", tz = "UTC"))

#now find the mean of this filtered subset
platmeann10m = mean(plat_n10$adjusted_ppm)
platmean10m = mean(plat_10$adjusted_ppm)
platmean50m = mean(plat_50$adjusted_ppm)

# find average at each station after the slug

#first, clean up data by focusing on wanted time
postplat_n10 <- filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))
postplat_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 15:10:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))
postplat_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 15:20:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:24:00", tz = "UTC"))

#find mean of post plateau
postplatmeann10m = mean(postplat_n10$adjusted_ppm)
postplatmean10m = mean(postplat_10$adjusted_ppm)
postplatmean50m = mean(postplat_50$adjusted_ppm) 

```


## Calculating CO2 in the air (look at data before or after vaisalas went into the water)
```{r plot, echo=FALSE}
# Create new data frames for time when vaisalas are out of water
air_n10 <-filter(df_xn10m, DateTime >= as.POSIXct("2022-06-06 15:26:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:27:00", tz = "UTC"))
air_10 <- filter(df_x10m, DateTime >= as.POSIXct("2022-06-06 12:36:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 12:38:00", tz = "UTC"))
air_50 <- filter(df_x50m, DateTime >= as.POSIXct("2022-06-06 15:25:30", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:26:00", tz = "UTC"))

# Now find mean for this time frame 
airmean_n10m = mean(air_n10$adjusted_ppm)
airmean_10m = mean(air_10$adjusted_ppm)
#airmean_50m = mean(air_50$adjusted_ppm) # not plugged in for long enough to collect good air measurement
airmean_50m = NA
```

## Create data table with important objects and export to excel 
focus on calculated vars: pre plateau, plateau, post plateau, and air 
```{r plot, echo=FALSE}
# Create a data frame 
vaisala <- c('xn10m', 'x10m', 'x50m')
air_co2_ppm <- c(airmean_n10m, airmean_10m, airmean_50m)
pre_plateau_co2_ppm <- c(preplatmeann10m, preplatmean10m, preplatmean50m) 
plateau_co2_ppm <- c(platmeann10m, platmean10m, platmean50m)
post_plateau_co2_ppm <- c(postplatmeann10m, postplatmean10m, postplatmean50m)

co2_table <- data.frame(vaisala, air_co2_ppm, pre_plateau_co2_ppm, plateau_co2_ppm, post_plateau_co2_ppm)

co2_table

# Export table to excel- you can stop here if you don't want to do CO2 conversions 
#write.csv(co2_table,here::here("Injections/2022-06-06/injection_co2_result.csv"))

#melt data so it is easier to manipulate for CO2 conversions
library(reshape)
co2_table_melt <- melt(co2_table, id=c("vaisala"))


```
##calc kc02 for river stretch using kriddie's own brain 
I'm going off road, baby

#First comes the flux

We are pulling from methods in stream ecology now 
eq) 31.1  describes decay rate of leaves over time
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: final weight
  wi: initial weight
  t: time
  
adjusted for decay rate of CO2 over meters
  -k = loge(Wf/Wi)/t
  k: decay rate
  wf: co2 mass at 50 m (concentration * discharge)
  wi: co2 mass at 10m  (concentration * discharge)
  t: meters

```{r kdub rules the roost}
#convert ppm to mg/l is the easiest thing in the world becaust it is 1:1

#difference between plateu and baseline for upstream and downstream
C_mgperL_10m <- (platmean10m - mean(c(preplatmean10m,postplatmean10m)))

C_mgperL_50m <- (platmean50m - mean(c(preplatmean50m,postplatmean50m)))

#Discharge comes from salt injection
#multiply by 1000 to convert from m3/s to L/s
#Q at 10m = 0.003140479
Q_10m = 0.003140479 * 1000
# Q for 50m = .003311749
Q_50m = 0.003311749 * 1000 

#stream reach length
dist = 50-10

km <- -log(C_mgperL_50m*Q_50m/(C_mgperL_10m*Q_10m))/dist
#km units: 1/m
```
#convert k in meters to time
kgas,t = kgas,m * v

kgas,t: decay rate over time
kgas,m: decay rate over meters (calculates in chunk above)
v: mean velocity of stream

```{r meters to time }
#mean velocity of stream reach from salt injection

#start: 13:26
start <- as.POSIXct("2022-06-06 13:26:00",tz="UTC")
#End: 14:48
end <- as.POSIXct("2022-06-06 14:48:00",tz="UTC")

#we will use the EC data collected at 50m
EC_Data <- read.csv(here::here("Injections/2022-06-06/Discharge/EC/Inj_EC_50m_2022-06-06.csv"),skip=1)[,c(2:5)]
colnames(EC_Data) <- c("DateTime","LowRange","HighRange","Temp_c")
EC_Data$DateTime <- as.POSIXct(EC_Data$DateTime,format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
EC_Data <- EC_Data%>%filter(DateTime > start & DateTime < end)

plot_ly(EC_Data, x = ~DateTime, y = ~LowRange, type = 'scatter', mode = 'markers') 

#manually found plateau time
plateau <- as.POSIXct("2022-06-06 13:48:40",tz="UTC")

#isolate time between salt injection and plateu, subtract out background

df <- EC_Data%>%filter(DateTime<plateau)
df$LowRange <- df$LowRange - 11 #background is 11
df$Time <- format(as.POSIXct(df$DateTime), format = "%H:%M:%S")
df$seconds <- period_to_seconds(hms(df$Time)) - min(period_to_seconds(hms(df$Time)))

#find Mean Travel Time (MTT)
x <- sintegral(df$seconds, df$LowRange, n.pts = nrow(df))
df_int <- data.frame(matrix(ncol = 2, nrow = nrow(df)))
colnames(df_int) <- c("sec","sum")
df_int$sec <- x$x
df_int$sum <- x$y
AUC <- x$int

MTT <- df_int[which.min(abs(AUC/2-df_int$sum)),]$sec

dist = 50

v = dist/MTT #units (m/s)
kt = km * v #units (1/s)
kCO2_mperd <- kt*86400
  
```
#k600
convert to k to k600
```{r convert to k6000}

# Find average water temp for injection

df_avg_water <- filter(df_corr, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:00:00", tz = "UTC"))
WaterTempC_ave <- mean(df_avg_water$Temp)

#calc sc
Sc <- 1911.1 - 118.11*WaterTempC_ave + 3.4527*(WaterTempC_ave)^2 - 0.04132*(WaterTempC_ave)^3

K600 <- kCO2_mperd * (600/Sc)^(-0.5)

print(K600)
```


#k600 at -10m
```{r k600 at -10m}
# first, read in WL hobo at -10m 
flux_n10 <- read.csv(here::here("Injections/2022-07-21/Injections_Flux_xn10m_2022-07-21.csv"))
flux_n10 <- flux_n10[,c(1:5)]
#colnames(flux_n10) <- c("DateTime", "WL_Pressure", "Temp")
flux_n10$Date<-as.Date(with(flux_n10,paste(Year,Month,Day,sep="-")),"%y-%m-%d")
flux_n10$DateTime <- as.POSIXct(paste(flux_n10$Date, flux_n10$Time), format="%Y-%m-%d %H:%M:%S", tz = "UTC")
flux_n10 <- flux_n10%>%filter(Date == "2022-06-06")
#before october, EOS was in EST, not ecuador time, so subtract 1 hour
flux_n10$DateTime <- flux_n10$DateTime - hours(1)
flux_n10 <- flux_n10[,c("DateTime","Flux")]

backgrond_df <- left_join(flux_n10,df_xn10m, by="DateTime")

backgrond_df <- filter(backgrond_df, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))
#add baro data because we need air temp

baro_n10 <- read.csv(here::here("Injections/2022-06-06/Inj_Baro_-10m_2022-06-06.csv"),skip = 1)[2:4]
colnames(baro_n10) <- c("DateTime","AirPress_kpa","AirTemp_c")
baro_n10$DateTime <- as.POSIXct(baro_n10$DateTime, format="%m/%d/%y %I:%M:%S %p", tz = "UTC")

backgrond_df <- left_join(backgrond_df,baro_n10,by="DateTime")

#######
##calculate k600
########
adjustment <-filter(baro_n10, DateTime >= as.POSIXct("2022-06-06 13:00:00", tz = "UTC") & DateTime < as.POSIXct("2022-06-06 15:20:00", tz = "UTC"))

#concentration of air
#use vaisala when in the air

AirPress_hpa <- mean(adjustment$AirPress_kpa)*10
AirTemp_mean <- mean(adjustment$AirTemp_c)

#for this injection, the background vaisala was new
#correct the adjusted ppm and correct for individual vaisala calibration

CO2_air <- mean(air_n10$ppm) * (1 + (1013 - AirPress_hpa) * 0.0015) 
CO2_air <-(CO2_air * 1.00054) + 65.15813
CO2_air_ppm <- CO2_air*10^-6

R=0.08205736608096
gCO2asC <- 12

#convert hpa to atm; 1kPa = 1/101.3 atm
backgrond_df$AirPress_atm <- backgrond_df$AirPress_kpa / 101.3

backgrond_df$VaporPressure_atm <- 10^(5.40221-(1838.675/((backgrond_df$AirTemp_c + 273.15)-31.737)))

backgrond_df$TotalAir_atm <- backgrond_df$AirPress_atm - backgrond_df$VaporPressure_atm
backgrond_df$Total_air_MolperL <- backgrond_df$TotalAir_atm/(R*(backgrond_df$AirTemp_c + 273.15)) 
backgrond_df$CO2_air_MolesPerLiter <- backgrond_df$Total_air_MolperL * CO2_air_ppm
# 12 grams of C in 1 mole of CO2
backgrond_df$CO2_air_gCO2asCPerLiter <- backgrond_df$CO2_air_MolesPerLiter * gCO2asC


### Calculate concentration CO2 in water (gCO2-C per Liter) using Henry's law ###
#Equation below can be used to adjust Henry's constant to the temperature of the environment
# *NOTE: we may need to do an additional calculation to adjust for low pressure in our environment?*
#**KH = KH(STP) x exp(D(1/T-1/T(STP)))**
#* KH(STP) = Henry's law constant at STP (0.035 mol/L)
#*NOTE: the cited literature say that this in mol/(kg x bar)*
#  * D = Temperature dependence constant (2400 K)
#* T = Water Temperature (K)
#* T(STP) = Temp at STP (298.15 K)

#set constants
kH_STP_mol.L.atm = .035
D_K = 2400 
backgrond_df$Watertemp_K <- backgrond_df$Temp + 273.15
T_STP_K = 298.15

#calculate henry's law constant using 
backgrond_df$KH_mol.L.atm <- kH_STP_mol.L.atm * exp(D_K*(1/backgrond_df$Watertemp_K - 1/T_STP_K))

UatmToatm <- 10^6

#calculate mass equivalence of CO2 in water
backgrond_df$CO2_water_gCO2asCPerLiter <- (backgrond_df$adjusted_ppm / UatmToatm) * backgrond_df$KH_mol.L.atm * gCO2asC

#calculate concntration difference between CO2 in the water and in the air
#for some reason, unclear to me, Mcdowell multiplies by henry's constant AGAIN. Let's try it
LiterToCubicMeter = 1000

backgrond_df$deltaCO2_gCO2asCperM3 <-  (backgrond_df$CO2_water_gCO2asCPerLiter - backgrond_df$CO2_air_gCO2asCPerLiter)  *
  backgrond_df$KH_mol.L.atm  * 
  LiterToCubicMeter


#convert flux to mole/m2/d
#seconds per day (86,400)
SecToDay <- 86400
#umole to mole
UmoleToMole <- 10^6
#convert moles to grams of Carbon dioxide as Carbon
#gCO2asC <- 12

backgrond_df$Flux_gCO2asCperM2perDay <- backgrond_df$Flux * SecToDay /  UmoleToMole *gCO2asC

#Fick' Law: calculate K

#**F(aq) = K[pCO2(aq) - pCO2(air)] x KH**
#  * k = F/(pCO2(aq)-pC02(air))/KH
#* F = Flux mole/m2/d
#* K = gas transfer rate m/d
#* KH = henry's constant for molar concentration of CO2 in water 

#*rearrange equation to solve for k*
#**k = F(aq) / ([pCO2(aq) - pCO2(air)] x KH)**

#convert Liters to cubic meters
#LiterToCubicMeter <- 1000
#df$deltaCO2_gCO2asCPerCubicMeter <- df$deltaCO2_gCO2asCPerLiter * LiterToCubicMeter

#calculate

backgrond_df$k_m.d <- backgrond_df$Flux_gCO2asCperM2perDay  / backgrond_df$deltaCO2_gCO2asCperM3


#convert to k600
#k600 = kCO2 * (600/SC)^-0.5
#SC= schmidst constant, temperature dependent
#SC = 1911.1 - 118.11*T + 3.4527*T^2 - 0.04132*T^3
#T = temperature in c
backgrond_df$Sc <- 1911.1 - 118.11*backgrond_df$Temp + 3.4527*(backgrond_df$Temp)^2 - 0.04132*(backgrond_df$Temp)^3

backgrond_df$K600 <- backgrond_df$k_m.d * (600/backgrond_df$Sc)^(-0.5)


summary(backgrond_df)
```