---
title: "FindWaterlevelData_2022-08-19"
author: "Kriddie"
date: "2022-08-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate) #package for our date parsing
library(here)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(purrr)
library(sjmisc)
library(plotly)
#theme_set(theme_bw())
```

## Description

The purpose of this script is to identify the Waterlevel and water temp, at the time of sampling each wetland 

After reading in the data, we will plot it to see if the Waterlevel and water temp is within a range that "makes sense" for the environment that we are measuring.

For each wetland sampled we will take an average of the Waterlevel and water temp collected during the sample period

For example: if samples were sampled wetland 1 on 7/14/2022 between 10am and 11am, we need an average of Waterlevel and water temp from that time period

#Read in Data
We will run a loop so that all water level is merged by site

```{r Hobo WL}
#First the Hobos

setwd(here::here("Wetlands/Files_Renamed/WaterLevelDATA"))
all_files=list.files(pattern=".csv") #pulls out the csv files from CO2 folder
sites_rp = sub('_[^_]+$', '', all_files)
site_names=unique(sites_rp) #creates list of site names for following loop


#rm old files, if they exist
rm(WLData)
rm(Temp_WLData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("WLData")){
      WLData <- read.csv(file, skip=11, header = FALSE, sep = ",",
                         quote = "\"",dec = ".", fill = TRUE, comment.char = "")
      
      if(str_contains(WLData[1,3],"Abs Pres, psi")){
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
        WLData$WLPres_kpa <- WLData$WLPres_kpa*6.89476
        WLData$WLTemp_c <- (WLData$WLTemp_c - 32)/1.8000
        
      } else { 
        WLData <- WLData[-1,]
        colnames(WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        WLData <- WLData[2:4]
        WLData$WLPres_kpa <- as.numeric(as.character(WLData$WLPres_kpa), digits=6)
        WLData$WLTemp_c <- as.numeric(as.character(WLData$WLTemp_c), digits=5)
      }
      WLData$DateTime <- as.POSIXct(WLData$DateTime, tz="UTC",
                                    tryFormats = c("%m/%d/%y %I:%M:%S %p",
                                                   "%m/%d/%Y %H:%M"))
    }
    if (exists("WLData")){
      Temp_WLData <- read.csv(file, skip=1, header = FALSE, sep = ",",
                              quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      #      
      
      if(str_contains(Temp_WLData[1,3],"Abs Pres, psi")){
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
        Temp_WLData$WLPres_kpa <- Temp_WLData$WLPres_kpa*6.89476
        Temp_WLData$WLTemp_c <- (Temp_WLData$WLTemp_c - 32)/1.8000
        
        
      } else { 
        Temp_WLData <- Temp_WLData[-1,]
        colnames(Temp_WLData)=c("row","DateTime","WLPres_kpa","WLTemp_c")
        Temp_WLData <- Temp_WLData[2:4]
        Temp_WLData$WLPres_kpa <- as.numeric(as.character(Temp_WLData$WLPres_kpa), digits=6)
        Temp_WLData$WLTemp_c <- as.numeric(as.character(Temp_WLData$WLTemp_c), digits=5)
      }
      
      
      Temp_WLData$DateTime <- as.POSIXct(Temp_WLData$DateTime, tz="UTC",
                                         tryFormats = c("%m/%d/%y %I:%M:%S %p",
                                                        "%m/%d/%Y %H:%M"))
      
      WLData <- rbind(WLData, Temp_WLData)
      rm(Temp_WLData)
    }
    
  }
  WLData$DateTime <- round_date(WLData$DateTime, "15 mins")
  WLData <- WLData[!with(WLData,is.na(WLPres_kpa)& is.na(WLTemp_c)),]
  WLData$Station <- site
  WLData=unique(WLData)
  assign((paste(site,sep="_")),WLData) #creates object with new appended data
  rm(WLData) #removes WLdata so that multiple sites aren't appended together
}


```



#Clean Data

```{r clean data and plot, echo=FALSE}


#wetland01
WL_Wetland01 <- WL_Wetland01%>%filter(DateTime >= as.POSIXct("2022-06-16 11:00:00",tz = "UTC"))
WL_Wetland01 <- WL_Wetland01%>%filter(DateTime < as.POSIXct("2022-07-14 10:00:00",tz="UTC")|
                                        DateTime > as.POSIXct("2022-07-14 11:00:00",tz = "UTC"))
WL_Wetland01 <- WL_Wetland01%>%filter(DateTime != as.POSIXct("2022-07-25 10:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-11-01 09:15:00",tz = "UTC"))
WL_Wetland01 <- WL_Wetland01%>%filter(DateTime != as.POSIXct("2023-06-20 09:45:00",tz = "UTC"))
#temp
WL_Wetland01$WLTemp_c[WL_Wetland01$DateTime ==  as.POSIXct("2023-02-18 13:30:00",tz = "UTC")] <- NA


#wetland02
WL_Wetland02 <- WL_Wetland02%>%filter(DateTime != as.POSIXct("2022-06-16 11:30:00",tz = "UTC"))
WL_Wetland02 <- WL_Wetland02%>%filter(DateTime != as.POSIXct("2022-07-07 13:45:00",tz = "UTC"))
WL_Wetland02 <- WL_Wetland02%>%filter(DateTime < as.POSIXct("2023-02-20 05:30:00",tz="UTC")|
                                        DateTime > as.POSIXct("2023-02-20 06:15:00",tz = "UTC"))
WL_Wetland02 <- WL_Wetland02%>%filter(DateTime < as.POSIXct("2023-02-20 05:15:00",tz="UTC")|
                                        DateTime > as.POSIXct("2023-02-20 22:15:00",tz = "UTC"))
WL_Wetland02 <- WL_Wetland02%>%filter(DateTime != as.POSIXct("2023-06-20 11:45:00",tz = "UTC")&
                                       DateTime != as.POSIXct("2023-06-20 12:00:00",tz = "UTC"))

 #string broke, bad data for water level. We do need water level for wetland 02 so that we can pair with ave depths measurments collected in July 2023. lets do the correction so that we at least have an thos estimates, and then we will delete the data. I had hoped we could save all the data, but it just looks so weird. I don't know whats going on. maybe some could be saved if I understood?
wl02_sub_1 <- WL_Wetland02%>%filter(DateTime <  as.POSIXct("2023-03-20 14:30:00",tz = "UTC"))
wl02_sub_2 <- WL_Wetland02%>%filter(DateTime >  as.POSIXct("2023-03-20 14:30:00",tz = "UTC"))
wl02_sub_2$WLPres_kpa <- wl02_sub_2$WLPres_kpa + (68.612 - 66.423)
WL_Wetland02_1 <- rbind(wl02_sub_1,wl02_sub_2)

  #extract water level at time of depth data collection
WL_atDepthMeasurment_kpa <- WL_Wetland02_1$WLPres_kpa[WL_Wetland02_1$DateTime ==  as.POSIXct("2023-06-20 09:00:00",tz = "UTC")] 

  #lets keep temp, but delete the bad water level
WL_Wetland02$WLPres_kpa[WL_Wetland02$DateTime >  as.POSIXct("2023-03-20 14:15:00",tz = "UTC")] <- NA


#wetland03
WL_Wetland03 <- WL_Wetland03%>%filter(DateTime != as.POSIXct("2022-07-14 12:30:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-11-01 09:45:00",tz = "UTC"))


#wetland04
WL_Wetland04 <- WL_Wetland04%>%filter(DateTime < as.POSIXct("2022-07-15 13:00:00",tz="UTC")|
                                        DateTime > as.POSIXct("2022-07-15 13:30:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2023-02-18 14:00:00",tz = "UTC"))
#logger shifted 6/29/2022 10:00
#there are no notes in the notebook, but I believe the logger was switched for ? reason

WL_Wetland04_1 <- WL_Wetland04%>%filter(DateTime < as.POSIXct("2022-06-29 10:00:00",tz="UTC"))
WL_Wetland04_1$WLPres_kpa <- WL_Wetland04_1$WLPres_kpa + (66.926-64.264)
WL_Wetland04_2 <- WL_Wetland04%>%filter(DateTime > as.POSIXct("2022-06-29 12:00:00",tz="UTC"))
WL_Wetland04 <- rbind(WL_Wetland04_1,WL_Wetland04_2)
rm(WL_Wetland04_1,WL_Wetland04_2)

WL_Wetland04 <- WL_Wetland04%>%
  filter(DateTime != as.POSIXct("2022-07-15 13:45:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-16 10:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-16 09:45:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2023-06-20 13:15:00",tz = "UTC"))

#wetland05
WL_Wetland05 <- WL_Wetland05%>%filter(DateTime > as.POSIXct("2022-06-16 14:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-27 11:15:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-27 11:15:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-06-28 10:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-19 09:30:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-12-01 11:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2023-08-25 14:30:00",tz = "UTC"))

#temp
WL_Wetland05$WLTemp_c[WL_Wetland05$DateTime ==  as.POSIXct("2022-11-01 11:00:00",tz = "UTC")] <- NA


#wetland06
WL_Wetland06 <- WL_Wetland06%>%filter(DateTime != as.POSIXct("2022-06-16 14:15:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-19 13:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-19 13:15:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2023-02-18 14:15:00",tz = "UTC"))

#wetland07
WL_Wetland07 <- WL_Wetland07%>%filter(DateTime >= as.POSIXct("2022-06-16 15:30:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-11 12:45:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2023-02-18 14:30:00",tz = "UTC"))


#wetland08
WL_Wetland08 <- WL_Wetland08%>%filter(DateTime > as.POSIXct("2022-07-05 10:00:00",tz="UTC"))%>%
  filter(DateTime < as.POSIXct("2022-07-08 10:00:00",tz="UTC")|
                                        DateTime > as.POSIXct("2022-07-08 12:30:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-16 16:30:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-16 16:45:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-16 17:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2023-07-20 15:15:00",tz = "UTC"))
#temp
WL_Wetland08$WLTemp_c[WL_Wetland08$DateTime >  as.POSIXct("2023-07-20 15:15:00",tz = "UTC")] <- NA
WL_Wetland08$WLTemp_c[WL_Wetland08$DateTime >=  as.POSIXct("2023-06-20 15:45:00",tz = "UTC")&
                        WL_Wetland08$DateTime <=  as.POSIXct("2023-06-20 18:00:00",tz = "UTC")] <- NA
WL_Wetland08$WLTemp_c[WL_Wetland08$DateTime ==  as.POSIXct("2023-04-01 13:15:00",tz = "UTC")] <- NA
WL_Wetland08$WLTemp_c[WL_Wetland08$DateTime >  as.POSIXct("2022-10-16 15:45:00",tz = "UTC")&
                        WL_Wetland08$DateTime <=  as.POSIXct("2022-10-16 18:45:00",tz = "UTC")] <- NA
WL_Wetland08$WLTemp_c[WL_Wetland08$DateTime >  as.POSIXct("2022-07-08 09:45:00",tz = "UTC")&
                        WL_Wetland08$DateTime <=  as.POSIXct("2022-07-08 11:15:00",tz = "UTC")] <- NA
WL_Wetland08$WLTemp_c[WL_Wetland08$DateTime <  as.POSIXct("2022-07-05 09:45:00",tz = "UTC")] <- NA


#wetland09
WL_Wetland09 <- WL_Wetland09%>%filter(DateTime > as.POSIXct("2022-07-05 11:30:00",tz="UTC"))%>%
  filter(DateTime < as.POSIXct("2022-07-08 10:00:00",tz="UTC")|
        DateTime > as.POSIXct("2022-07-08 12:30:00",tz = "UTC")) %>%
  filter(DateTime < as.POSIXct("2022-10-16 16:45:00",tz="UTC")|
        DateTime > as.POSIXct("2022-10-17 20:45:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-19 12:45:00",tz = "UTC"))
#temp
WL_Wetland09$WLTemp_c[WL_Wetland09$DateTime >=  as.POSIXct("2022-10-19 13:00:00",tz = "UTC")&
                        WL_Wetland09$DateTime <=  as.POSIXct("2022-10-19 17:00:00",tz = "UTC")] <- NA
WL_Wetland09$WLTemp_c[WL_Wetland09$DateTime >=  as.POSIXct("2022-10-16 16:30:00",tz = "UTC")&
                        WL_Wetland09$DateTime <=  as.POSIXct("2022-10-16 17:00:00",tz = "UTC")] <- NA
WL_Wetland09$WLTemp_c[WL_Wetland09$DateTime >=  as.POSIXct("2022-12-02 13:90:00",tz = "UTC")&
                        WL_Wetland09$DateTime <=  as.POSIXct("2022-12-02 14:30:00",tz = "UTC")] <- NA

#wetland10
WL_Wetland10 <- WL_Wetland10%>%filter(DateTime != as.POSIXct("2022-07-12 11:15:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2023-04-01 13:15:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2023-06-20 15:45:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2023-07-20 15:30:00",tz="UTC"))

#temp
WL_Wetland10$WLTemp_c[WL_Wetland10$DateTime >=  as.POSIXct("2022-10-16 15:00:00",tz = "UTC")&
                        WL_Wetland10$DateTime <=  as.POSIXct("2022-10-16 17:15:00",tz = "UTC")] <- NA
WL_Wetland10$WLTemp_c[WL_Wetland10$DateTime ==  as.POSIXct("2022-07-05 11:45:00",tz = "UTC")] <- NA
WL_Wetland10$WLTemp_c[WL_Wetland10$DateTime >  as.POSIXct("2022-12-02 12:45:00",tz = "UTC")&
                        WL_Wetland10$DateTime <  as.POSIXct("2022-12-02 14:45:00",tz = "UTC")] <- NA
WL_Wetland10$WLTemp_c[WL_Wetland10$DateTime >=  as.POSIXct("2023-06-20 15:30:00",tz = "UTC")&
                        WL_Wetland10$DateTime <=  as.POSIXct("2023-06-20 18:15:00",tz = "UTC")] <- NA


#logger shifted July 12
WL_Wetland10_1 <- WL_Wetland10%>%filter(DateTime <= as.POSIXct("2022-07-12 10:00:00",tz="UTC"))
WL_Wetland10_1$WLPres_kpa <- WL_Wetland10_1$WLPres_kpa + (68.838-68.04)
WL_Wetland10_2 <- WL_Wetland10%>%filter(DateTime > as.POSIXct("2022-07-12 11:30:00",tz="UTC"))
WL_Wetland10 <- rbind(WL_Wetland10_1,WL_Wetland10_2)
rm(WL_Wetland10_1,WL_Wetland10_2)

#wetland11
WL_Wetland11 <- WL_Wetland11%>%filter(DateTime > as.POSIXct("2022-07-11 12:30:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2022-07-28 12:15:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-15 13:15:00",tz="UTC"))%>%
  filter(DateTime >= as.POSIXct("2022-07-11 14:00:00",tz="UTC"))%>%
  filter(DateTime <= as.POSIXct("2022-10-15 13:00:00",tz="UTC")|
          DateTime >= as.POSIXct("2022-10-16 09:30:00",tz="UTC"))%>%
  filter(DateTime <= as.POSIXct("2023-06-20 14:00:00",tz="UTC"))

#temp
WL_Wetland11$WLTemp_c[WL_Wetland11$DateTime >=  as.POSIXct("2022-12-02 10:15:00",tz = "UTC")&
                        WL_Wetland11$DateTime <=  as.POSIXct("2022-12-02 11:30:00",tz = "UTC")] <- NA


#wetland12
WL_Wetland12 <- WL_Wetland12%>%filter(DateTime > as.POSIXct("2022-06-07 14:15:00",tz="UTC"))%>%
  filter(DateTime < as.POSIXct("2022-07-28 11:30:00",tz="UTC")|
        DateTime > as.POSIXct("2022-07-28 13:00:00",tz = "UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-12 13:00:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2022-10-12 13:15:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2023-08-25 16:00:00",tz="UTC"))

wl12_sub_1 <- WL_Wetland12%>%filter(DateTime < as.POSIXct("2022-10-12 14:15:00",tz="UTC"))
wl12_sub_2 <- WL_Wetland12%>%filter(DateTime >= as.POSIXct("2022-10-12 14:15:00",tz="UTC"))
wl12_sub_1$WLPres_kpa <- wl12_sub_1$WLPres_kpa + (66.311 - 65.24536)
WL_Wetland12 <- rbind(wl12_sub_1,wl12_sub_2)

wl12_sub_1 <- WL_Wetland12%>%filter(DateTime < as.POSIXct("2022-12-02 11:00:00",tz="UTC"))
wl12_sub_2 <- WL_Wetland12%>%filter(DateTime >= as.POSIXct("2022-12-02 11:00:00",tz="UTC"))
wl12_sub_1$WLPres_kpa <- wl12_sub_1$WLPres_kpa + (65.04923 - 66.255)
WL_Wetland12 <- rbind(wl12_sub_1,wl12_sub_2)

rm(wl12_sub_1,wl12_sub_2)

#temp
WL_Wetland12$WLTemp_c[WL_Wetland12$DateTime ==  as.POSIXct("2022-10-12 14:15:00",tz = "UTC")] <- NA

##join all
WL_Wetland <- rbind(WL_Wetland01,WL_Wetland02,WL_Wetland03,WL_Wetland04,WL_Wetland05,WL_Wetland06,WL_Wetland07,WL_Wetland08,WL_Wetland09,WL_Wetland10,WL_Wetland11,WL_Wetland12)
```

#check data

```{r plot individual wetlands, echo=FALSE}
ggplot(data = WL_Wetland06, aes(x = DateTime, y = WLPres_kpa)) + geom_point()
ggplot(data = WL_Wetland02, aes(x = DateTime, y = WLTemp_c)) + geom_point()

plot_ly(data = WL_Wetland06, x = ~DateTime, y = ~WLPres_kpa)
plot_ly(data = WL_Wetland12, x = ~DateTime, y = ~WLTemp_c)

#plot all

p1 <- ggplot(data = WL_Wetland, aes(x = DateTime, y = WLPres_kpa)) + geom_point()
p1 + facet_wrap(~Station)+theme(text=element_text(size=21))

p2 <- ggplot(data = WL_Wetland, aes(x = DateTime, y = WLTemp_c)) + geom_point()
p2 + facet_wrap(~Station)

```

#baRO LOOP

```{r baro, echo=FALSE}

###merge data with baro data###
setwd(here::here("Water_Level/BaroPress"))
all_files=list.files(pattern=".csv") #pulls out the csv files from WL folder in HOBOware folder
sites_rp=gsub("_.*","",all_files) #selects the correct pattern so as to seelct only desired files
site_names="Baro" #creates list of site names for following loop

#rm old files, if they exsist
rm(BaroData)
rm(Temp_BaroData)

for (site in site_names){
  
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("BaroData")){
      BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                           quote = "\"",dec = ".", fill = TRUE, comment.char = "")
    }
    if (exists("BaroData")){
      Temp_BaroData <- read.csv(file, skip=10, header = TRUE, sep = ",",
                                quote = "\"",dec = ".", fill = TRUE, comment.char = "")  
      BaroData <- rbind(BaroData, Temp_BaroData)
      rm(Temp_BaroData)
    }
    
  }
  colnames(BaroData)=c("Date","Time","ms","Baro_kpa","BaroTemp_c")
  BaroData=unique(BaroData)
  BaroData$DateTime <- paste(BaroData$Date, BaroData$Time)
  BaroData$DateTime <- as.POSIXct(BaroData$DateTime, format="%m/%d/%Y %I:%M:%S %p", tz="UTC")
  BaroData$DateTime <- round_date(BaroData$DateTime, "15 mins")
  BaroData$ms <- NULL
  BaroData$Date <- NULL
  BaroData$Time <- NULL
  BaroData <- BaroData[,c(3,1,2)]
  BaroData=unique(BaroData)
   BaroData <- BaroData[!with(BaroData,is.na(Baro_kpa)& is.na(BaroTemp_c)),]
  assign((paste(site,sep="_")),BaroData) #creates object with new appended data
  rm(BaroData) #removes WLdata so that multiple sites aren't appended together
}

BaroSTATION <- Baro

#clean baro
BaroSTATION <- BaroSTATION%>%filter(DateTime != as.POSIXct("2022-07-12 10:15:00",tz="UTC"))%>%
  filter(DateTime != as.POSIXct("2023-02-18 12:30:00",tz="UTC"))

```

#correct for baro press
```{r subtract baro, echo=FALSE}

BaroSTATION <- BaroSTATION%>%filter(DateTime > as.POSIXct("2022-06-01 00:00:00",tz="UTC"))
#test <-  BaroSTATION[duplicated(BaroSTATION$DateTime)|duplicated(BaroSTATION$DateTime, fromLast=TRUE),]


WL_Wetland <- rbind(WL_Wetland01,WL_Wetland02,WL_Wetland03,WL_Wetland04,WL_Wetland05,WL_Wetland06,WL_Wetland07,WL_Wetland08,WL_Wetland09,WL_Wetland10,WL_Wetland11,WL_Wetland12)

WL_Wetland <- right_join(BaroSTATION,WL_Wetland,by="DateTime")

WL_Wetland$WaterLevel_m <- (WL_Wetland$WLPres_kpa - WL_Wetland$Baro_kpa) * 0.10197442889221

#correct for baro at that one wetland 2 measurment
Baro_atDepthMeasurment_kpa <- BaroSTATION$Baro_kpa[BaroSTATION$DateTime ==  as.POSIXct("2023-06-20 09:00:00",tz = "UTC")] 

WL_atDepthMeasurment_m <- (WL_atDepthMeasurment_kpa - Baro_atDepthMeasurment_kpa) * 0.10197442889221

p_baro <- ggplot(data = BaroSTATION , aes(x = DateTime, y = Baro_kpa)) + geom_point()
#p_baro

p1 <- ggplot(data = WL_Wetland, aes(x = DateTime, y = WaterLevel_m)) + geom_point()
#p1 + facet_wrap(~Station)

#export data 
#write.csv(WL_Wetland12_corrected, here::here("Kriddie/WL_Wetland12_update.csv"))

```

##Plot


```{r select time, echo=FALSE}
#enter wetland dataframe
wetland <- "WL_Wetland02" # example: WL_Wetland01, WL_Wetland02

#code below extract desired wetland, do not change
wetland_data <- WL_Wetland%>%filter(Station==wetland)
#Water Level
plot_ly(data=wetland_data, x=~DateTime,y=~WaterLevel_m)
#Water Temp
plot_ly(data=wetland_data, x=~DateTime,y=~WLTemp_c)

```

#depth data
add in depth data, best ya can

```{r depth data, echo=FALSE}
depth_DF <- read.csv(here::here("Wetlands/WetlandDepths.csv"))
depth_DF$DateTime <- paste(depth_DF$Date,depth_DF$Start_Time)
depth_DF$DateTime  <- as.POSIXct(depth_DF$DateTime,formula="%Y-%m-%d %H:%M",tz="UTC" )

depth_DF_datetime <- depth_DF%>%select(Wetland,DateTime)
depth_DF_datetime <- unique(depth_DF_datetime)
depth_DF_depth <- depth_DF%>%select(Wetland,Depth_cm)

depth_DF_depth<- depth_DF_depth%>%
  group_by(Wetland) %>% 
  summarize(depth_ave_cm = mean(Depth_cm),
            depth_count = n())

depth_DF <- full_join(depth_DF_datetime,depth_DF_depth,by="Wetland")

depth_DF$Station <- sub("_", "",depth_DF$Wetland)
depth_DF$Station <- sub("^", "WL_", depth_DF$Station )

depth_DF$DateTime <- lubridate::floor_date(depth_DF$DateTime, "3 hour")
depth_DF <- left_join(depth_DF,WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))
depth_DF$WaterLevel_m[2] <- WL_atDepthMeasurment_m

depth_DF$depth_ave_m <- depth_DF$depth_ave_cm/100

depth_DF$depth_diff_m <- depth_DF$depth_ave_m - depth_DF$WaterLevel_m 

WL_Wetland <- full_join(WL_Wetland,depth_DF%>%select(Station,depth_diff_m),by="Station")
WL_Wetland$depth_ave_m <- WL_Wetland$WaterLevel_m + WL_Wetland$depth_diff_m


write.csv(WL_Wetland, here::here("Kriddie/WL_Wetland_ALL.csv"))

```

#add surface area data

```{r surface area data, echo=FALSE}

#test <-  wetland_data[duplicated(wetland_data$DateTime)|duplicated(wetland_data$DateTime, fromLast=TRUE),]

#wetland depth vs surface area relationships

SurfaceArea_df <- read.csv(here::here("Wetlands/DroneFiles/Drone_flights_2023-08-25.csv"))#[,1:7]
#SurfaceArea_df$WL <- as.numeric(SurfaceArea_df$WL)

SurfaceArea_df$Station <- sub("_", "",SurfaceArea_df$Wetland)
SurfaceArea_df$Station <- sub("^", "WL_", SurfaceArea_df$Station )

SurfaceArea_df$Date <- mdy(SurfaceArea_df$Date)
SurfaceArea_df$DateTime <- paste(SurfaceArea_df$Date,SurfaceArea_df$Time_recoreded)
SurfaceArea_df$DateTime  <- as.POSIXct(SurfaceArea_df$DateTime,formula="%Y/%m/%d %H:%M",tz="UTC" )
SurfaceArea_df$DateTime <- lubridate::round_date(SurfaceArea_df$DateTime, "15 minutes")

SurfaceArea_df <- left_join(SurfaceArea_df,WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

Sdf1 <- SurfaceArea_df%>% filter(!is.na(WaterLevel_m))

Sdf2 <- SurfaceArea_df%>% filter(is.na(WaterLevel_m))
Sdf2$DateTime <- as.POSIXct(Sdf2$DateTime, format="%Y-%m-%d %H:%M:%S", tz="UTC") - as.difftime(15, units="mins")
Sdf2 <- left_join(Sdf2%>%select(-WaterLevel_m,-WLTemp_c),WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

Sdf3 <- Sdf2%>% filter(is.na(WaterLevel_m))
Sdf3$DateTime <- as.POSIXct(Sdf3$DateTime, format="%Y-%m-%d %H:%M:%S", tz="UTC") + as.difftime(30, units="mins")
Sdf3 <- left_join(Sdf3%>%select(-WaterLevel_m,-WLTemp_c),WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

Sdf4 <- Sdf3%>% filter(is.na(WaterLevel_m))
Sdf4$DateTime <- as.POSIXct(Sdf4$DateTime, format="%Y-%m-%d %H:%M:%S", tz="UTC") + as.difftime(15, units="mins")
Sdf4 <- left_join(Sdf4%>%select(-WaterLevel_m,-WLTemp_c),WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

Sdf5 <- Sdf4%>% filter(is.na(WaterLevel_m))
Sdf5$DateTime <- as.POSIXct(Sdf5$DateTime, format="%Y-%m-%d %H:%M:%S", tz="UTC") + as.difftime(30, units="mins")
Sdf5 <- left_join(Sdf5%>%select(-WaterLevel_m,-WLTemp_c),WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

Sdf6 <- Sdf5%>% filter(is.na(WaterLevel_m))
Sdf6$DateTime <- as.POSIXct(Sdf6$DateTime, format="%Y-%m-%d %H:%M:%S", tz="UTC") + as.difftime(15, units="mins")
Sdf6 <- left_join(Sdf6%>%select(-WaterLevel_m,-WLTemp_c),WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

Sdf7 <- Sdf6%>% filter(is.na(WaterLevel_m))
Sdf7$DateTime <- as.POSIXct(Sdf7$DateTime, format="%Y-%m-%d %H:%M:%S", tz="UTC") + as.difftime(105, units="mins")
Sdf7 <- left_join(Sdf7%>%select(-WaterLevel_m,-WLTemp_c),WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

Sdf8 <- Sdf7%>% filter(is.na(WaterLevel_m))
Sdf8$DateTime <- as.POSIXct(Sdf8$DateTime, format="%Y-%m-%d %H:%M:%S", tz="UTC") + as.difftime(15, units="mins")
Sdf8 <- left_join(Sdf8%>%select(-WaterLevel_m,-WLTemp_c),WL_Wetland%>%select(Station,DateTime,WaterLevel_m,WLTemp_c),by=c("DateTime","Station"))

SurfaceArea_df_2 <- rbind(Sdf1,Sdf2,Sdf3,Sdf4,Sdf5,Sdf6,Sdf7,Sdf8)

SurfaceArea_df_2 <- SurfaceArea_df_2%>% filter(!is.na(WaterLevel_m))

ggplot(data = SurfaceArea_df_2%>%filter(Wetland == "Wetland_3"), aes(x = WL, y = Area, color=Date)) + 
   geom_point(size=3)

#notes
 #Wetland 1 and 3, revisit
 #I feel certain that, at least one day, wetland 7 was completly dry, but I don't know what day that was
 # wetland 10, revisit
 # did I ever fly both wetland 7 and 11, and 11 was missed?
 
 # also, draw those redlines on rating curves.
 
p2 <- ggplot(data = SurfaceArea_df_2, aes(x = WL, y = Area)) + geom_point()
p2 + facet_wrap(~Wetland)


fig1 <- plot_ly(data=wetland_data ,
        x=~DateTime,y=~WaterLevel_m)
#Water Temp
fig2 <- plot_ly(data=wetland_data,
        x=~DateTime,y=~WLTemp_c)
fig <- subplot(fig1, fig2,nrows = 2)

#
#write.csv(SurfaceArea_df_2, here::here("Kriddie/SurfaceArea_df.csv"))

 WL_low = 1.054550
 WL_high = 0
 
 p <- ggplot(wetland_data%>%filter(Station == "WL_Wetland02") , aes(x=DateTime,y=Q_Ls)) +
   geom_point() + 
   labs(x=NULL, y="WL_m") +
   theme(plot.title = element_text(size = 9)) + 
   geom_hline(yintercept=WL_low, color="red") +
   geom_hline(yintercept=WL_high, color="red") +
   theme(text=element_text(size=18))
 p



```

#write out data

```{r write out data, echo=FALSE}

```


